---
title: "Dementia PDS Quarterly Management Report - DRAFT"
output: 
  flexdashboard::flex_dashboard:
    navbar:
      - title: "Data as at 30 June 2019"
    logo: isdscotland.png
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}

# Load environment file
source(here::here("code", "00_setup-environment.R"))

# Load functions
purrr::walk(dir(here::here("functions"), full.names = TRUE), source)

# Load PDS data
pds <- read_rds(here("data", glue("{fy}-{qt}_final-data.rds"))) %>%
  
  # Filter HB for faster knitting when testing
  
  # Remove codes from board and IJB
  mutate(health_board = str_sub(health_board, 3, -1),
         ijb          = str_sub(ijb, 11, -1))

# Load expected diagnoses reference file
exp <- read_csv(here("reference-files", "expected-diagnoses.csv"))

# Load error summary
err <- read_rds(here("data", glue("{fy}-{qt}_error-summary.rds")))

```

Home
=================================================

Row
-------------------------------------------------

### **About This Report**

This report has been produced by Information Services Division (ISD), part of NHS National Services Scotland, and contains analysis of performance against the [Scottish Government's LDP Standard](https://www.gov.scot/About/Performance/scotPerforms/NHSScotlandperformance/Dementia-LDP) on provision of Dementia Post Diagnostic Support (PDS).

<span style="color:red"> **The information contained in this report is for management information only and should not be distributed widely.** </span>

These reports are an ongoing development following the implementation of the revised [Dementia PDS dataset](https://www.isdscotland.org/Health-Topics/Mental-Health/Dementia-Post-diagnostic-Support/_docs/Dementia-PDS-Definitions-and-Recording-Guidance.pdf) effective 01 April 2019. As such, they are currently marked as **DRAFT** and may be subject to change in future versions.

This report contains data for individuals diagnosed with dementia between **`r format(start_date, "%d %B %Y")`** and **`r format(end_date, "%d %B %Y")`** who were referred for post diagnostic support.

Data are submitted to ISD by health boards on a quarterly basis. Each health board provides updated information for all individuals referred for post diagnostic support with a diagnosis date from `r format(start_date, "%d %B %Y")` onwards. Therefore, data for the full reporting period is refreshed in each management report and is based on the most recently submitted data. This report is based on data submitted in `r sub_month(fy, qt)` and contains data as at **`r format(end_date, "%d %B %Y")`**. 

Information is shown at Scotland, Health Board and Integration Joint Board level using the drop down menus at the top of the page.

To ensure these reports are as useful as possible, we would welcome any comments or feedback you may have via the ISD Dementia PDS team mailbox at: [NSS.ISDDementiaPDS@nhs.net](mailto:NSS.ISDDementiaPDS@nhs.net).



Row
-------------------------------------------------

### LDP Standard

The Local Delivery Plan (LDP) standard is that *everyone newly diagnosed with dementia will be offered a minimum of one year’s post-diagnostic support, coordinated by an appropriately trained Link Worker*. Perfromance is reported in two parts:

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

1. The percentage of people estimated to be newly diagnosed with dementia who were referred for post-diagnostic support.

2. The percentage of people referred who received a minimum of one year’s support.

</div> <br>

For more detail on how the above is calculated, please see the [methodology](#methodology) page.

Further information regarding the Dementia PDS dataset and submission process can be found on the [Dementia PDS pages](https://www.isdscotland.org/Health-Topics/Mental-Health/Dementia-Post-diagnostic-Support/_docs/Dementia-PDS-Definitions-and-Recording-Guidance.pdf?) of the [ISD website](https://www.isdscotland.org/).


<!-- Scotland -->

```{r scotland, include=FALSE, eval = FALSE}

scotland <- map(.x = sort(unique(pds$fy)),
                .f = ~ set_env(data = pds,
                               exp  = exp,
                               err  = err,
                               hb   = "Scotland",
                               year = .x,
                               quarter = qt))

```

`r # paste(knitr::knit_child(text = scotland), collapse = '')`

`r knitr::knit_child("subpage-scotland-temp.Rmd")`


<!-- HEALTH BOARDS -->

```{r health-boards, include=FALSE}

health_boards <- pmap(expand.grid(sort(unique(pds$fy)),
                                  sort(unique(pds$health_board))), 
                      .f = ~ set_env(data = pds,
                                     exp  = exp,
                                     err  = err,
                                     hb   = .y,
                                     year = .x,
                                     quarter = qt))

```

`r paste(knitr::knit_child(text = health_boards), collapse = '')`


Methodology
=================================================

Row
-------------------------------------------------

### <!-- No Title -->

This page includes more detail regarding the methodology used to arrive at the figures in this report. It is hoped that by sharing this, the reports will be easier to understand and local reporting will be more consistent.

This report was produced using R and R Markdown. The code is available publically on [GitHub](https://github.com/alicebyers5/dementia-pds).


Row {.tabset data-height=800}
-------------------------------------------------

### **Number of Expected Diagnoses**

In December 2016, the Scottish Government published a report: [Estimated and Projected Disgnosis Rates for Dementia in Scotland: 2014-2020](https://www.gov.scot/publications/estimated-projected-diagnosis-rates-dementia-scotland-2014-2020/). Estimations are available per calendar year and health board therefore analysis of this part of the LDP standard is unavailable by IJB or any other breakdowns. 

More infomation of the methodology used to calculate these figures and the limitations of this are available in the report.

Please note that as estimations are available by calendar year and figures in this report are by financial year, the estimation for the calendar year with the majority of months in the selected financial year is used. For example, analysis for financial year 2019/20 uses estimations for the calendar year 2019.

It is expected that this report will be refreshed and methodology reviewed in the near future. More information of this will be included in this section as and when it is available.


### **Local Delivery Plan (LDP) Standard Classification**

A record is classed as _complete_ if it meets the following criteria:

* Started PDS within 12 months of diagnosis and support is still ongoing after 12 months

* Started PDS within 12 months of diagnosis and PDS has ended after at least 11 months


A record is classed as a _fail_ if it meets the following criteria:

* PDS started more than 12 months after diagnosis

* PDS not started and more than 12 months has passed since diagnosis

* PDS terminated less than 11 months after first contact date

* PDS terminated before first contact has been made


A record is classed as _exempt_ if the termination reason is one of the following:

* Service user has died

* Service user has moved to a different Health Board

* Service user has terminated PDS early/refused

* Service user no longer able to engage in PDS


A record is classed as _ongoing_ if it meets the following criteria:

* Less than 12 months has passed since diagnosis and PDS has not yet started

* PDS has started within 12 months of diagnosis, is still being received and 12 months has not yet passed


### **Data Quality**

Any errors or queries outstanding following the resubmission deadline will be included in analytical outputs such as these management reports and annual publication. Therefore, the better quality of data submitted, the more accurate these figures will be.

The only adjustments made to the data before analysis by ISD are to remove any records with a diagnosis date outwith the reporting period; i.e. before `r format(start_date, "%d %B %Y")` or after `r format(end_date, "%d %B %Y")` and also remove any records with no diagnosis date provided.

```{r error summary}
err %>% 
  group_by(fy, health_board) %>% 
  summarise(err_rate = round_half_up(sum(total_errors) / sum(records) * 100, 1)) %>%
  ungroup() %>%
  mutate(err_rate = paste0(err_rate, "%")) %>%
  spread(fy, err_rate) %>%
  rename(`Health Board` = health_board) %>%
  kable() %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(15, bold = TRUE)
```

<!-- END OF SCRIPT -->