---
title: "Dementia PDS Quarterly Management Report"
output: 
  flexdashboard::flex_dashboard:
    logo: phs-logo.png
    orientation: rows
    vertical_layout: scroll
---

```{r load-setup, include=FALSE}
source(here::here("code", "00_setup-environment.R"))

# Write numbers with thousands separator
knit_hooks$set(inline = function(x){
  if(!is.character(x)){prettyNum(x, big.mark=",")}else{x}
})
```

---
date: "`r paste('Data as at', format(end_date, '%d %B %Y'))`"
---

```{r setup, include=FALSE}

# Remove tidylog
detach("package:tidylog", unload = TRUE)

# Load functions
walk(dir(here::here("functions"), full.names = TRUE), source)

# Load PDS data
pds <- read_rds(data_path(directory = "mi", 
                    type = "final_data",
                    ext = "rds")) %>% 
  
  # Remove codes from board and IJB
  mutate(health_board = str_sub(health_board, 3, -1),
         ijb          = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))

# Load expected diagnoses reference file
exp <- read_csv(exp_diagnoses_path())


# Load error summary
err <- read_rds(data_path(directory = "mi",
                      type = "error_data", 
                      ext = "rds")) %>% 

  mutate(ijb = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))
```

Home
=================================================

Row
-------------------------------------------------

### **About This Report**

This report has been produced by Public Health Scotland (PHS) and contains analysis of performance against the [Scottish Government's LDP Standard](https://www.gov.scot/About/Performance/scotPerforms/NHSScotlandperformance/Dementia-LDP) on provision of Dementia Post Diagnostic Support (PDS).

<span style="color:red"> **The information contained in this report is for management information only and should not be distributed widely.** </span>

**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS have been affected by the COVID-19 pandemic.**

These reports reflect the [Dementia PDS dataset](https://www.isdscotland.org/Health-Topics/Mental-Health/Dementia-Post-diagnostic-Support/_docs/Dementia-PDS-Definitions-and-Recording-Guidance.pdf) effective 01 April 2019 and contain data for individuals diagnosed with dementia between **`r format(dmy(01042016), "%d %B %Y")`** and **`r format(end_date, "%d %B %Y")`** who were referred for post diagnostic support.

Data are submitted to PHS by health boards on a quarterly basis. Each health board provides updated information for all individuals referred for post diagnostic support with a diagnosis date from `r format(start_date, "%d %B %Y")` onwards. Therefore, data for diagnoses from this date onwards are refreshed in each management report and are based on the most recently submitted data. Data for diagnoses prior to `r format(start_date, "%d %B %Y")` are also included but are now final and will not be updated in future versions of this report.

Information is shown at Scotland, Health Board and Integration Joint Board level using the drop down menus at the top of the page.

To ensure these reports are as useful as possible, we would welcome any comments or feedback you may have via the PHS Dementia PDS team mailbox at: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot).



Row
-------------------------------------------------

### **About the LDP Standard**

The Local Delivery Plan (LDP) standard is that *everyone newly diagnosed with dementia will be offered a minimum of one year’s post-diagnostic support, coordinated by an appropriately trained Link Worker, including the building of a person-centred support plan*. Performance is reported in two parts:

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

1. The percentage of people estimated to be newly diagnosed with dementia who were referred for post-diagnostic support.

2. The percentage of people referred who received a minimum of one year’s worth of post-diagnostic support coordinated by a Link Worker, including the building of a person-centred support plan.

</div> <br>

For more detail on how the above is calculated, please see the [methodology](#methodology) page.

Further information regarding the Dementia PDS dataset and submission process can be found on the [Dementia PDS pages](https://www.isdscotland.org/Health-Topics/Mental-Health/Dementia-Post-diagnostic-Support).


Row
-------------------------------------------------

### **Additional Notes**

*Please note the following:*

**Scotland** – Due to staffing issues the *2022/23* and *2023/24* Scotland figure does not include data from the following areas for the stated quarters : NHS Orkney 2022/23 (*Q3 and Q4*) and 2023/24 (*Q1* and *Q2*). 

**NHS Orkney** – Due to IT staff issues and lack of access to a Consultant Psychiatrist in *2022/23* and *2023/24*, NHS Orkney were unable to provide data for 2022/23 (*Q3*, *Q4*) and 2023/24 (*Q1* and *Q2*).

**NHS Shetland** - NHS Shetland have not had a PDS worker in post since *2022/23 Q1*.  As a result 38 people referred to PDS could not be allocated or contacted by a PDS worker within 12 months of diagnosis hence they have been recorded as not having met the standard. A PDS worker has recently been assigned to post and the PDS service in Shetland will resume. Currently due to the lack of the required information to calculate the standard it is not possible to calculate the standard for *2023/24* year.  It is anticipated that the necessary information will be available in future submissions and figures for *2023/24* will then be revised. 

**NHS Grampian** - Due to staffing issues and system changes, Aberdeen City have reported that they are finding it difficult to collate and report their data timeously and that there will be a lag in the numbers reported. Therefore the numbers presented for recent quarters will be an underestimate of the true number of referrals and likely to be revised in subsequent quarters. Due to changes in service provider the figures for Aberdeen City in 2019/20 and 2020/21 have been affected.

**NHS Tayside** – Due to local IT system issues the figures for *2018/19* and *2019/20* have been affected. PHS have identified issues with the data submitted by NHS Tayside for *2023/24*, which has resulted in some records showing as having met the standard at the end of Q3.  PHS will work with the Health Board to try and rectify this data issue in future submissions.

The figures for the number of people estimated to be newly diagnosed with dementia are not currently available for *2021/22*, *2022/23* and *2023/24*.


<!-- Scotland -->

```{r scotland, include=FALSE}

scotland <- map(.x = sort(unique(pds$fy)),
                .f = ~ set_env(data = pds,
                               exp  = exp,
                               hb   = "Scotland",
                               year = .x,
                               quarter = qt))

```

`r paste(knitr::knit_child(text = scotland), collapse = '')`


<!-- HEALTH BOARDS -->

```{r health-boards, include=FALSE}

health_boards <- pmap(expand.grid(sort(unique(pds$fy)),
                                  sort(unique(pds$health_board))), 
                      .f = ~ set_env(data = pds,
                                     exp  = exp,
                                     hb   = .y,
                                     year = .x,
                                     quarter = qt))

```

`r paste(knitr::knit_child(text = health_boards), collapse = '')`


Methodology
=================================================

Row
-------------------------------------------------

### <!-- No Title -->

This page includes more detail regarding the methodology used to arrive at the figures in this report. It is hoped that by sharing this, the reports will be easier to understand and local reporting will be more consistent.


Row {.tabset data-height=800}
-------------------------------------------------

### **Local Delivery Plan (LDP) Standard Classification**

The following steps are taken to ensure the data is of sufficient quality for analysis:

* Remove records with diagnosis date outwith the reporting period.
* Remove records with missing diagnosis date.

#### LDP Standard Met

* Started PDS within 12 months of diagnosis and support ongoing after 12 months.
* Started PDS within 12 months of diagnosis and PDS ended after at least 11 months.

#### LDP Standard Not Met

* PDS started more than 12 months after diagnosis.
* PDS not started and more than 12 months has passed since diagnosis.
* PDS terminated (for non-exempt reason) less than 11 months after first contact date.
* PDS terminated (for non-exempt reason) before first contact made.

#### Exempt from LDP Standard

* No first contact date or less than 12 months between diagnosis and first contact date and one of the following termination reasons:
    * 03 Service user has died.
    * 04 Service user has moved to a different Health Board area.
    * 05 Service user has terminated PDS early/refused.
    * 06 Service user no longer able to engage in PDS.

#### PDS Ongoing

* Less than 12 months since diagnosis and PDS not yet started.
* PDS started within 12 months and not yet ended.


### **Number of Expected Diagnoses**

In December 2016, the Scottish Government published a report: [Estimated and Projected Diagnosis Rates for Dementia in Scotland: 2014-2020](https://www.gov.scot/publications/estimated-projected-diagnosis-rates-dementia-scotland-2014-2020/). Estimations in this report are available per calendar year and health board therefore analysis of this part of the LDP standard is unavailable by IJB or any other breakdowns. Information on the methodology used to calculate these figures and the limitations of this are available in the report.

For financial years *2021/22, 2022/23 and 2023/24,* the rates referenced in the report above were used to create national, age specific rates of dementia incidence per 1,000 population which were then applied to the National Records of Scotland (NRS) Mid-2021 Population Estimates to obtain the incidence estimates. 

Please note that as estimations are available by calendar year and figures in this report are by financial year, the estimation for the calendar year with the majority of months in the selected financial year is used. For example, analysis for financial year 2018/19 uses estimations for the calendar year 2018.


### **Removal of Duplicate Records**

For a relatively small number of individuals, multiple records have been submitted. To avoid counting these service users more than once, the following rules have been applied to select only one record per CHI Number:

1. Keep record with earliest diagnosis date. If these are the same, then;
2. Keep record with termination reason 04 Service user has moved to a different Health Board area. If no record was terminated for this reason, then;
3. Keep record with earliest first contact date.

There also exists a Service Level Agreement between NHS Highland and NHS Greater Glasgow & Clyde health boards, where some PDS is provided to Argyll & Bute residents by West Dunbartonshire IJB. The support provided to these service users has been apportioned to NHS Highland in this report, as part of the LDP Standard is a population based measure, and so by not including these Argyll & Bute residents this figure may be skewed.

If you have any queries regarding the above, please contact [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot).


Data Quality
=================================================

Row
-------------------------------------------------

### <!-- No Title -->

This page includes information about data quality. Any queries/errors outstanding following the resubmission deadline will be included in analytical outputs such as these management reports and annual publication. Therefore, the better quality of data submitted, the more accurate these figures will be.


Row {.tabset data-height=800}
-------------------------------------------------

### **Errors**

The table below shows the percentage of records which contain one or more queries/errors. Records with a missing diagnosis date or diagnosis date outwith the reporting period are not included in the below counts. Duplicate records are included.

```{r error summary}
err %>% 
  group_by(fy, health_board) %>% 
  summarise(err_rate = round_half_up(sum(total_errors) / sum(records) * 100, 1),
            .groups = "drop") %>%
  bind_rows(
    err %>% 
    group_by(fy = "All", health_board) %>% 
    summarise(err_rate = round_half_up(sum(total_errors) / sum(records) * 100, 1),
              .groups = "drop")) %>%
  mutate(err_rate = paste0(err_rate, "%")) %>%
  pivot_wider(names_from = fy,
              values_from = err_rate,
              values_fill = list(err_rate = "\\-")) %>%
  rename(`Health Board` = health_board) %>%
  kable() %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(15, bold = TRUE) %>%
  # Add header above table 
  add_header_above(
        c(" " = 1,
          "Financial Year of Diagnosis" = 8,
          " " = 1)) %>%
  add_footnote(label = paste("A dash (\\-) indicates no records were submitted",
                             "for diagnoses in this year."),
               notation = "none")
```


### **Number of Records Submitted**

The table below shows the number of records submitted by each Health Board. Records with a missing diagnosis date or diagnosis date outwith the reporting period are not included in the below counts. Duplicate records are included.

```{r record-summary}
err %>%
  filter(str_sub(fy, 1, 4) >= year(start_date)) %>%
  group_by(fy, health_board, ijb) %>% 
  summarise(records = sum(records),
            .groups = "drop") %>%
  bind_rows(
    err %>%
    group_by(fy = "All", health_board, ijb) %>% 
    summarise(records = sum(records),
              .groups = "drop")) %>%
  mutate(records = format(records, big.mark = ",")) %>%
  pivot_wider(names_from = fy, 
              values_from = records,
              values_fill = list(records = "0")) %>%
  arrange(health_board, ijb) %>%
  rename(`Health Board` = health_board,
         `Integration Joint Board (IJB)` = ijb) %>%
  kable(align = c("l", "l", rep("r", length(unique(err$fy)) + 1))) %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(length(unique(paste(err$health_board, err$ijb))), bold = TRUE) %>%
  collapse_rows(columns = 1, valign = "top") %>%
  scroll_box(height = "740px")
```


<!-- END OF SCRIPT -->