`r if_else(max_fy == sel_fy, paste0(hb, '{data-navmenu="Health Boards"}'), paste0(hb, " ", str_replace(sel_fy, "/", ""), ' {.hidden}'))`
=================================================

```{r summary figures, include=FALSE}

# Expected vs Referrals
ref <- sum(subpage_data$referrals)
exp_rate <- (ref / exp) * 100

# 12 Months Complete
num <- subpage_data %>% filter(ldp %in% c("complete", "exempt")) %>% {sum(.$referrals)}
den <- subpage_data %>% filter(ldp %in% c("complete", "exempt", "fail")) %>% {sum(.$referrals)}
pds_rate <- (num / den) * 100

complete_year <- if_else(max_fy == sel_fy & qt != 4, FALSE, TRUE)
```

Sidebar {.sidebar}
-----------------------------------------------------------------------

### `r hb`
#### Financial Year `r sel_fy`

***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

Select Financial Year

<!-- For some reason need '-2' on end of 1819 links - check why this is -->
|     `r paste0("[2019/20](#", hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"), "-3)")`
|     `r paste0("[2018/19](#", hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"), "-", "201819)")`
|     `r paste0("[2017/18](#", hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"), "-", "201718)")`
|     `r paste0("[2016/17](#", hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"), "-", "201617)")`

***

<!-- Reword this and try and force to bottom of sidebar -->
Please get in touch with any comments, suggestions and feedback: [NSS.ISDDementiaPDS@nhs.net](mailto:NSS.ISDDementiaPDS@nhs.net)


Row 
----------------------------------------------------------------------

`r ifelse(complete_year == TRUE, "", "### Text here")`
```{r Referrals Value Box, include = !complete_year}
valueBox(ref, 
         icon = "fa-hashtag",
         caption = glue("referrals were made for post-diagnostic support."))
```

`r ifelse(complete_year == TRUE, "### Referrals Value Box", "")`
```{r Referrals Value Box, include = complete_year}
valueBox(ref, 
         icon = "fa-hashtag",
         caption = glue("referrals were made for post-diagnostic support."))
```


`r ifelse(complete_year == TRUE, "### Expected Value Box", "")`
```{r Expected Value Box, include = complete_year}
valueBox(paste0(round_half_up(exp_rate, 1), "%"), 
         icon = "fa-percent",
         caption = glue("of the expected number of diagnoses were ",
                        "referred for post diagnostic support."))
```

`r ifelse(complete_year == TRUE, "### 12 Months Value Box", "")`
```{r 12 Months Value Box, include = complete_year}
valueBox(paste0(round_half_up(pds_rate, 1), "%"), 
         icon = "fa-percent",
         caption = glue("of those referred for post diagnostic support ",
                        "received 12 months of support."))
```


Row {data-height=450}
----------------------------------------------------------------------

### LDP Breakdown

Some text here to set the scene...


```{r LDP Table}
subpage_data %>%
  group_by(ijb, ldp) %>%
  summarise(referrals = sum(referrals)) %>%
  bind_rows(subpage_data %>%
              group_by(ldp) %>%
              summarise(ijb = hb,
                        referrals = sum(referrals))) %>%
  ungroup() %>%
  complete(ijb, ldp = c("complete", "exempt", "fail", "ongoing"),
           fill = list(referrals = 0)) %>%
  bind_rows(subpage_data %>%
              group_by(ijb) %>%
              summarise(ldp = "Total",
                        referrals = sum(referrals)),
            subpage_data %>%
              summarise(ldp = "Total",
                        ijb = hb,
                        referrals = sum(referrals))) %>%
  mutate(`LDP Status` = 
           case_when(
             ldp == "complete" ~ "Met Standard",
             ldp == "fail" ~ "Not Met Standard",
             TRUE ~ str_to_title(ldp)
           )) %>%
  select(-ldp) %>%
  spread(ijb, referrals) %>%
  mutate_all(~ replace_na(., 0)) %>%
  kable() %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(5, bold = TRUE) %>%
  add_header_above(
    c(" " = 2, 
      "Integration Joint Board (IJB)" = length(unique(subpage_data$ijb))))
```


### **Number of Individuals Diagnosed and Referred for PDS** {data-width=800}

```{r Referrals Plot}

plot_referrals(subpage_data, 
               scotland = FALSE,
               quarter = ifelse(max_fy == sel_fy, qt, NA))

```

