---
title: "PATHWAYS DRAFT"
output: 
  flexdashboard::flex_dashboard:
    logo: phs-logo.png
    orientation: rows
    vertical_layout: scroll
---

```{r load-setup, include=FALSE}
source(here::here("code", "00_setup-environment.R"))
library(crosstalk) # for drop down menus
library(phsstyles)
library(htmltools)


# Write numbers with thousands separator
knit_hooks$set(inline = function(x){
  if(!is.character(x)){prettyNum(x, big.mark=",")}else{x}
})
```

---
date: "`r paste('Data as at', format(end_date, '%d %B %Y'))`"
---

```{r setup, include=FALSE}

# Remove tidylog
detach("package:tidylog", unload = TRUE)

# Load functions
walk(dir(here::here("functions"), full.names = TRUE), source)

# Load PDS data
pds <- read_rds(get_mi_data_path("final_data", ext = "rds", test_output = test_output)) %>% 
  
  # Remove codes from board and IJB
  mutate(health_board = str_sub(health_board, 3, -1),
         ijb          = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))

# Load expected diagnoses reference file
exp <- read_csv(get_exp_diagnoses_path())


# Load error summary
err <- read_rds(get_mi_data_path("error_data", ext = "rds", test_output = test_output)) %>% 

  mutate(ijb = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))
```
<!-- delete all of above when finished testing -->


```{r data setup, include=FALSE}
wait_data <- read_rds(get_mi_data_path("wait_data", ext = "rds", test_output = test_output))

wait_data_2 <- read_rds(get_mi_data_path("wait_data_2", ext = "rds", test_output = test_output))

wait_data_3 <- read_rds(get_mi_data_path("wait_data_3", ext = "rds", test_output = test_output))

pds_ijb <- pds %>% arrange(ijb)

pds_scot <- pds %>% group_by(health_board = "Scotland", ijb = "Scotland", fy, month, ldp, age_grp, simd) %>% 
  summarise(referrals = sum(referrals), .groups = "drop")

pds_hb <- pds %>% group_by(health_board, fy, month, ldp, age_grp, simd) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ijb = health_board, .before = fy)

pds_all <- bind_rows(pds_scot, pds_hb, pds_ijb)

pds_all %<>% rename(geog = ijb) 

pds_all$geog<- factor(pds_all$geog, levels = unique(pds_all$geog))

wait_data$health_board <- as.factor(wait_data$health_board)
wait_data$fy <- as.factor(wait_data$fy)
wait_data$simd <- as.factor(wait_data$simd)
wait_data$sex <- as.factor(wait_data$sex)
wait_data$ijb <- as.factor(wait_data$ijb)


wait_data_2$health_board <- as.factor(wait_data_2$health_board)
wait_data_2$fy <- as.factor(wait_data_2$fy)
wait_data_2 %<>% arrange(termination_or_transition_reason)
wait_data_2$sex <- as.factor(wait_data_2$sex)
wait_data_2$ijb <- factor(wait_data_2$ijb, levels = unique(pds_all$geog))
wait_data_2 %<>% mutate(termination_or_transition_reason = if_else(termination_or_transition_reason == "14 All reasons", substring(termination_or_transition_reason, 3), termination_or_transition_reason))
wait_data_2$termination_or_transition_reason <- as.factor(wait_data_2$termination_or_transition_reason)

wait_data_3$health_board <- as.factor(wait_data_3$health_board)
wait_data_3$fy <- as.factor(wait_data_3$fy)
wait_data_3 %<>% arrange(termination_or_transition_reason)
wait_data_3$sex <- as.factor(wait_data_3$sex)
wait_data_3$ijb <- factor(wait_data_3$ijb, levels = unique(pds_all$geog))
wait_data_3 %<>% mutate(termination_or_transition_reason = if_else(termination_or_transition_reason == "14 All reasons", substring(termination_or_transition_reason, 4), termination_or_transition_reason))
wait_data_3$termination_or_transition_reason <- as.factor(wait_data_3$termination_or_transition_reason)
 
```



PDS Pathways
=================================================
Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

### Pathways - Waiting Times
***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

<ul>
  <li>[Pathways - Waiting Times](#pds-pathways)</li>
  <li>[Pathways - Termination of PDS](#termination-reasons)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

Row
----------------------------------------------------------------------

### **Note**

**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.**


Row {.tabset data-height=760}
----------------------------------------------------------------------

### **Integration Authority Areas**

```{r dropdown-wait-ijb}
wait_data_ijb <- wait_data %>% 
      filter(sex == "All") %>% 
     filter(ijb != "All", simd == "All") %>% 
      select(ijb, fy, total_referrals, median_diagnosis_to_referral,
             perc_allocated, median_referral_to_allocation,
             perc_contacted, median_allocation_to_contact,
             median_diagnosis_to_contact) %>% 
  mutate(across(starts_with("perc"), ~ paste0(.,"%"))) %>%
  mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
      mutate(ijb = if_else(ijb == "Scotland", "AAA", ijb)) %>%
      arrange(ijb) %>% 
      mutate(ijb = if_else(ijb == "AAA", "Scotland", ijb)) %>% 
      set_colnames(c("Integration Authority Area", "fy", "Number of People Referred to PDS",  "Average (median) days from diagnosis to PDS referral",
                     "Percentage of Referrals allocated to PDS practitioner", "Average (median) days from referral to allocation of PDS practitioner", 
                     "Percentage of Referrals contacted by PDS practitioner",  "Average (median) days from allocation to first contact with PDS practitioner",
                     "Average (median) days from diagnosis to first contact"
      )) 

wait_table_data_ijb <- SharedData$new(wait_data_ijb)

data_filter_ijb_year <- filter_select(id = "wait_filter_ijb_year",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = wait_table_data_ijb,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,4,NA), NULL,
data_filter_ijb_year, NULL)

```

<h2 style="margin-left: 60px; margin-top: 0px; margin-bottom: -20px"> Pathways from diagnosis to contact by PDS practitioner </h2>
```{r wait-table-ijb}
bscols(widths = 12,
       div(style = css(width="97%", height="585px", margin="20px"),
    DT::datatable(wait_table_data_ijb, rownames = FALSE,  
                                        caption = htmltools::tags$caption(
                       style = 'caption-side: bottom; text-align: left;',
                       "A dash (-) indicates no dates of referral were submitted for diagnoses in this 
                              year."),
                       options = list(pageLength = 32,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:8)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

  

```

### **Health Boards**

```{r wait-dropdown-hb}

wait_data_hb <- wait_data %>% 
      filter(sex == "All") %>% 
      filter(ijb == "All" | ijb == "Scotland", simd == "All") %>% 
     select(health_board, fy, total_referrals, median_diagnosis_to_referral,
             perc_allocated, median_referral_to_allocation,
             perc_contacted, median_allocation_to_contact,
             median_diagnosis_to_contact) %>% 
  mutate(across(starts_with("perc"), ~ paste0(.,"%"))) %>%
  mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
      set_colnames(c("Health Board", "fy", "Number of People Referred to PDS",  "Average (median) days from diagnosis to PDS referral",
                     "Percentage of Referrals allocated to PDS practitioner", "Average (median) days from referral to allocation of PDS practitioner", 
                     "Percentage of Referrals contacted by PDS practitioner",  "Average (median) days from allocation to first contact with PDS practitioner",
                     "Average (median) days from diagnosis to first contact"
      )) 

wait_table_data_hb <- SharedData$new(wait_data_hb)

data_filter_hb_year <- filter_select(id = "wait_filter_hb_year",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = wait_table_data_hb,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,4,NA), NULL,
data_filter_hb_year, NULL)

```

<h2 style="margin-left: 60px; margin-top: 0px; margin-bottom: -20px"> Pathways from diagnosis to contact by PDS practitioner </h2>
```{r wait-table-hb}

bscols(widths = 12,
       div(style = css(width="97%", height="585px", margin="20px"),
  DT::datatable(wait_table_data_hb, rownames = FALSE,
                 caption = htmltools::tags$caption(
                       style = 'caption-side: bottom; text-align: left;',
                       "A dash (-) indicates no dates of referral were submitted for diagnoses in this 
                              year."),
              options = list(pageLength = 15,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:8)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```


Termination Reasons {.hidden}
=================================================
Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

### Pathways - Termination of PDS
***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

<ul>
  <li>[Pathways - Waiting Times](#pds-pathways)</li>
  <li>[Pathways - Termination of PDS](#termination-reasons)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

Row
----------------------------------------------------------------------

### **Note**

**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.**

Row {.tabset data-height=670}
----------------------------------------------------------------------

### **Integration Authority Areas**

```{r dropdown-term-ijb}
term_data_ijb_1 <- wait_data_3 %>% 
    filter(sex == "All", termination_or_transition_reason == "All reasons") %>%
    filter(ijb == "Scotland" | !grepl("NHS", ijb)) %>% 
    pivot_wider(names_from = ldp, values_from = c(referrals, median_referral_to_termination)) %>%
   select(fy, ijb,
           referrals_All,
           median_referral_to_termination_All,
           referrals_exempt,
           referrals_fail)
    
wait_data_totals_ijb <- wait_data %>% filter(sex == "All", simd == "All", ijb != "All" | ijb == "Scotland") %>% select(ijb, fy, total_referrals)

term_data_ijb <- left_join(wait_data_totals_ijb, term_data_ijb_1) %>% 
  mutate(across(starts_with("referrals"), ~ replace(., is.na(.), 0))) %>%
    mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
     mutate(perc_term_early = paste0(round((referrals_All/total_referrals)*100,1),"%")) %>% 
      mutate(perc_term_early_exempt = if_else(referrals_exempt == 0, NA,
        round((referrals_exempt/referrals_All)*100,1))) %>% 
          mutate(perc_term_early_exempt = if_else(!is.na(perc_term_early_exempt), paste0(perc_term_early_exempt, "%"), "-")) %>% 
  select(fy, ijb,
         total_referrals,
           referrals_All,
         perc_term_early,
           referrals_exempt,
         perc_term_early_exempt) %>% 

    set_colnames(c("fy", "Integration Authority Area", "Number of People Referred to PDS",
                   "Number of referrals whose PDS ended with no contact",
                   "Percentage of referrals whose PDS ended with no contact",
                   "Number of referrals whose PDS ended with no contact Exempt from LDP standard",
                   "Percentage of referrals whose PDS ended with no contact Exempt from LDP standard"))

term_table_data_ijb <- SharedData$new(term_data_ijb)

data_filter_year_term_ijb <- filter_select(id = "term_filter_year_ijb",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = term_table_data_ijb,
                                    multiple = FALSE
                                   )


bscols(widths = c(1,4,NA), NULL,
data_filter_year_term_ijb, NULL)

```

<h2 style="margin-left: 60px; margin-top: 0px; margin-bottom: -20px"> Pathways from referral to termination of PDS </h2>
```{r term-table-ijb}

bscols(widths = 12,
       div(style = css(width="97%", height="500px", margin="20px"),
     DT::datatable(term_table_data_ijb, rownames = FALSE,
              options = list(pageLength = 33,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0),
                                                list(className = 'dt-right', targets = 2:6)
                                                #list(width = '30px', targets = 6)
                                                ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```

### **Health Boards**

```{r dropdown-term-hb}

 term_data_hb_1 <- wait_data_3 %>% 
    filter(sex == "All", termination_or_transition_reason == "All reasons") %>%
    filter(ijb == "Scotland" | grepl("NHS", ijb)) %>% 
    pivot_wider(names_from = ldp, values_from = c(referrals, median_referral_to_termination)) %>%
  select(-health_board) %>% rename(health_board = ijb) %>% 
  select(fy, health_board,
           referrals_All,
           median_referral_to_termination_All,
           referrals_exempt,
           referrals_fail)
    
wait_data_totals_hb <- wait_data %>% filter(sex == "All", simd == "All", ijb == "All" | ijb == "Scotland") %>% select(health_board, fy, total_referrals)

term_data_hb <- left_join(wait_data_totals_hb, term_data_hb_1) %>% 
  mutate(across(starts_with("referrals"), ~ replace(., is.na(.), 0))) %>%
    mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
     mutate(perc_term_early = paste0(round((referrals_All/total_referrals)*100,1),"%")) %>% 
      mutate(perc_term_early_exempt = if_else(referrals_exempt == 0, NA,
        round((referrals_exempt/referrals_All)*100,1))) %>% 
          mutate(perc_term_early_exempt = if_else(!is.na(perc_term_early_exempt), paste0(perc_term_early_exempt, "%"), "-")) %>% 
  select(fy, health_board,
         total_referrals,
           referrals_All,
         perc_term_early,
           referrals_exempt,
         perc_term_early_exempt) %>% 

    set_colnames(c("fy", "Health Board", "Number of People Referred to PDS",
                   "Number of referrals whose PDS ended with no contact",
                   "Percentage of referrals whose PDS ended with no contact",
                   "Number of referrals whose PDS ended with no contact Exempt from LDP standard",
                   "Percentage of referrals whose PDS ended with no contact Exempt from LDP standard"))

term_table_data_hb <- SharedData$new(term_data_hb)

data_filter_year_term_hb <- filter_select(id = "term_filter_year_hb",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = term_table_data_hb,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,4,NA), NULL,
data_filter_year_term_hb, NULL)

```

<h2 style="margin-left: 60px; margin-top: 0px; margin-bottom: -20px"> Pathways from referral to termination of PDS </h2>
```{r term-table-hb}
bscols(widths = 12,
       div(style = css(width="97%", height="500px", margin="20px"),
     DT::datatable(term_table_data_hb, rownames = FALSE,
              options = list(pageLength = 15,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0),
                                                list(className = 'dt-right', targets = 2:6)
                                                #list(width = '30px', targets = 6)
                                                ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```

Row {.tabset data-height=770}
----------------------------------------------------------------------

### **Termination Reasons - PDS Ending Without Contact**

```{r dropdown-term-1}
 term_data_2 <- wait_data_3 %>%
    filter(sex == "All") %>%
    pivot_wider(names_from = ldp, values_from = c(referrals, median_referral_to_termination)) %>%
    mutate(across(starts_with("referrals"), ~ replace(., is.na(.), 0))) %>%
    mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>%
    select(fy, ijb, termination_or_transition_reason,
           referrals_All, 
           median_referral_to_termination_All,
           referrals_exempt,
           referrals_fail) %>%
    set_colnames(c("fy", "geog", "Reason for termination of post-diagnostic support",
                   "Number of people", 
                   "Average (median) days from referral to termination of PDS",
                   "Exempt from Standard",
                   "Standard Not Met"))

term_table_data_2 <- SharedData$new(term_data_2)

data_filter_year_term_2 <- filter_select(id = "term_filter_year_2",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = term_table_data_2,
                                    multiple = FALSE
                                   )

data_filter_geog_term_2 <- filter_select(id = "term_filter_geog_2",
                                    label = "Select Health Board or Integration Authority Area:",
                                    group = ~geog,
                                    sharedData = term_table_data_2,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,5,5,NA), NULL,
data_filter_year_term_2, data_filter_geog_term_2, NULL)



```

<h2 style="margin-left: 60px; margin-top: 0px; margin-bottom: -20px"> Pathways from referral to termination of post-diagnostic support without contact </h2>
```{r term-table-1}

bscols(widths = 12,
       div(style = css(width="97%", height="590px", margin="20px"),
     DT::datatable(term_table_data_2, rownames = FALSE,
              options = list(pageLength = 14,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0:1),
                                                list(className = 'dt-right', targets = 3:6)
                                                #list(width = '30px', targets = 6)
                                                ))) %>%
           DT::formatStyle(3, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```

### **Termination Reasons - PDS Ending On or After Contact**

```{r dropdown-term-2}
 term_data <- wait_data_2 %>% 
    filter(sex == "All") %>% 
    pivot_wider(names_from = ldp, values_from = c(referrals, median_contact_to_termination)) %>% 
    mutate(across(starts_with("referrals"), ~ replace(., is.na(.), 0))) %>% 
    mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
    select(fy, ijb, termination_or_transition_reason,
           referrals_All,
           median_contact_to_termination_All,
           referrals_complete,
           referrals_exempt,
           referrals_fail) %>% 
    set_colnames(c("fy", "geog", "Reason for end of post-diagnostic support",
                   "Number of people", 
                   "Average (median) days from first contact with PDS practitioner to end of PDS",
                   "Standard Met",
                   "Exempt from Standard",
                   "Standard Not Met"))
 
term_table_data <- SharedData$new(term_data)

data_filter_year_term <- filter_select(id = "term_filter_year",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = term_table_data,
                                    multiple = FALSE
                                   )

data_filter_geog_term <- filter_select(id = "term_filter_geog",
                                    label = "Select Health Board or Integration Authority Area:",
                                    group = ~geog,
                                    sharedData = term_table_data,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,5,5,NA), NULL,
data_filter_year_term, data_filter_geog_term, NULL)

```

<h2 style="margin-left: 60px; margin-top: 0px; margin-bottom: -20px"> Pathways from contact by PDS practitioner to end of post-diagnostic support </h2>
```{r term-table-2}

bscols(widths = 12,
       div(style = css(width="97%", height="590px", margin="20px"),
     DT::datatable(term_table_data, rownames = FALSE,
              options = list(pageLength = 14,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0:1),
                                                list(className = 'dt-right', targets = 3:7)#,
                                                #list(width = '10px', targets = 6)
                                                ))) %>%
           DT::formatStyle(3, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```

```{js }
function filter_default() {

  document.getElementById("wait_filter_ijb_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("wait_filter_ijb_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("wait_filter_hb_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("wait_filter_hb_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_year_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("term_filter_year_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("term_filter_year_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("term_filter_year_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("term_filter_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_geog").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("term_filter_geog").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_year_2").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("term_filter_year_2").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_geog_2").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("term_filter_geog_2").getElementsByClassName("selectized")
  [0].selectize.removeOption("");

 document.getElementById("trend_filter_age_prop").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("trend_filter_age_prop").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("filter_pop_age_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("filter_pop_age_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("filter_pop_age_hb_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("NHS Ayrshire & Arran", false);

  document.getElementById("filter_pop_age_hb_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
    document.getElementById("filter_ldp_simd").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("filter_ldp_simd").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
    document.getElementById("trend_filter_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue("NHS Ayrshire & Arran", false);

  document.getElementById("trend_filter_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("trend_filter_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("Aberdeen City", false);

  document.getElementById("trend_filter_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
 
   document.getElementById("trend_filter_pop").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("trend_filter_pop").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("trend_filter_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("trend_filter_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  }
  
  window.onload = filter_default;

```
