---
title: "PATHWAYS DRAFT"
output: 
  flexdashboard::flex_dashboard:
    logo: phs-logo.png
    orientation: rows
    vertical_layout: scroll
---

```{r load-setup, include=FALSE}
source(here::here("code", "00_setup-environment.R"))
library(crosstalk) # for drop down menus
library(phsstyles)
library(htmltools)


# Write numbers with thousands separator
knit_hooks$set(inline = function(x){
  if(!is.character(x)){prettyNum(x, big.mark=",")}else{x}
})
```

---
date: "`r paste('Data as at', format(end_date, '%d %B %Y'))`"
---

```{r setup, include=FALSE}

# Load functions
walk(dir(here::here("functions"), full.names = TRUE), source)


# Load PDS data
pds <- read_rds(get_mi_data_path("final_data", ext = "rds", test_output = test_output)) %>% 
  
  # Remove codes from board and IJB
  mutate(health_board = str_sub(health_board, 3, -1),
         ijb          = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))

# Load expected diagnoses reference file
exp <- read_csv(get_exp_diagnoses_path())


# Load error summary
err <- read_rds(get_mi_data_path("error_data", ext = "rds", test_output = test_output)) %>% 

  mutate(ijb = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))

# calculate referrals for Scotland and health boards
pds_ijb <- pds %>% arrange(ijb)

pds_ijb %<>% rename(geog = ijb) 

pds_ijb$geog<- factor(pds_ijb$geog, levels = unique(pds_ijb$geog))

pds_scot <- pds %>% group_by(health_board = "Scotland", ijb = "Scotland", fy, month, ldp_full, ldp, age_grp_2, age_grp, simd, sex) %>%  summarise(referrals = sum(referrals), .groups = "drop")

pds_scot %<>% rename(geog = ijb) 

pds_scot$geog<- factor(pds_scot$geog, levels = unique(pds_scot$geog))

pds_hb <- pds %>% group_by(health_board, fy, month, ldp_full, ldp, age_grp_2, age_grp, simd, sex) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ijb = health_board, .before = fy)

pds_hb %<>% rename(geog = ijb) 

pds_hb$geog<- factor(pds_hb$geog, levels = unique(pds_hb$geog))

# combine data for ijb, hb and Scotland
pds_all <- bind_rows(pds_scot, pds_ijb, pds_hb)

pds_all$geog<- factor(pds_all$geog, levels = unique(pds_all$geog))

#get totals for all geogs, hbs, ijbs, scotland
pds_all_totals <- pds_all %>% group_by(geog, fy, age_grp_2 = "All") %>% summarise(total_referrals = sum(referrals))

pds_ijb_totals <- pds_ijb %>% group_by(geog, fy, age_grp_2 = "All") %>% summarise(total_referrals = sum(referrals))

pds_hb_totals <- pds_hb %>% group_by(geog, fy, age_grp_2 = "All") %>% summarise(total_referrals = sum(referrals))

pds_scot_totals <- pds_scot %>% group_by(geog, fy, age_grp_2 = "All") %>% summarise(total_referrals = sum(referrals))


#get totals for all geogs, hbs, ijbs, scotland with LARGE AGE GROUPS
pds_all_totals_2 <- bind_rows(pds_all_totals,
  pds_all %>% filter(age_grp_2 != "Unknown") %>% group_by(geog, fy, age_grp_2) %>% summarise(total_referrals = sum(referrals))
)

pds_all_totals_2$age_grp_2<- factor(pds_all_totals_2$age_grp_2, levels = c("All", "65+", "64 and Under"))

pds_ijb_totals_2 <- bind_rows(pds_ijb_totals,
    pds_ijb %>% filter(age_grp_2 != "Unknown") %>% group_by(geog, fy, age_grp_2) %>% summarise(total_referrals = sum(referrals))
)

pds_ijb_totals_2$age_grp_2<- factor(pds_ijb_totals_2$age_grp_2, levels = c("All", "65+", "64 and Under"))


pds_hb_totals_2 <- bind_rows(pds_hb_totals,
    pds_hb %>% filter(age_grp_2 != "Unknown") %>% group_by(geog, fy, age_grp_2) %>% summarise(total_referrals = sum(referrals))
)

pds_hb_totals_2$age_grp_2<- factor(pds_hb_totals_2$age_grp_2, levels = c("All", "65+", "64 and Under"))


pds_scot_totals_2 <- bind_rows(pds_scot_totals,
    pds_scot %>% filter(age_grp_2 != "Unknown") %>% group_by(geog, fy, age_grp_2) %>% summarise(total_referrals = sum(referrals))
)

pds_scot_totals_2$age_grp_2<- factor(pds_scot_totals_2$age_grp_2, levels = c("All", "65+", "64 and Under"))



#create year lists
provisional_year <- paste0(as.numeric(substr(last(finalised_years),1,4)) + 1,
                           "/", as.numeric(substr(last(finalised_years),6,7)) + 1)

current_fy <- paste0(substr(fy,1,4),
                           "/", as.numeric(substr(fy,3,4)) + 1)

last_full_year <- if_else(qt == 4, current_fy, paste0(as.numeric(substr(fy,1,4)) - 1,
                           "/", as.numeric(substr(fy,3,4))))

all_years <- unique(pds_all$fy)

if(qt == 4){full_years = all_years}else{full_years = all_years[-length(all_years)]}


```
<!-- delete all of above when finished testing -->


PDS Pathways
=================================================

```{r data-setup-pathways, include=FALSE}

wait_data <- read_rds(get_mi_data_path("wait_data", ext = "rds", test_output = test_output))

term_data_contact <- read_rds(get_mi_data_path("wait_data_2", ext = "rds", test_output = test_output))

term_data_no_contact <- read_rds(get_mi_data_path("wait_data_3", ext = "rds", test_output = test_output))

wait_data$health_board <- as.factor(wait_data$health_board)
wait_data$fy <- as.factor(wait_data$fy)
wait_data$simd <- as.factor(wait_data$simd)
wait_data$sex <- as.factor(wait_data$sex)
wait_data$ijb <- as.factor(wait_data$ijb)


term_data_contact$health_board <- as.factor(term_data_contact$health_board)
term_data_contact$fy <- as.factor(term_data_contact$fy)
term_data_contact %<>% arrange(termination_or_transition_reason)
term_data_contact$sex <- as.factor(term_data_contact$sex)
term_data_contact$ijb <- factor(term_data_contact$ijb, levels = unique(pds_all$geog))
term_data_contact %<>% mutate(termination_or_transition_reason = if_else(termination_or_transition_reason == "14 All reasons", substring(termination_or_transition_reason, 4), termination_or_transition_reason))
term_data_contact$termination_or_transition_reason <- as.factor(term_data_contact$termination_or_transition_reason)

term_data_no_contact$health_board <- as.factor(term_data_no_contact$health_board)
term_data_no_contact$fy <- as.factor(term_data_no_contact$fy)
term_data_no_contact %<>% arrange(termination_or_transition_reason)
term_data_no_contact$sex <- as.factor(term_data_no_contact$sex)
term_data_no_contact$ijb <- factor(term_data_no_contact$ijb, levels = unique(pds_all$geog))
term_data_no_contact %<>% mutate(termination_or_transition_reason = if_else(termination_or_transition_reason == "14 All reasons", substring(termination_or_transition_reason, 4), termination_or_transition_reason))
term_data_no_contact$termination_or_transition_reason <- as.factor(term_data_no_contact$termination_or_transition_reason)
 
```

Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

### Pathways - Waiting Times
***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

<ul>
  <li>[**Pathways - Waiting Times**](#pds-pathways)</li>
  <li>[Pathways - PDS Outcomes](#outcomes)</li>
  <li>[Pathways - No Contact within 12 Months](#no-contact)</li>
  <li>[Pathways - Termination Reasons](#termination-reasons)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

Row
----------------------------------------------------------------------

### **Note**

**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.**

**Please note:** *Aberdeen City Health & Social Care Partnership changed to provide PDS in 2019 to an inhouse hybrid model. This change in model, and process of receiving referrals and recording, resulted in data quality issues for financial years 2019/20 and 2020/21. This should be taken into account when interpreting figures for Aberdeen City and NHS Grampian.*

Row {.tabset data-height=1070}
----------------------------------------------------------------------

### **Integration Authority Areas**

```{r dropdown-median-ijb}
median_data_ijb <- wait_data %>% 
      filter(sex == "All") %>% 
     filter(ijb != "All", simd == "All") %>% 
      select(ijb, fy, median_diagnosis_to_contact) %>% 
  mutate(median_diagnosis_to_contact = if_else(is.na(median_diagnosis_to_contact)| median_diagnosis_to_contact < 0, 0, median_diagnosis_to_contact)) %>% 
      mutate(ijb = if_else(ijb == "Scotland", "AAA", ijb)) %>%
      arrange(ijb) %>% 
      mutate(ijb = if_else(ijb == "AAA", "Scotland", ijb)) %>% 
    mutate(median_diagnosis_to_contact = if_else(ijb == "Aberdeen City" & fy %in% c("2019/20", "2020/21"), 0, median_diagnosis_to_contact))

median_data_ijb <- left_join(median_data_ijb,
median_data_ijb %>% filter(ijb == "Scotland") %>% select(fy, median_diagnosis_to_contact) %>%  rename(scot_median_diagnosis_to_contact = median_diagnosis_to_contact)) %>% filter(ijb != "Scotland") %>% 
  rename(geog = ijb)

median_data_ijb$geog<- factor(median_data_ijb$geog, levels = c(unique(median_data_ijb$geog)))


median_data_ijb_table <- SharedData$new(median_data_ijb, key = ~fy, group = "median_ijb")

data_filter_median <- filter_select(id = "filter_median",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = median_data_ijb_table,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,5,NA),NULL,
data_filter_median,
NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px">Average (median) days from diagnosis to contact by PDS practitioner by Integration Authority Area</h2>
```{r plot-median-ijb}

bscols(widths = 12,
  div(style = css(width="98%", height="385px", marginBottom="-30px"),
plot_bar_median(median_data_ijb_table))
)

```


```{r table-median-ijb}
median_ijb_table_data <- wait_data %>% 
      filter(sex == "All") %>% 
     filter(ijb != "All", simd == "All") %>% 
      select(ijb, fy, total_referrals, perc_contacted, median_diagnosis_to_contact) %>% 
  mutate(across(starts_with("perc"), ~ paste0(.,"%"))) %>%
    mutate(across(where(is.numeric), ~format(., big.mark = ","))) %>%
      mutate(ijb = if_else(ijb == "Scotland", "AAA", ijb)) %>%
      arrange(ijb) %>% 
      mutate(ijb = if_else(ijb == "AAA", "Scotland", ijb)) %>% 
    mutate(median_diagnosis_to_contact = if_else(ijb == "Aberdeen City" & fy %in% c("2019/20", "2020/21"), "-", median_diagnosis_to_contact)) %>% 
    mutate(perc_contacted = if_else(ijb == "Aberdeen City" & fy %in% c("2019/20", "2020/21"), "-", perc_contacted)) %>%
  rename(`Number of People Referred to PDS` = total_referrals, 
         `% of Referrals contacted by PDS practitioner` = perc_contacted,
        `Average (median) days from diagnosis to first contact` = median_diagnosis_to_contact) %>% 
  pivot_longer(!c(ijb,fy), names_to = "measure", values_to = "n") %>% 
  pivot_wider(names_from = ijb, values_from = n) %>% 
  rename(" " = "measure")

median_ijb_table <- SharedData$new(median_ijb_table_data, key = ~fy, group = "median_ijb")


bscols(widths = 12,
       div(style = css(width="97%", height="460px", margin="20px"),
DT::datatable(median_ijb_table, rownames = FALSE, extensions = "FixedColumns",
              options = list(pageLength = 5,
                             scrollX = TRUE,
                             fixedColumns = list(leftColumns = 1),
                             scrollY = FALSE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0),
                                               list(className = 'dt-right', targets = 2:33)
                                               ))) %>%
           DT::formatStyle(2, fontWeight = "bold", padding = "4px"
                          )
        )
     )



```

### **Health Boards**

```{r dropdown-median-hb}
median_data_hb <- wait_data %>% 
      filter(sex == "All") %>% 
     filter(ijb == "All" | ijb == "Scotland", simd == "All") %>% 
      select(health_board, fy, median_diagnosis_to_contact) %>% 
  mutate(median_diagnosis_to_contact = if_else(is.na(median_diagnosis_to_contact)| median_diagnosis_to_contact < 0, 0, median_diagnosis_to_contact))

median_data_hb <- left_join(median_data_hb,
median_data_hb %>% filter(health_board == "Scotland") %>% select(fy, median_diagnosis_to_contact) %>%  rename(scot_median_diagnosis_to_contact = median_diagnosis_to_contact)) %>% filter(health_board != "Scotland") %>% 
    mutate(median_diagnosis_to_contact = if_else(health_board == "NHS Grampian" & fy %in% c("2019/20", "2020/21"), 0, median_diagnosis_to_contact)) %>% 
  rename(geog = health_board)

median_data_hb$geog<- factor(median_data_hb$geog, levels = c(unique(median_data_hb$geog)))


median_data_hb_table <- SharedData$new(median_data_hb, key = ~fy, group = "median_hb")

data_filter_median_hb <- filter_select(id = "filter_median_hb",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = median_data_hb_table,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,5,NA),NULL,
data_filter_median_hb,
NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px">Average (median) days from diagnosis to contact by PDS practitioner by Health Board</h2>
```{r plot-median-hb}

bscols(widths = 12,
  div(style = css(width="98%", height="385px", marginBottom="-30px"),
plot_bar_median(median_data_hb_table))
)

```


```{r table-median-hb}
median_hb_table_data <- wait_data %>% 
      filter(sex == "All") %>% 
     filter(ijb == "All" | ijb == "Scotland", simd == "All") %>% 
      select(health_board, fy, total_referrals, perc_contacted, median_diagnosis_to_contact) %>% 
  mutate(across(starts_with("perc"), ~ paste0(.,"%"))) %>%
    mutate(across(where(is.numeric), ~format(., big.mark = ","))) %>%
        mutate(median_diagnosis_to_contact = if_else(health_board == "NHS Grampian" & fy %in% c("2019/20", "2020/21"), "-", median_diagnosis_to_contact)) %>% 
    mutate(perc_contacted = if_else(health_board == "NHS Grampian" & fy %in% c("2019/20", "2020/21"), "-", perc_contacted)) %>%
  rename(`Number of People Referred to PDS` = total_referrals, 
         `% of Referrals contacted by PDS practitioner` = perc_contacted,
        `Average (median) days from diagnosis to first contact` = median_diagnosis_to_contact) %>% 
  pivot_longer(!c(health_board,fy), names_to = "measure", values_to = "n") %>% 
  pivot_wider(names_from = health_board, values_from = n) %>% 
  rename(" " = "measure")

median_hb_table <- SharedData$new(median_hb_table_data, key = ~fy, group = "median_hb")


bscols(widths = 12,
       div(style = css(width="97%", height="470px", margin="20px"),
DT::datatable(median_hb_table, rownames = FALSE, extensions = "FixedColumns",
              options = list(pageLength = 5,
                             scrollX = TRUE,
                             fixedColumns = list(leftColumns = 1),
                             scrollY = FALSE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0),
                                               list(className = 'dt-right', targets = 2:16)
                                               ))) %>%
           DT::formatStyle(2, fontWeight = "bold", padding = "4px"
                          )
        )
     )



```

### **Trend**

```{r dropdown-wait-trend}
wait_data_trend_all <- wait_data %>% filter(sex == "All", simd == "All") %>% 
                                     mutate(ijb = if_else(ijb == "All", health_board, ijb)) %>%
                                     rename(geog = ijb) %>% select(geog, fy, median_diagnosis_to_contact) %>% 
  #coding Aberdeen City and NHS Grampian medians as -999 so they do not appear on chart
            mutate(median_diagnosis_to_contact = 
              if_else(geog == "Aberdeen City" & fy %in% c("2019/20", "2020/21"), -999, median_diagnosis_to_contact)) %>% 
            mutate(median_diagnosis_to_contact = 
              if_else(geog == "NHS Grampian" & fy %in% c("2019/20", "2020/21"), -999, median_diagnosis_to_contact)) 
  
wait_data_trend_all$geog<- factor(wait_data_trend_all$geog, levels = unique(pds_all$geog))

wait_data_trend <- SharedData$new(wait_data_trend_all %>% arrange(geog))

data_filter_wait_trend <- filter_select(id = "trend_filter_wait",
                                    label = "Select Integration Authority Area(s) or Health Board(s):",
                                    group = ~geog,
                                    sharedData = wait_data_trend
                                   )
bscols(widths = c(1,10,NA),NULL,
data_filter_wait_trend,NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px">Average (median) days from diagnosis to contact by PDS practitioner</h2>
```{r plot-wait-trend}

 wait_plot_trend <- plot_trend(wait_data_trend, median_diagnosis_to_contact, x ="Financial Year of Diagnosis", y = "Median", colours = phs_colours_46, measure_text = "Average (median) days from diagnosis to first contact: ")

bscols(widths = 12,
        div(style = css(width="98%", height="385px"),
wait_plot_trend)
)
```

```{r table-wait-trend}

wait_data_trend_all %>% arrange(geog) %>% 
            mutate(median_diagnosis_to_contact = as.character(median_diagnosis_to_contact)) %>% 
            mutate(median_diagnosis_to_contact = 
              if_else(geog == "Aberdeen City" & fy %in% c("2019/20", "2020/21"), "\\-", median_diagnosis_to_contact)) %>% 
            mutate(median_diagnosis_to_contact = 
              if_else(geog == "NHS Grampian" & fy %in% c("2019/20", "2020/21"), "\\-", median_diagnosis_to_contact)) %>%             pivot_wider(names_from = fy, values_from = median_diagnosis_to_contact) %>%
            rename(`Integration Authority Area/Health Board` = geog) %>%
            kable(align = c("l", rep("r", length(all_years)))) %>%
            kable_styling(full_width = TRUE) %>%
            column_spec(1, bold = TRUE) %>%
  # Add header above table
            add_header_above(
                    c(" " = 1,
                     "Financial Year of Diagnosis" = length(all_years))) %>%
            scroll_box(height = "470px")

```

### **Waiting Times Breakdown**

```{r dropdown-wait}
wait_data_all <- wait_data %>% 
      filter(sex == "All", simd == "All") %>% 
  mutate(ijb = if_else(ijb == "All", health_board, ijb)) %>% 
  rename(geog = ijb) %>% 
      select(geog, fy, total_referrals, median_diagnosis_to_referral,
             perc_allocated, median_referral_to_allocation,
             perc_contacted, median_allocation_to_contact,
             median_diagnosis_to_contact) %>% 
  mutate(across(starts_with("perc"), ~ paste0(.,"%"))) %>%
  mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
        mutate(across(where(is.numeric), ~format(., big.mark = ","))) %>% 
    mutate(across(starts_with("perc"),
                  ~if_else(geog == "Aberdeen City" & fy %in% c("2019/20", "2020/21"), "-", .))) %>%
    mutate(across(starts_with("median"),
                  ~if_else(geog == "Aberdeen City" & fy %in% c("2019/20", "2020/21"), "-", .))) %>% 
  mutate(across(starts_with("perc"),
                  ~if_else(geog == "NHS Grampian" & fy %in% c("2019/20", "2020/21"), "-", .))) %>%
  mutate(across(starts_with("median"),
                  ~if_else(geog == "NHS Grampian" & fy %in% c("2019/20", "2020/21"), "-", .))) 

wait_data_all$geog<- factor(wait_data_all$geog, levels = unique(pds_all$geog))

   wait_data_all %<>% arrange(geog) %>% set_colnames(c("Integration Authority Area/Health Board", "fy", "Number of People Referred to PDS",  "Average (median) days from diagnosis to PDS referral",
                     "% of Referrals allocated to PDS practitioner", "Average (median) days from referral to allocation of PDS practitioner", 
                     "% of Referrals contacted by PDS practitioner",  "Average (median) days from allocation to first contact with PDS practitioner",
                     "Average (median) days from diagnosis to first contact"
      )) 



wait_table_data_all <- SharedData$new(wait_data_all)

data_filter_all_year <- filter_select(id = "wait_filter_all_year",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = wait_table_data_all,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,4,NA), NULL,
data_filter_all_year, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: -20px"> Pathways from diagnosis to contact by PDS practitioner </h2>
```{r wait-table-all}
bscols(widths = 12,
       div(style = css(width="97%", height="785px", margin="20px"),
    DT::datatable(wait_table_data_all, rownames = FALSE,  
                                        caption = htmltools::tags$caption(
                       style = 'caption-side: bottom; text-align: left;',
                       "A dash (-) indicates insufficient data for this measure to be calculated."),
                       options = list(pageLength = 46,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:8)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(1, fontWeight = "bold",
                           ) %>%
           DT::formatStyle(9, fontWeight = "bold",
                           backgroundColor = "#E1C7DF"
                          )
        )
     )

  

```

Outcomes {.hidden}
=================================================

```{r add-percentage-function, include=FALSE}

add_percent <- function(df, value, name) {
  
 data <- df %>%  mutate(perc =  if_else(total == 0, "-",
    paste0(round(100*{{value}}/total,1), "%")))
  
colnames(data)[colnames(data) == 'perc'] <- name

return(data)
  
}

```

Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

### Pathways - PDS Outcomes
***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

<ul>
  <li>[Pathways - Waiting Times](#pds-pathways)</li>
  <li>[**Pathways - PDS Outcomes**](#outcomes)</li>
  <li>[Pathways - No Contact within 12 Months](#no-contact)</li>
  <li>[Pathways - Termination Reasons](#termination-reasons)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

Row
----------------------------------------------------------------------

### **Note**

**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.**

**Please note:** *Aberdeen City Health & Social Care Partnership changed to provide PDS in 2019 to an inhouse hybrid model. This change in model, and process of receiving referrals and recording, resulted in data quality issues for financial years 2019/20 and 2020/21. This should be taken into account when interpreting figures for Aberdeen City and NHS Grampian.*

Row {.tabset data-height=780}
----------------------------------------------------------------------

### **Standard Met**

```{r dropdown-met}
met_data <- pds_all %>% filter(ldp == "complete", fy %in% full_years) %>% group_by(geog, fy, ldp_full) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ldp_full = substring(ldp_full, 12)) %>%   pivot_wider(names_from = ldp_full, values_from = referrals) %>%
   mutate(total = rowSums(across(where(is.numeric))), .after = fy) %>% 
mutate(`% Standard Met with termination date` = if_else(total == 0, "-",
  paste0(round(100*`PDS ended`/total,1), "%")), .after = `PDS ended`) %>% 
mutate(`% Standard Met without termination date` = if_else(total == 0, "-",
  paste0(round(100*`Without termination date`/total,1), "%")), .after = `Without termination date`) %>% 
  select(-`PDS ended`, -`Without termination date`)

met_data_totals <- left_join(pds_all_totals %>% 
                               select(-age_grp_2) %>% filter(fy %in% full_years), met_data) %>% 
  #mutate(`% of Total referrals Standard Met` = paste0(round(100*total/total_referrals,1), "%"),
                                              #.after = total_referrals) %>% 
  rename(`Integration Authority Area/Health Board` = geog, 
         `Total referrals` = total_referrals,
         `Standard Met` = total) %>% mutate(across(where(is.numeric), ~format(., big.mark = ","))) 
  

met_table_data <- SharedData$new(met_data_totals)

 data_filter_met_year <- filter_select(id = "met_filter_year",
                                     label = "Select Financial Year of Diagnosis:",
                                     group = ~fy,
                                     sharedData = met_table_data,
                                    multiple = FALSE
                                    )

 bscols(widths = c(1,4,NA), NULL,
 data_filter_met_year, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: -20px">Individuals who received a minimum of one year’s PDS (Standard Met)</h2>
```{r met-table}
bscols(widths = 12,
       div(style = css(width="97%", height="585px", margin="20px"),
    DT::datatable(met_table_data, rownames = FALSE,
                                       # caption = htmltools::tags$caption(
                      # style = 'caption-side: bottom; text-align: left;',
                      # "A dash (-) indicates no dates of referral were submitted for diagnoses in this
                        #      year."),
                       options = list(pageLength = 46,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:5)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(1, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )


```

### **Standard Not Met**

```{r dropdown-not-met}
not_met_data <- pds_all %>% filter(ldp == "fail") %>% group_by(geog, fy, ldp_full) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ldp_full = substring(ldp_full, 8)) %>% 
  pivot_wider(names_from = ldp_full, values_from = referrals) %>%
    mutate(total = rowSums(across(where(is.numeric))), .after = fy) %>% 
   add_percent(`PDS terminated before first contact`, "% PDS terminated without contact") %>% 
 add_percent(`PDS not started and more than 12 months since diagnosis`, "% PDS not started and more than 12 months since diagnosis") %>% 
  add_percent(`PDS started more than 12 months after diagnosis`, "% PDS started more than 12 months after diagnosis") %>% 
  add_percent(`PDS terminated less than 11 months after first contact`, "% PDS terminated less than 11 months after first contact") %>% 
  select(-starts_with("PDS"))

not_met_data_totals <- left_join(pds_all_totals %>% 
                               select(-age_grp_2), not_met_data) %>% 
    #mutate(`% of Total referrals Standard Not Met` = paste0(round(100*total/total_referrals,1), "%"),
                                          #    .after = total_referrals) %>% 
  rename(`Integration Authority Area/Health Board` = geog, 
         `Total referrals` = total_referrals,
         `Standard Not Met` = total) %>% mutate(across(where(is.numeric), ~format(., big.mark = ","))) 

not_met_table_data <- SharedData$new(not_met_data_totals)

 data_filter_not_met_year <- filter_select(id = "not_met_filter_year",
                                     label = "Select Financial Year of Diagnosis:",
                                     group = ~fy,
                                     sharedData = not_met_table_data,
                                    multiple = FALSE
                                    )

 bscols(widths = c(1,4,NA), NULL,
 data_filter_not_met_year, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: -20px">Individuals who did not receive a minimum of one year’s PDS (Standard Not Met)</h2>
```{r not-met-table}

bscols(widths = 12,
       div(style = css(width="97%", height="585px", margin="20px"),
    DT::datatable(not_met_table_data, rownames = FALSE,
                                       # caption = htmltools::tags$caption(
                      # style = 'caption-side: bottom; text-align: left;',
                      # "A dash (-) indicates no dates of referral were submitted for diagnoses in this
                        #      year."),
                       options = list(pageLength = 46,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:7)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(1, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )


```

### **PDS Ongoing**

```{r dropdown-ongoing}
ongoing_data <- pds_all %>% filter(ldp == "ongoing") %>% group_by(geog, fy, ldp_full) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ldp_full = substring(ldp_full, 11)) %>%   pivot_wider(names_from = ldp_full, values_from = referrals) %>%
   mutate(total = rowSums(across(where(is.numeric))), .after = fy) %>% 
   add_percent(`PDS not started and less than 12 months since diagnosis`, "% PDS not yet started and less than 12 months since diagnosis") %>% 
 add_percent(`Still receiving PDS and less than 12 months since first contact`, "% Still receiving PDS and less than 12 months since first contact") %>% 
  select(-starts_with("PDS"), -starts_with("Still"))

ongoing_data_totals <- left_join(pds_all_totals %>% 
                               select(-age_grp_2), ongoing_data) %>% 
   mutate(`% of Total referrals PDS Ongoing` = paste0(round(100*total/total_referrals,1), "%"),
                                              .after = total_referrals) %>% 
  filter(!fy %in% finalised_years) %>% 
  rename(`Integration Authority Area/Health Board` = geog, 
         `Total referrals` = total_referrals,
         `PDS Ongoing` = total) %>% mutate(across(where(is.numeric), ~format(., big.mark = ","))) 

ongoing_table_data <- SharedData$new(ongoing_data_totals)

 data_filter_ongoing_year <- filter_select(id = "ongoing_filter_year",
                                     label = "Select Financial Year of Diagnosis:",
                                     group = ~fy,
                                     sharedData = ongoing_table_data,
                                    multiple = FALSE
                                    )

 bscols(widths = c(1,4,NA), NULL,
 data_filter_ongoing_year, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: -20px">Individuals where LDP Standard cannot yet be determined (PDS Ongoing)</h2>
```{r ongoing-table}

bscols(widths = 12,
       div(style = css(width="97%", height="585px", margin="20px"),
    DT::datatable(ongoing_table_data, rownames = FALSE,
                                       # caption = htmltools::tags$caption(
                      # style = 'caption-side: bottom; text-align: left;',
                      # "A dash (-) indicates no dates of referral were submitted for diagnoses in this
                        #      year."),
                       options = list(pageLength = 46,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:6)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(1, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )


```

### **Exempt**

```{r dropdown-exempt}
exempt_data <- pds_all %>% filter(ldp == "exempt") %>% group_by(geog, fy, ldp_full) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ldp_full = substring(ldp_full, 10)) %>%   pivot_wider(names_from = ldp_full, values_from = referrals) %>%
   mutate(total = rowSums(across(where(is.numeric))), .after = fy) %>% 
   add_percent(`03 Service user has died`, "% 03 Service user has died") %>% 
 add_percent(`04 Service user has moved to a different Health Board area`, "% 04 Service user has moved to a different Health Board area") %>% 
  add_percent(`05 Service user has terminated PDS early/refused`, "% 05 Service user has terminated PDS early/refused") %>% 
  add_percent(`06 Service user no longer able to engage in PDS`, "% 06 Service user no longer able to engage in PDS") %>% 
  select(-starts_with("0"))

exempt_data_totals <- left_join(pds_all_totals %>% 
                               select(-age_grp_2), exempt_data) %>% 
   mutate(`% of Total referrals Exempt` = paste0(round(100*total/total_referrals,1), "%"),
                                              .after = total_referrals) %>% 
  rename(`Integration Authority Area/Health Board` = geog, 
         `Total referrals` = total_referrals,
         `Number of referrals Exempt` = total) %>% mutate(across(where(is.numeric), ~format(., big.mark = ","))) 

exempt_table_data <- SharedData$new(exempt_data_totals)

 data_filter_exempt_year <- filter_select(id = "exempt_filter_year",
                                     label = "Select Financial Year of Diagnosis:",
                                     group = ~fy,
                                     sharedData = exempt_table_data,
                                    multiple = FALSE
                                    )

 bscols(widths = c(1,4,NA), NULL,
 data_filter_exempt_year, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: -20px">Individuals exempt from LDP Standard</h2>
```{r exempt-table}

bscols(widths = 12,
       div(style = css(width="97%", height="585px", margin="20px"),
    DT::datatable(exempt_table_data, rownames = FALSE,
                                       # caption = htmltools::tags$caption(
                      # style = 'caption-side: bottom; text-align: left;',
                      # "A dash (-) indicates no dates of referral were submitted for diagnoses in this
                        #      year."),
                       options = list(pageLength = 46,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:8)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(1, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )


```

No Contact {.hidden}
=================================================
Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

### Pathways - No Contact within 12 Months
***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

<ul>
  <li>[Pathways - Waiting Times](#pds-pathways)</li>
  <li>[Pathways - PDS Outcomes](#outcomes)</li>
  <li>[**Pathways - No Contact within 12 Months**](#no-contact)</li>
  <li>[Pathways - Termination Reasons](#termination-reasons)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

Row
----------------------------------------------------------------------

### **Note**

**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.**

**Please note:** *Aberdeen City Health & Social Care Partnership changed to provide PDS in 2019 to an inhouse hybrid model. This change in model, and process of receiving referrals and recording, resulted in data quality issues for financial years 2019/20 and 2020/21. This should be taken into account when interpreting figures for Aberdeen City and NHS Grampian.*

Row {.tabset data-height=670}
----------------------------------------------------------------------

### **Integration Authority Areas**

```{r dropdown-no-contact-ijb}

no_contact_term_ijb <- term_data_no_contact %>%  
    filter(sex == "All", termination_or_transition_reason == "All reasons", ldp == "All") %>%
    filter(!grepl("NHS", ijb)) %>% 
    pivot_wider(names_from = ldp, values_from = c(referrals, median_referral_to_termination)) %>%
    select(fy, ijb,
           referrals_All) %>% rename(referrals_no_contact_term = referrals_All)
    
totals_ijb <- wait_data %>% filter(sex == "All", simd == "All", ijb != "All" | ijb == "Scotland") %>% select(ijb, fy, total_referrals)

no_contact_12_ijb <- pds_all %>% filter(!grepl("NHS", geog), ldp_full == "fail - PDS not started and more than 12 months since diagnosis" | ldp_full == "fail - PDS started more than 12 months after diagnosis") %>% 
   group_by(fy, geog) %>% summarise(referrals_no_contact_12 = sum(referrals)) %>% rename(ijb = geog)
 
ijb_totals_12 <- left_join(totals_ijb, no_contact_12_ijb)

no_contact_ijb <- left_join(ijb_totals_12, no_contact_term_ijb) %>% 
  mutate(across(starts_with("referrals"), ~ replace(., is.na(.), 0))) %>%
    mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
     mutate(perc_no_contact_term = paste0(round((referrals_no_contact_term/total_referrals)*100,1),"%")) %>% 
   mutate(perc_no_contact_12 = paste0(round((referrals_no_contact_12/total_referrals)*100,1),"%")) %>% 
  select(fy, ijb,
         total_referrals,
         perc_no_contact_12, referrals_no_contact_12,
         perc_no_contact_term, referrals_no_contact_term) %>% 
    mutate(ijb = if_else(ijb == "Scotland", "AAA", ijb)) %>% arrange(ijb) %>%
    mutate(ijb = if_else(ijb == "AAA", "Scotland", ijb)) %>% 
    mutate(across(where(is.numeric), ~format(., big.mark = ","))) %>% 
   mutate(across(starts_with("%"),
                  ~if_else(ijb == "Aberdeen City" & fy %in% c("2019/20", "2020/21"), "-", .))) %>%
   mutate(across(starts_with("referrals"),
                  ~if_else(ijb == "Aberdeen City" & fy %in% c("2019/20", "2020/21"), "-", .))) %>% 
    set_colnames(c("fy", "Integration Authority Area", "Number of People Referred to PDS",
                   "% of total referrals not contacted within 12 months of diagnosis",
                   "Number of referrals not contacted within 12 months of diagnosis",
                   "% of total referrals whose PDS ended with no contact",
                   "Number of referrals whose PDS ended with no contact"))
    

no_contact_table_data_ijb <- SharedData$new(no_contact_ijb)

data_filter_year_no_contact_ijb <- filter_select(id = "no_contact_filter_year_ijb",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = no_contact_table_data_ijb,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,4,NA), NULL,
data_filter_year_no_contact_ijb, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: -20px">Individuals referred to PDS not contacted within 12 months of diagnosis</h2>
```{r no-contact-table-ijb}

bscols(widths = 12,
       div(style = css(width="97%", height="500px", margin="20px"),
     DT::datatable(no_contact_table_data_ijb, rownames = FALSE, caption = htmltools::tags$caption(
                       style = 'caption-side: bottom; text-align: left;',
                       "A dash (-) indicates insufficient data for this measure to be calculated. Referrals not contacted within 12 months of diagnosis includes records with no contact date and those with a contact date more than 12 months after diagnosis."),
              options = list(pageLength = 33,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0),
                                                list(className = 'dt-right', targets = 2:6)
                                                #list(width = '30px', targets = 6)
                                                ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          ) %>% 
       DT::formatStyle(5, `border-right` = "solid 1px")
        )
     )

```

### **Health Boards**

```{r dropdown-no-contact-hb}

no_contact_term_hb <- term_data_no_contact %>%  
    filter(sex == "All", termination_or_transition_reason == "All reasons", ldp == "All") %>%
    filter(health_board == "Scotland" | grepl("NHS", health_board)) %>% 
    pivot_wider(names_from = ldp, values_from = c(referrals, median_referral_to_termination)) %>%
    select(fy, health_board,
           referrals_All) %>% rename(referrals_no_contact_term = referrals_All)
    
totals_hb <- wait_data %>% filter(sex == "All", simd == "All", ijb == "All" | ijb == "Scotland") %>% select(health_board, fy, total_referrals)

no_contact_12_hb <- pds_all %>% filter(geog == "Scotland" | grepl("NHS", geog), ldp_full == "fail - PDS not started and more than 12 months since diagnosis" | ldp_full == "fail - PDS started more than 12 months after diagnosis") %>% 
   group_by(fy, geog) %>% summarise(referrals_no_contact_12 = sum(referrals)) %>% rename(health_board = geog)
 
hb_totals_12 <- left_join(totals_hb, no_contact_12_hb)

no_contact_hb <- left_join(hb_totals_12, no_contact_term_hb) %>% 
  mutate(across(starts_with("referrals"), ~ replace(., is.na(.), 0))) %>%
    mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
     mutate(perc_no_contact_term = paste0(round((referrals_no_contact_term/total_referrals)*100,1),"%")) %>% 
   mutate(perc_no_contact_12 = paste0(round((referrals_no_contact_12/total_referrals)*100,1),"%")) %>% 
  select(fy, health_board,
         total_referrals,
         perc_no_contact_12, referrals_no_contact_12,
         perc_no_contact_term, referrals_no_contact_term) %>% 
     mutate(across(where(is.numeric), ~format(., big.mark = ","))) %>% 
   mutate(across(starts_with("%"),
                  ~if_else(health_board == "NHS Grampian" & fy %in% c("2019/20", "2020/21"), "-", .))) %>%
   mutate(across(starts_with("referrals"),
                  ~if_else(health_board == "NHS Grampian" & fy %in% c("2019/20", "2020/21"), "-", .))) %>% 
    set_colnames(c("fy", "Health Board", "Number of People Referred to PDS",
                   "% of total referrals not contacted within 12 months of diagnosis",
                   "Number of referrals not contacted within 12 months of diagnosis",
                   "% of total referrals whose PDS ended with no contact",
                   "Number of referrals whose PDS ended with no contact"))
    
no_contact_table_data_hb <- SharedData$new(no_contact_hb)

data_filter_year_no_contact_hb <- filter_select(id = "no_contact_filter_year_hb",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = no_contact_table_data_hb,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,4,NA), NULL,
data_filter_year_no_contact_hb, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: -20px">Individuals referred to post-diagnostic support with no contact by PDS practitioner</h2>
```{r no-contact-table-hb}
bscols(widths = 12,
       div(style = css(width="97%", height="500px", margin="20px"),
     DT::datatable(no_contact_table_data_hb, rownames = FALSE, caption = htmltools::tags$caption(
                       style = 'caption-side: bottom; text-align: left;',
                       "A dash (-) indicates insufficient data for this measure to be calculated. Referrals not contacted within 12 months of diagnosis includes records with no contact date and those with a contact date more than 12 months after diagnosis."),
              options = list(pageLength = 15,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0),
                                                list(className = 'dt-right', targets = 2:6)
                                                #list(width = '30px', targets = 6)
                                                ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          ) %>% 
       DT::formatStyle(5, `border-right` = "solid 1px")
        )
     )

```

Termination Reasons {.hidden}
=================================================
Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

### Pathways - Termination Reasons
***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

<ul>
  <li>[Pathways - Waiting Times](#pds-pathways)</li>
  <li>[Pathways - PDS Outcomes](#outcomes)</li>
  <li>[Pathways - No Contact within 12 Months](#no-contact)</li>
  <li>[**Pathways - Termination Reasons**](#termination-reasons)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

Row
----------------------------------------------------------------------

### **Note**

**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.**

**Please note:** *Aberdeen City Health & Social Care Partnership changed to provide PDS in 2019 to an inhouse hybrid model. This change in model, and process of receiving referrals and recording, resulted in data quality issues for financial years 2019/20 and 2020/21. This should be taken into account when interpreting figures for Aberdeen City and NHS Grampian.*

Row {.tabset data-height=770}
----------------------------------------------------------------------

### **Termination Reasons - All**

```{r dropdown-term-all}
 term_data_all <- full_join(
   
  term_data_contact %>% filter(sex == "All", ldp == "All") %>% select(-sex,-ldp,-median_contact_to_termination) %>% rename(contact_referrals = referrals),
  
  term_data_no_contact %>% filter(sex == "All", ldp == "All") %>% select(-sex,-ldp,-median_referral_to_termination) %>% rename(no_contact_referrals = referrals)
 ) %>% 
   mutate(across(where(is.numeric),  ~replace(., is.na(.), 0))) %>% 
  mutate(referrals = contact_referrals + no_contact_referrals) %>% select(-contact_referrals, -no_contact_referrals, -health_board)

# term_totals <- left_join(pds_all_totals %>% rename(ijb = geog) %>% select(-age_grp_2), term_data_all %>% filter(termination_or_transition_reason == "All reasons") %>% select(ijb, fy, referrals) %>% rename(all_terminated_referrals = referrals)) %>%
#   mutate(total_referrals = format(total_referrals, big.mark = ","))

term_table_totals <- bind_rows(term_data_all %>%
                              mutate(termination_or_transition_reason = if_else(termination_or_transition_reason == "All reasons", "00 All reasons", termination_or_transition_reason)),
                            pds_all_totals %>% rename(ijb = geog, termination_or_transition_reason = age_grp_2, referrals = total_referrals) %>% mutate(termination_or_transition_reason = "00 AAA")) %>% 
  arrange(termination_or_transition_reason, fy, ijb) %>% 
  complete(nesting(ijb, fy), termination_or_transition_reason, fill = list(referrals = 0))

term_table_all <- left_join(term_table_totals,
                term_table_totals %>% filter(termination_or_transition_reason == "00 All reasons") %>%  select(ijb, fy, referrals) %>% rename(term_referrals = referrals)) %>% 
  mutate(perc = case_when(termination_or_transition_reason == "00 AAA" ~format(referrals, big.mark = ","),
                 termination_or_transition_reason == "00 All reasons" ~format(referrals, big.mark = ","),
                 term_referrals == 0 ~paste0("-"),
                      TRUE ~paste0(round((referrals/term_referrals)*100,1),"%"))) %>% 
  select(-referrals, -term_referrals) %>% 
  pivot_wider(names_from = ijb, values_from = perc) %>% 
  mutate(termination_or_transition_reason = case_when(termination_or_transition_reason == "00 AAA" ~"Number of people referred to PDS",
                 termination_or_transition_reason == "00 All reasons" ~"Number of referrals with termination date recorded",
                 TRUE ~ termination_or_transition_reason)) %>% 
           rename(" " = termination_or_transition_reason)

                    
# term_table_all <- full_join(term_totals, term_data_all) %>% 
#    mutate(all_terminated_referrals = if_else(is.na(all_terminated_referrals), 0, 
#                                              all_terminated_referrals)) %>% 
#      mutate(termination_or_transition_reason = if_else(is.na(termination_or_transition_reason), "All reasons",
#                                                        termination_or_transition_reason)) %>% 
#      mutate(referrals = if_else(is.na(referrals), 0, referrals)) %>% 
#    mutate(perc = if_else(termination_or_transition_reason == "All reasons", format(referrals, big.mark = ","),
#                          paste0(round((referrals/all_terminated_referrals)*100,1),"%"))) %>% 
#  
#   select(-referrals, -all_terminated_referrals) %>% 
#   pivot_wider(names_from = termination_or_transition_reason, values_from = perc, values_fill = "0%") %>% 
#   relocate(`All reasons`, .after = total_referrals) %>% arrange(ijb) %>% 
#   mutate(across(starts_with("0"), ~if_else(`All reasons` == "0", "-", .))) %>% 
#    mutate(across(starts_with("11"), ~if_else(`All reasons` == "0", "-", .))) %>% 
#    mutate(across(starts_with("13"), ~if_else(`All reasons` == "0", "-", .))) %>% 
#   rename("Number of referrals with termination date recorded" = "All reasons",
#          "Number of people referred to PDS" = "total_referrals",
#          "Integration Authority Area/Health Board" = "ijb")



term_table_data_all <- SharedData$new(term_table_all)

data_filter_year_term_all <- filter_select(id = "term_filter_year",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = term_table_data_all,
                                    multiple = FALSE
                                   )


bscols(widths = c(1,5,NA), NULL,
data_filter_year_term_all,NULL)



```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: -20px">Reasons for termination of post-diagnostic support as percentage of referrals with termination date recorded</h2>
```{r term-table-all}

# headers_term <- htmltools::withTags(table(
#   class = 'display',
#   thead(
#     tr( 
#       th(rowspan = 2, "Integration Authority Area/Health Board"),
#       th(rowspan = 2, ""),
#       th(rowspan = 2, "Number of people referred to PDS"),
#       th(rowspan = 2, "Number of referrals with termination date recorded"),
#       th(colspan = 3, " "),
#       th(colspan = 8, "Termination reason as % of referrals with termination date recorded")
#     ),
#     tr(
#       
#       th(colspan = 1, '01 PDS Complete and have moved to self management'),
#       th(colspan = 1, '02 PDS Complete and have progressed onto more advanced model of care'),
#       th(colspan = 1, '03 Service user has died'),
#       th(colspan = 1, '04 Service user has moved to a different Health Board area'),
#       th(colspan = 1, '05 Service user has terminated PDS early/refused'),
#       th(colspan = 1, '06 Service user no longer able to engage in PDS'),
#       th(colspan = 1, '07 Service user has moved into care'),
#       th(colspan = 1, '08 Other models of care deemed more appropriate'),
#       th(colspan = 1, '09 Transition to community support'),
#       th(colspan = 1, '11 Other Service Reasons'),
#       th(colspan = 1, '13 Unknown Reason')
#     )
#   )
# ))





bscols(widths = 12,
       div(style = css(width="97%", height="590px", margin="20px"),
     DT::datatable(term_table_data_all, #container = headers_term, 
                   rownames = FALSE, extensions = "FixedColumns",
              options = list(pageLength = 13,
                             scrollX = TRUE,
                             fixedColumns = list(leftColumns = 1),
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0),
                                                list(className = 'dt-right', targets = 2:47)
                                                #list(width = '30px', targets = 6)
                                                ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```


### **Termination Reasons - PDS Ending Without Contact**

```{r dropdown-term-1}
 term_data_1 <- term_data_no_contact %>%
    filter(sex == "All") %>%
    pivot_wider(names_from = ldp, values_from = c(referrals, median_referral_to_termination)) %>%
    mutate(across(starts_with("referrals"), ~ replace(., is.na(.), 0))) %>%
    mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>%
    select(fy, ijb, termination_or_transition_reason,
           referrals_All, 
           median_referral_to_termination_All,
           referrals_exempt,
           referrals_fail) %>%
  mutate(across(where(is.numeric), ~format(., big.mark = ","))) %>% 
  mutate(referrals_exempt = case_when(
    termination_or_transition_reason != "All reasons" & referrals_exempt != "  0" ~"\U2713",
    termination_or_transition_reason != "All reasons" & referrals_exempt == "  0" ~" ",
                   TRUE ~referrals_exempt)) %>% 
   mutate(referrals_fail = case_when(
    termination_or_transition_reason != "All reasons" & referrals_fail != "  0" ~"\U2713",
    termination_or_transition_reason != "All reasons" & referrals_fail == "  0" ~" ",
                   TRUE ~referrals_fail)) %>%
    set_colnames(c("fy", "geog", "Reason for termination of post-diagnostic support",
                   "Number of people", 
                   "Average (median) days from referral to termination of PDS",
                   "Exempt from Standard",
                   "Standard Not Met"))


term_table_data_1 <- SharedData$new(term_data_1)

data_filter_year_term_1 <- filter_select(id = "term_filter_year_2",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = term_table_data_1,
                                    multiple = FALSE
                                   )

data_filter_geog_term_1 <- filter_select(id = "term_filter_geog_2",
                                    label = "Select Integration Authority Area or Health Board:",
                                    group = ~geog,
                                    allLevels = TRUE,
                                    sharedData = term_table_data_1,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,5,5,NA), NULL,
data_filter_year_term_1, data_filter_geog_term_1, NULL)



```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: -20px">Pathways from referral to termination of post-diagnostic support without contact</h2>
```{r term-table-1}

bscols(widths = 12,
       div(style = css(width="97%", height="590px", margin="20px"),
     DT::datatable(term_table_data_1, rownames = FALSE,
              options = list(pageLength = 14,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0:1),
                                                list(className = 'dt-right', targets = 3:6)
                                                #list(width = '30px', targets = 6)
                                                ))) %>%
           DT::formatStyle(3, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```

### **Termination Reasons - PDS Ending On or After Contact**

```{r dropdown-term-2}
 term_data <- term_data_contact %>% 
    filter(sex == "All") %>% 
    pivot_wider(names_from = ldp, values_from = c(referrals, median_contact_to_termination)) %>% 
    mutate(across(starts_with("referrals"), ~ replace(., is.na(.), 0))) %>% 
    mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
    select(fy, ijb, termination_or_transition_reason,
           referrals_All,
           median_contact_to_termination_All,
           referrals_complete,
           referrals_exempt,
           referrals_fail) %>% 
    mutate(across(where(is.numeric), ~format(., big.mark = ","))) %>%  
    set_colnames(c("fy", "geog", "Reason for end of post-diagnostic support",
                   "Number of people", 
                   "Average (median) days from first contact to end of PDS",
                   "Standard Met",
                   "Exempt from Standard",
                   "Standard Not Met"))
 
term_table_data <- SharedData$new(term_data)

data_filter_year_term <- filter_select(id = "term_filter_year_3",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = term_table_data,
                                    multiple = FALSE
                                   )

data_filter_geog_term <- filter_select(id = "term_filter_geog_3",
                                    label = "Select Integration Authority Area or Health Board:",
                                    group = ~geog,
                                    sharedData = term_table_data,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,5,5,NA), NULL,
data_filter_year_term, data_filter_geog_term, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: -20px"> Pathways from contact by PDS practitioner to end of post-diagnostic support </h2>
```{r term-table-2}

bscols(widths = 12,
       div(style = css(width="97%", height="590px", margin="20px"),
     DT::datatable(term_table_data, rownames = FALSE,
              options = list(pageLength = 14,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0:1),
                                                list(className = 'dt-right', targets = 3:7)#,
                                                #list(width = '10px', targets = 6)
                                                ))) %>%
           DT::formatStyle(3, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```


```{js }

function filter_default() {

  document.getElementById("met_filter_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("met_filter_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("not_met_filter_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("not_met_filter_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("ongoing_filter_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("ongoing_filter_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("exempt_filter_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("exempt_filter_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("wait_filter_all_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("wait_filter_all_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("filter_median").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("filter_median").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("filter_median_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("filter_median_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("trend_filter_wait").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("trend_filter_wait").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("no_contact_filter_year_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("no_contact_filter_year_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("no_contact_filter_year_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("no_contact_filter_year_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("term_filter_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_year_3").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("term_filter_year_3").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_geog_3").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("term_filter_geog_3").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_year_2").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("term_filter_year_2").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_geog_2").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("term_filter_geog_2").getElementsByClassName("selectized")
  [0].selectize.removeOption("");

 
  }
  
  $(document).ready(filter_default);

```
