---
title: "TRENDS DRAFT"
output: 
  flexdashboard::flex_dashboard:
    logo: phs-logo.png
    orientation: rows
    vertical_layout: scroll
---

```{r load-setup, include=FALSE}
source(here::here("code", "00_setup-environment.R"))
library(crosstalk) # for drop down menus

# Write numbers with thousands separator
knit_hooks$set(inline = function(x){
  if(!is.character(x)){prettyNum(x, big.mark=",")}else{x}
})
```

---
date: "`r paste('Data as at', format(end_date, '%d %B %Y'))`"
---

```{r setup, include=FALSE}

# Remove tidylog
detach("package:tidylog", unload = TRUE)

# Load functions
walk(dir(here::here("functions"), full.names = TRUE), source)

# Load PDS data
pds <- read_rds(get_mi_data_path("final_data", ext = "rds", test_output = test_output)) %>% 
  
  # Remove codes from board and IJB
  mutate(health_board = str_sub(health_board, 3, -1),
         ijb          = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))

# Load expected diagnoses reference file
exp <- read_csv(get_exp_diagnoses_path())


# Load error summary
err <- read_rds(get_mi_data_path("error_data", ext = "rds", test_output = test_output)) %>% 

  mutate(ijb = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))
```
<!-- delete all of above when finished tetsing -->

Trends
=================================================

```{r data setup, include=FALSE}
# to be automated based on whether current year is complete or not??
#included_years <- c("2016/17", "2017/18", "2018/19", "2019/20", "2020/21", "2021/22", "2022/23", "2023/24")

#prepare data for plot_yearly_referrals() function
pds_ijb <- pds %>% arrange(ijb)

pds_scot <- pds %>% group_by(health_board = "Scotland", ijb = "Scotland", fy, month, ldp, age_grp, simd) %>% 
  summarise(referrals = sum(referrals), .groups = "drop")

pds_hb <- pds %>% group_by(health_board, fy, month, ldp, age_grp, simd) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ijb = health_board, .before = fy)

pds_all <- bind_rows(pds_scot, pds_hb, pds_ijb)

pds_all$ijb <- factor(pds_all$ijb, levels = unique(pds_all$ijb))

pds_all %<>% group_by(ijb, fy) %>% summarise(total_referrals = sum(referrals))

# assigns data to filter_select in sidebar
pds_trends_data <- SharedData$new(pds_all)
   
 
```


Sidebar {.sidebar}
-----------------------------------------------------------------------

### 

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

```{r dropdown}
data_filter_hb_ijb <- filter_select(id = "trend_filter",
                                    label = "Select Health Board or Integration Authority Area:",
                                    group = ~ijb,
                                    sharedData = pds_trends_data
                                   )
data_filter_hb_ijb

```

```{js}
function filter_default() {
    document.getElementById("trend_filter").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("trend_filter").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  }
  
  window.onload = filter_default;

```

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)


Row
----------------------------------------------------------------------

### **Note**

**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.**


Row {.data-height=1000}
----------------------------------------------------------------------

### **Number of Individuals referred to Post-Diagnostic Support by Financial Year** {data-width=800}

```{r trend-plot}

trends_plot <- plot_yearly_referrals(pds_trends_data)
trends_plot

```


Row {.tabset data-height=750}
----------------------------------------------------------------------

### **Scotland/Health Board - Number of Individuals referred to Post-Diagnostic Support by Financial Year**

```{r trend-table-hb}

pds_all %>% filter(ijb == "Scotland" | grepl("NHS", ijb)) %>% 
            mutate(total_referrals = format(total_referrals, big.mark = ",")) %>% 
            pivot_wider(names_from = fy, values_from = total_referrals) %>%
            rename(`Health Board` = ijb) %>%
            kable() %>%
            kable_styling(full_width = FALSE) %>%
            column_spec(1, bold = TRUE) %>%
  # Add header above table 
            add_header_above(
                    c(" " = 1,
                     "Financial Year of Diagnosis" = 9)) 

```

### **Scotland/Integration Authority Area - Number of Individuals referred to Post-Diagnostic Support by Financial Year**

```{r trend-table-ijb}

pds_all %>% filter(ijb == "Scotland" | !grepl("NHS", ijb)) %>% 
            mutate(total_referrals = format(total_referrals, big.mark = ",")) %>% 
            pivot_wider(names_from = fy, values_from = total_referrals) %>% 
            rename(`Integration Authority Area` = ijb) %>%
            kable() %>%
            kable_styling(full_width = FALSE) %>%
            column_spec(1, bold = TRUE) %>%
  # Add header above table 
            add_header_above(
                       c(" " = 1,
                         "Financial Year of Diagnosis" = 9)) %>%
            scroll_box(height = "740px")
 

```

