`r if_else(max_fy == sel_fy, paste0(hb, '{data-navmenu="Health Boards"}'), paste0(hb, " ", str_replace(sel_fy, "/", ""), ' {.hidden}'))`
=================================================

```{r summary figures, include=FALSE}

# Expected vs Referrals
ref <- sum(subpage_data$referrals)
exp_rate <- (ref / exp) * 100

# 12 Months Complete
num <- subpage_data %>% filter(ldp %in% c("complete", "exempt")) %>% {sum(.$referrals)}
den <- subpage_data %>% filter(ldp %in% c("complete", "exempt", "fail")) %>% {sum(.$referrals)}
pds_rate <- (num / den) * 100

# Is there data for all four quarters of the selected year?
complete_year <- if_else(max_fy == sel_fy & qt != 4, FALSE, TRUE)

# Format figures with thousands separator
ref_format <- format(ref, big.mark = ",")
exp_format <- format(exp, big.mark = ",")
num_format <- format(num, big.mark = ",")
den_format <- format(den, big.mark = ",")
```

Sidebar {.sidebar}
-----------------------------------------------------------------------

### `r hb`
#### Financial Year `r sel_fy`

***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

Select Financial Year

<!-- For some reason need '-2' on end of 1819 links - check why this is -->
|     `r paste0("[2019/20](#", hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"), "-3)")`
|     `r paste0("[2018/19](#", hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"), "-", "201819)")`
|     `r paste0("[2017/18](#", hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"), "-", "201718)")`
|     `r paste0("[2016/17](#", hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"), "-", "201617)")`

***

For more information regarding how the LDP Standard is calculated, please see the [methodology](#methodology) page.

***

Please get in touch with any comments, suggestions and feedback: [NSS.ISDDementiaPDS@nhs.net](mailto:NSS.ISDDementiaPDS@nhs.net)


Row
----------------------------------------------------------------------

### **Note**

`r if_else(hb == "NHS Greater Glasgow & Clyde", "<span style='color:red'>Data for some IJBs in NHS Greater Glasgow & Clyde are currently unavailable and therefore board level figures should be treated with caution.</span>", if_else(hb == "NHS Lanarkshire", "<span style='color:red'>Some South Lanarkshire records are submitted by NHS Greater Glasgow & Clyde. Due to data submission issues, these records are not included in the below information.</span>", ""))`

These reports are an ongoing development following the implementation of the revised [Dementia PDS dataset](https://www.isdscotland.org/Health-Topics/Mental-Health/Dementia-Post-diagnostic-Support/_docs/Dementia-PDS-Definitions-and-Recording-Guidance.pdf) effective 01 April 2019. As such, they are currently marked as **DRAFT** and may be subject to change in future versions.

`r ifelse(complete_year == FALSE, "LDP Standard performance figures are not provided until data is available for the full financial year.", "")`


Row `r if(complete_year == FALSE)"{.hidden}"` 
----------------------------------------------------------------------

`r ifelse(complete_year == TRUE, "### Expected Value Box", "")`
```{r Expected Value Box, include = complete_year}
valueBox(paste0(round_half_up(exp_rate, 1), "%"), 
         caption = glue("of people estimated to be newly diagnosed with ",
                        "dementia were referred for post-diagnostic support."))
```

`r ifelse(complete_year == TRUE, "### <span style='color:CornflowerBlue'>**How is this figure calculated?**</span>", "")`

`r ifelse(complete_year == TRUE, glue("A total of <span style='color:CornflowerBlue'>**{ref_format}**</span> referrals were made to post-diagnostic support. This is divided by <span style='color:CornflowerBlue'>**{exp_format}**</span>, the estimated number of people newly diagnosed with dementia."), "")`

Row `r if(complete_year == FALSE)"{.hidden}"`
----------------------------------------------------------------------

`r ifelse(complete_year == TRUE, "### 12 Months Value Box", "")`
```{r 12 Months Value Box, include = complete_year}
valueBox(paste0(round_half_up(pds_rate, 1), "%"), 
         caption = glue("of those referred for post-diagnostic support ",
                        "received a minimum of 12 months of support."))
```

`r ifelse(complete_year == TRUE, "### <span style='color:CornflowerBlue'>**How is this figure calculated?**</span>", "")`

`r ifelse(complete_year == TRUE, glue("<span style='color:CornflowerBlue'>**{num_format}**</span> of referrals either met or were exempt from the LDP standard. This is divided by <span style='color:CornflowerBlue'>**{den_format}**</span>, the total number of referrals (excluding those whose support is ongoing)."), "")`


Row
----------------------------------------------------------------------

### **Number of Individuals relating to LDP Standard**

```{r ldp-table}

ldp_table(subpage_data,
          include_pc = complete_year)

```


Row {.data-height=1000}
----------------------------------------------------------------------

### **Number of Individuals Diagnosed and Referred for PDS** {data-width=800}

```{r referrals-plot}

plot_referrals(subpage_data, 
               scotland = FALSE,
               quarter = ifelse(max_fy == sel_fy, qt, NA))

```


Row
-----------------------------------------------------------------------
