---
title: "TRENDS DRAFT"
output: 
  flexdashboard::flex_dashboard:
    logo: phs-logo.png
    orientation: rows
    vertical_layout: scroll
---

```{r load-setup, include=FALSE}
source(here::here("code", "00_setup-environment.R"))
library(crosstalk) # for drop down menus
#library(phsstyles)
library(htmltools)


# Write numbers with thousands separator
knit_hooks$set(inline = function(x){
  if(!is.character(x)){prettyNum(x, big.mark=",")}else{x}
})
```

---
date: "`r paste('Data as at', format(end_date, '%d %B %Y'))`"
---

```{r setup, include=FALSE}

# Load functions
walk(dir(here::here("functions"), full.names = TRUE), source)


# Load PDS data
pds <- read_rds(get_mi_data_path("final_data", ext = "rds", test_output = test_output)) %>% 
  
  # Remove codes from board and IJB
  mutate(health_board = str_sub(health_board, 3, -1),
         ijb          = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))

# Load expected diagnoses reference file
exp <- read_csv(get_exp_diagnoses_path())


# Load error summary
err <- read_rds(get_mi_data_path("error_data", ext = "rds", test_output = test_output)) %>% 

  mutate(ijb = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))

# calculate referrals for Scotland and health boards
pds_ijb <- pds %>% arrange(ijb)

pds_ijb %<>% rename(geog = ijb) 

pds_ijb$geog<- factor(pds_ijb$geog, levels = unique(pds_ijb$geog))

pds_scot <- pds %>% group_by(health_board = "Scotland", ijb = "Scotland", fy, month, ldp_full, ldp, age_grp_2, age_grp, simd, sex) %>%  summarise(referrals = sum(referrals), .groups = "drop")

pds_scot %<>% rename(geog = ijb) 

pds_scot$geog<- factor(pds_scot$geog, levels = unique(pds_scot$geog))

pds_hb <- pds %>% group_by(health_board, fy, month, ldp_full, ldp, age_grp_2, age_grp, simd, sex) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ijb = health_board, .before = fy)

pds_hb %<>% rename(geog = ijb) 

pds_hb$geog<- factor(pds_hb$geog, levels = unique(pds_hb$geog))

# combine data for ijb, hb and Scotland
pds_all <- bind_rows(pds_scot, pds_ijb, pds_hb)

pds_all$geog<- factor(pds_all$geog, levels = unique(pds_all$geog))

#get totals for all geogs, hbs, ijbs, scotland
pds_all_totals <- pds_all %>% group_by(geog, fy, age_grp_2 = "All") %>% summarise(total_referrals = sum(referrals))

pds_ijb_totals <- pds_ijb %>% group_by(geog, fy, age_grp_2 = "All") %>% summarise(total_referrals = sum(referrals))

pds_hb_totals <- pds_hb %>% group_by(geog, fy, age_grp_2 = "All") %>% summarise(total_referrals = sum(referrals))

pds_scot_totals <- pds_scot %>% group_by(geog, fy, age_grp_2 = "All") %>% summarise(total_referrals = sum(referrals))


#get totals for all geogs, hbs, ijbs, scotland with LARGE AGE GROUPS
pds_all_totals_2 <- bind_rows(pds_all_totals,
  pds_all %>% filter(age_grp_2 != "Unknown") %>% group_by(geog, fy, age_grp_2) %>% summarise(total_referrals = sum(referrals))
)

pds_all_totals_2$age_grp_2<- factor(pds_all_totals_2$age_grp_2, levels = c("All", "65+", "64 and Under"))

pds_ijb_totals_2 <- bind_rows(pds_ijb_totals,
    pds_ijb %>% filter(age_grp_2 != "Unknown") %>% group_by(geog, fy, age_grp_2) %>% summarise(total_referrals = sum(referrals))
)

pds_ijb_totals_2$age_grp_2<- factor(pds_ijb_totals_2$age_grp_2, levels = c("All", "65+", "64 and Under"))


pds_hb_totals_2 <- bind_rows(pds_hb_totals,
    pds_hb %>% filter(age_grp_2 != "Unknown") %>% group_by(geog, fy, age_grp_2) %>% summarise(total_referrals = sum(referrals))
)

pds_hb_totals_2$age_grp_2<- factor(pds_hb_totals_2$age_grp_2, levels = c("All", "65+", "64 and Under"))


pds_scot_totals_2 <- bind_rows(pds_scot_totals,
    pds_scot %>% filter(age_grp_2 != "Unknown") %>% group_by(geog, fy, age_grp_2) %>% summarise(total_referrals = sum(referrals))
)

pds_scot_totals_2$age_grp_2<- factor(pds_scot_totals_2$age_grp_2, levels = c("All", "65+", "64 and Under"))

#load population rates data
pop_data <- read_rds("//conf/dementia/A&I/Outputs/management-report/lookups/pop_data.rds")

#create year lists
provisional_year <- paste0(as.numeric(substr(last(finalised_years),1,4)) + 1,
                           "/", as.numeric(substr(last(finalised_years),6,7)) + 1)

current_fy <- paste0(substr(fy,1,4),
                           "/", as.numeric(substr(fy,3,4)) + 1)

last_full_year <- if_else(qt == 4, current_fy, paste0(as.numeric(substr(fy,1,4)) - 1,
                           "/", as.numeric(substr(fy,3,4))))

all_years <- unique(pds_all$fy)

if(qt == 4){full_years = all_years}else{full_years = all_years[-length(all_years)]}


```

<script>

var pds_year = "`r current_fy`";

var ldp_year = "`r last_full_year`";

</script>

<!-- delete all of above when finished testing -->


All Referrals - Trends & Rates
=================================================

```{r data-setup-trends, include=FALSE}

#prepare population rate data
pop_data_trends <- pop_data %>%  filter(age_grp != "All", age_grp != "59 and Under", age_grp != "60 to 64", age_grp_2 == "All", sex == "All") %>% select(geog, year, age_grp, pop_est) %>% 
  group_by(geog, year) %>% summarise(pop_est = sum(pop_est)) %>% ungroup()

pds_all_cal_year <- pds_all_totals %>% 
  mutate(year = as.numeric(substr(fy, 1, 4)))

pds_all_rates <- left_join(pds_all_cal_year, pop_data_trends) %>% select(geog, fy, total_referrals, pop_est) %>% 
  mutate(pop_rate_10000 = round((total_referrals/pop_est)*10000, 1)) %>%
  select(geog, fy, pop_rate_10000) %>% 
  ungroup()

pds_all_rates <- left_join(pds_all_rates,
pds_all_rates %>% filter(geog == "Scotland") %>% select(fy, pop_rate_10000) %>% rename(scot_pop_rate_10000 = pop_rate_10000))

pds_all_rates$geog<- factor(pds_all_rates$geog, levels = unique(pds_all_rates$geog))

pds_scot_rates <- pds_all_rates %>% filter(geog == "Scotland")

pds_ijb_rates <- pds_all_rates %>% filter(geog != "Scotland", !grepl("NHS", geog))

pds_hb_rates <- pds_all_rates %>% filter(geog != "Scotland", grepl("NHS", geog))
 
```

Sidebar - trend {.sidebar}
-----------------------------------------------------------------------

<br>

### All Referrals - Trend
***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

<ul>
  <li>[**All Referrals - Trend**](#all-referrals---trends-rates)</li>
  <li>[All Referrals - Rates per 10,000 population](#pop-rates)</li>
  <li>[All Referrals - Outcomes by Financial Year](#trend-outcomes)</li>
</ul>

***
**FURTHER INFORMATION:**

<ul style="list-style-type:square;">
   <li >[Glossary](#glossary)</li>
   <li >[Navigation Guide](#navigation-guide)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)


Row
----------------------------------------------------------------------

### **Note**

This page includes a chart and table showing the trend for number of people referred to PDS by financial year for Scotland, Integration Authority Areas and Health Boards. Multiple Geographies can be selected in the Integration Authority and Health Board tabs. 

`r if(qt != 4) {div(style = css(fontStyle="italic"),paste0("For diagnoses in financial year ", current_fy, " data is available up to and including Q", qt, "."))}`

<!-- **Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.** -->


Row {.tabset data-height=1300}
----------------------------------------------------------------------

### **Scotland**

<br>
<br>
<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px"> Number of Individuals Diagnosed and Referred for PDS, Scotland</h2>
```{r trend-plot}

trends_plot <- plot_trend(pds_scot_totals, total_referrals, x ="Financial Year of Diagnosis", y = "Number Referred", measure_text = "Referrals: ", Scotland = TRUE)

bscols(widths = 12,
        div(style = css(width="98%", height="365px"), 
            trends_plot))

```
<br>
<br>
```{r trend-table}

pds_all_totals %>%  
            mutate(total_referrals = format(total_referrals, big.mark = ",")) %>% 
            pivot_wider(names_from = fy, values_from = total_referrals) %>% 
            rename(`Integration Authority Area/Health Board` = geog) %>%
            select(-age_grp_2) %>% 
            kable(align = c("l", rep("r", length(all_years)))) %>% 
            kable_styling(full_width = TRUE) %>%
            column_spec(1, bold = TRUE) %>%
  # Add header above table 
            add_header_above(
                       c(" " = 1,
                         "Financial Year of Diagnosis" = length(all_years))) %>%
            scroll_box(height = "760px")
 

```

### **Integration Authority Areas**

```{r dropdown-ijb}
pds_trends_data_ijb <- SharedData$new(pds_ijb_totals)

data_filter_ijb <- filter_select(id = "trend_filter_ijb",
                                    label = "Select Integration Authority Area(s):",
                                    group = ~geog,
                                    sharedData = pds_trends_data_ijb
                                   )

bscols(widths = c(1,10,NA), NULL,
data_filter_ijb, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px">Number of Individuals Diagnosed and Referred for PDS, Integration Authority Areas </h2>
```{r trend-plot-ijb}

trends_plot_ijb <- plot_trend(pds_trends_data_ijb, total_referrals, x ="Financial Year of Diagnosis", y = "Number Referred", measure_text = "Referrals: ", colours = phs_colours_31)

bscols(widths = 12,
        div(style = css(width="98%", height="395px"),
trends_plot_ijb))

```

```{r trend-table-ijb}

pds_all_totals %>% filter(geog == "Scotland" | !grepl("NHS", geog)) %>% 
            mutate(total_referrals = format(total_referrals, big.mark = ",")) %>% 
            pivot_wider(names_from = fy, values_from = total_referrals) %>% 
            rename(`Integration Authority Area` = geog) %>%
            select(-age_grp_2) %>% 
            kable(align = c("l", rep("r", length(all_years)))) %>% 
            kable_styling(full_width = TRUE) %>%
            column_spec(1, bold = TRUE) %>%
  # Add header above table 
            add_header_above(
                       c(" " = 1,
                         "Financial Year of Diagnosis" = length(all_years))) %>%
            scroll_box(height = "730px")
 

```

### **Health Boards**

```{r dropdown-hb}
pds_trends_data_hb <- SharedData$new(pds_hb_totals)

data_filter_hb <- filter_select(id = "trend_filter_hb",
                                    label = "Select Health Board(s):",
                                    group = ~geog,
                                    sharedData = pds_trends_data_hb
                                   )

bscols(widths = c(1,10,NA), NULL,
data_filter_hb, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px">Number of Individuals Diagnosed and Referred for PDS, Health Boards </h2>
```{r trend-plot-hb}

trends_plot_hb <- plot_trend(pds_trends_data_hb, total_referrals, x ="Financial Year of Diagnosis", y = "Number Referred", measure_text = "Referrals: ", colours = phs_colours_14)

bscols(widths = 12,
        div(style = css(width="98%", height="395px"),
trends_plot_hb))

```

```{r trend-table-hb}

pds_all_totals %>% filter(geog == "Scotland" | grepl("NHS", geog)) %>% 
            mutate(total_referrals = format(total_referrals, big.mark = ",")) %>% 
            pivot_wider(names_from = fy, values_from = total_referrals) %>%
            rename(`Health Board` = geog) %>%
            select(-age_grp_2) %>% 
            kable(align = c("l", rep("r", length(all_years)))) %>%
            kable_styling(full_width = TRUE) %>%
            column_spec(1, bold = TRUE) %>%
  # Add header above table 
            add_header_above(
                    c(" " = 1,
                     "Financial Year of Diagnosis" = length(all_years)))

```

Pop Rates {.hidden}
=====================================
Sidebar - rates {.sidebar}
-----------------------------------------------------------------------

<br>

### All Referrals - Rates per 10,000 population 

***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***
<ul>
  <li>[All Referrals - Trend](#all-referrals---trends-rates)</li>
  <li>[**All Referrals - Rates per 10,000 population**](#pop-rates)</li>
  <li>[All Referrals - Outcomes by Financial Year](#trend-outcomes)</li>
</ul>

***
**FURTHER INFORMATION:**

<ul style="list-style-type:square;">
   <li >[Glossary](#glossary)</li>
   <li >[Navigation Guide](#navigation-guide)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)


Row
----------------------------------------------------------------------

### **Note**

This page includes rates of the number of people referred to PDS per 10,000 population (65 years and over). *See the [Glossary](#glossary) for more details.*

The Integration Authority Area and Health Board tabs include a chart and table showing the rate for each geographical area by financial year.  

The Trend tab includes a chart and table showing the trend of the rate by financial year for Scotland, Integration Authority Areas and Health Boards. Multiple geographies can be selected.  

`r if(qt != 4) {div(style = css(fontStyle="italic"),paste0("For diagnoses in financial year ", current_fy, " data is available up to and including Q", qt, "."))}`

<!-- **Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.** -->


Row {.tabset data-height=1300}
----------------------------------------------------------------------

### **Integration Authority Areas**

```{r dropdown-pop-ijb}
pds_ijb_pop_data <- SharedData$new(pds_ijb_rates,
                                   key = ~fy, group = "groupijb")

data_filter_year_ijb <- filter_select(id = "trend_filter_year_ijb",
                                    label = "Select Financial Year:",
                                    group = ~fy,
                                    sharedData = pds_ijb_pop_data,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,3,NA),NULL,
data_filter_year_ijb,NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px"> Number of Individuals Diagnosed and Referred for PDS per 10,000 Population (65+) by Integration Authority Area</h2>
```{r plot-ijb-pop}

ijb_rates_plot <- plot_bar_pop_rate(pds_ijb_pop_data)

bscols(widths = 12,
        div(style = css(width="98%", height="425px"),
 ijb_rates_plot))

```

```{r trend-table-ijb-pop}

pds_all_rates %>% filter(geog == "Scotland" | !grepl("NHS", geog)) %>%
            select(-scot_pop_rate_10000) %>% 
            pivot_wider(names_from = fy, values_from = pop_rate_10000) %>%
            rename(`Integration Authority Area` = geog) %>%
            kable(align = c("l", rep("r", length(all_years)))) %>%
            kable_styling(full_width = TRUE) %>%
            column_spec(1, bold = TRUE) %>%
  # Add header above table
            add_header_above(
                       c(" " = 1,
                         "Financial Year of Diagnosis" = length(all_years))) %>%
            scroll_box(height = "720px")


```

### **Health Boards**

```{r dropdown-pop-hb}
pds_hb_pop_data <- SharedData$new(pds_hb_rates ,
                                  key = ~fy, group = "grouphb")

data_filter_year_hb <- filter_select(id = "trend_filter_year_hb",
                                    label = "Select Financial Year:",
                                    group = ~fy,
                                    sharedData = pds_hb_pop_data,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,3,NA),NULL,
data_filter_year_hb,NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px"> Number of Individuals Diagnosed and Referred for PDS per 10,000 Population (65+) by Health Board</h2>
```{r plot-hb-pop}
 
 hb_rates_plot <- plot_bar_pop_rate(pds_hb_pop_data)

 bscols(widths = 12,
         div(style = css(width="98%", height="425px"),
  hb_rates_plot))

```

```{r trend-table-hb-pop}

pds_all_rates %>% filter(geog == "Scotland" | grepl("NHS", geog)) %>%
            select(-scot_pop_rate_10000) %>% 
            pivot_wider(names_from = fy, values_from = pop_rate_10000) %>%
            rename(`Health Board` = geog) %>%
            kable(align = c("l", rep("r", length(all_years)))) %>%
            kable_styling(full_width = TRUE) %>%
            column_spec(1, bold = TRUE) %>%
  # Add header above table
            add_header_above(
                    c(" " = 1,
                     "Financial Year of Diagnosis" = length(all_years)))

```

### **Trend**

```{r dropdown-pop}
pds_trends_pop_data <- SharedData$new(pds_all_rates)

data_filter_hb_ijb_pop <- filter_select(id = "trend_filter_pop",
                                    label = "Select Integration Authority Area(s) or Health Board(s):",
                                    group = ~geog,
                                    sharedData = pds_trends_pop_data
                                   )
bscols(widths = c(1,10,NA),NULL,
data_filter_hb_ijb_pop,NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px"> Number of Individuals Diagnosed and Referred for PDS per 10,000 Population (65+)</h2>
```{r trend-plot-pop}

 trends_pop_plot <- plot_trend(pds_trends_pop_data, pop_rate_10000, x ="Financial Year of Diagnosis", y = "Rate Per 10,000 Popuation", colours = phs_colours_46, measure_text = "Rate per 10,000 population: ")

bscols(widths = 12,
        div(style = css(width="98%", height="385px"),
 trends_pop_plot)
)
```

```{r trend-table-pop}

pds_all_rates %>% 
       select(-scot_pop_rate_10000) %>%
            pivot_wider(names_from = fy, values_from = pop_rate_10000) %>%
            rename(`Integration Authority Area/Health Board` = geog) %>%
            kable(align = c("l", rep("r", length(all_years)))) %>%
            kable_styling(full_width = TRUE) %>%
            column_spec(1, bold = TRUE) %>%
  # Add header above table
            add_header_above(
                    c(" " = 1,
                     "Financial Year of Diagnosis" = length(all_years))) %>%
            scroll_box(height = "720px")

```

Trend Outcomes {.hidden}
=====================================
Sidebar - outcomes {.sidebar}
-----------------------------------------------------------------------

<br>

### All Referrals - Outcomes by Financial Year 

***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***
<ul>
  <li>[All Referrals - Trend](#all-referrals---trends-rates)</li>
  <li>[All Referrals - Rates per 10,000 population](#pop-rates)</li>
  <li>[**All Referrals - Outcomes by Financial Year**](#trend-outcomes)</li>
</ul>

***
**FURTHER INFORMATION:**

<ul style="list-style-type:square;">
   <li >[Methodology](#methodology)</li>
   <li >[Glossary](#glossary)</li>
   <li >[Navigation Guide](#navigation-guide)</li>
</ul>


***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)


Row
----------------------------------------------------------------------

### **Note**

This page includes charts and tables showing, for the selected geographies, the trend by financial year for information relating to the LDP Standard.  

The first tab shows the percentage of the estimated number of people newly diagnosed with dementia that have been referred to PDS for Scotland and Health Boards (estimates are not available for Integration Authority Areas). 

The second tab shows the percentage of referrals that have received one year’s support which started within a year of diagnosis (or have been exempt from the LDP Standard) for Scotland, Integration Authority Areas and Health Boards. 

*As PDS for some referrals in `r provisional_year` onwards is still ongoing, it is not known yet whether or not they will meet the LDP standard. Therefore, the figures shown for these years are currently provisional and subject to change in future versions of this report.*

`r if(qt != 4) {div(style = css(fontStyle="italic"),paste("LDP Standard performance figures are not provided until data is available for the full financial year."))}`

<!-- **Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.** -->


Row {.tabset data-height=1240}
----------------------------------------------------------------------

### **Percentage of estimated diagnoses referred to PDS**

```{r dropdown-exp}
pds_exp_rates <- left_join(
bind_rows(pds_scot_totals, pds_hb_totals) %>% filter(fy %in% full_years),
exp %>% select(-health_board) %>% rename(geog = health_board_label)) %>% 
  mutate(exp_rate = round(100*total_referrals/diagnoses,1))

pds_exp_rates$geog<- factor(pds_exp_rates$geog, levels = unique(pds_exp_rates$geog))

pds_exp_rates_data <- SharedData$new(pds_exp_rates)

data_filter_exp_trend <- filter_select(id = "trend_filter_outcomes_exp",
                                    label = "Select Health Board(s):",
                                    group = ~geog,
                                    sharedData = pds_exp_rates_data
                                   )
bscols(widths = c(1,10,NA),NULL,
data_filter_exp_trend,NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px"> Percentage of people estimated to be newly diagnosed with dementia who were referred for post-diagnostic support</h2>
```{r trend-plot-exp}

 trends_exp_plot <- plot_trend_perc(pds_exp_rates_data, exp_rate, x ="Financial Year of Diagnosis", colours = phs_colours_15)

bscols(widths = 12,
        div(style = css(width="98%", height="385px"),
 trends_exp_plot)
)
```

```{r trend-table-exp}

pds_exp_rates %>% select(geog, fy, exp_rate) %>% 
            pivot_wider(names_from = fy, values_from = exp_rate) %>%
            mutate(across(where(is.numeric), ~paste0(.,"%"))) %>% 
            rename(`Health Board` = geog) %>%
            kable(align = c("l", rep("r", length(full_years)))) %>%
            kable_styling(full_width = TRUE) %>%
            column_spec(1, bold = TRUE) %>%
  # Add header above table
            add_header_above(
                    c(" " = 1,
                     "Financial Year of Diagnosis" = length(full_years)))

```

### **Percentage receiving one year's PDS support**

```{r dropdown-met-ldp}
pds_met_rates <-
  pds_all %>% filter(age_grp_2 != "Unknown", ldp != "ongoing", fy %in% full_years) %>% 
  group_by(geog, fy, ldp) %>% 
  summarise(referrals = sum(referrals)) %>% pivot_wider(names_from = ldp, values_from = referrals, values_fill = 0) %>% 
  mutate(perc_met = round(100*(complete + exempt)/(complete + exempt + fail), 1))

pds_met_rates$geog<- factor(pds_met_rates$geog, levels = unique(pds_met_rates$geog))

pds_met_rates_data <- SharedData$new(pds_met_rates)

data_filter_met_trend <- filter_select(id = "trend_filter_outcomes_met",
                                    label = "Select Integration Authority Area(s) or Health Board(s):",
                                    group = ~geog,
                                    sharedData = pds_met_rates_data
                                   )
bscols(widths = c(1,10,NA),NULL,
data_filter_met_trend,NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px">Percentage of referrals who received a minimum of one year’s PDS (Standard Met/Exempt)</h2>
```{r plot-med-ldp}
 trends_met_plot <- plot_trend_perc(pds_met_rates_data, perc_met, x ="Financial Year of Diagnosis", colours = phs_colours_46)

bscols(widths = 12,
        div(style = css(width="98%", height="385px"),
 trends_met_plot)
)

```


```{r trend-table-met}

pds_met_rates %>% select(geog, fy, perc_met) %>% 
            pivot_wider(names_from = fy, values_from = perc_met) %>%
            mutate(across(where(is.numeric), ~paste0(.,"%"))) %>% 
            rename(`Integration Authority Area/Health Board` = geog) %>%
            kable(align = c("l", rep("r", length(full_years)))) %>%
            kable_styling(full_width = TRUE) %>%
            column_spec(1, bold = TRUE) %>%
  # Add header above table
            add_header_above(
                    c(" " = 1,
                     "Financial Year of Diagnosis" = length(full_years))) %>% 
  scroll_box(height = "670px")

```


```{js }

function filter_default() {
  document.getElementById("trend_filter_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue("NHS Ayrshire & Arran", false);

  document.getElementById("trend_filter_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("trend_filter_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("Aberdeen City", false);

  document.getElementById("trend_filter_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
 
   document.getElementById("trend_filter_pop").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("trend_filter_pop").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("trend_filter_year_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue(pds_year, false);

  document.getElementById("trend_filter_year_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("trend_filter_year_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue(pds_year, false);

  document.getElementById("trend_filter_year_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("trend_filter_outcomes_exp").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("trend_filter_outcomes_exp").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
    document.getElementById("trend_filter_outcomes_met").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("trend_filter_outcomes_met").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  
  }
  
  $(document).ready(filter_default);

```