---
title: "PATHWAYS DRAFT"
output: 
  flexdashboard::flex_dashboard:
    logo: phs-logo.png
    orientation: rows
    vertical_layout: scroll
---

```{r load-setup, include=FALSE}
source(here::here("code", "00_setup-environment.R"))
library(crosstalk) # for drop down menus
library(phsstyles)
library(htmltools)


# Write numbers with thousands separator
knit_hooks$set(inline = function(x){
  if(!is.character(x)){prettyNum(x, big.mark=",")}else{x}
})
```

---
date: "`r paste('Data as at', format(end_date, '%d %B %Y'))`"
---

```{r setup, include=FALSE}

# Remove tidylog
detach("package:tidylog", unload = TRUE)

# Load functions
walk(dir(here::here("functions"), full.names = TRUE), source)

# Load PDS data
pds <- read_rds(get_mi_data_path("final_data", ext = "rds", test_output = test_output)) %>% 
  
  # Remove codes from board and IJB
  mutate(health_board = str_sub(health_board, 3, -1),
         ijb          = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))

# Load expected diagnoses reference file
exp <- read_csv(get_exp_diagnoses_path())


# Load error summary
err <- read_rds(get_mi_data_path("error_data", ext = "rds", test_output = test_output)) %>% 

  mutate(ijb = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))

# calculate final data referrals for Scotland and health boards
pds_ijb <- pds %>% arrange(ijb)

pds_scot <- pds %>% group_by(health_board = "Scotland", ijb = "Scotland", fy, month, ldp_full, ldp, age_grp_2, age_grp, simd, sex) %>%   summarise(referrals = sum(referrals), .groups = "drop")

pds_hb <- pds %>% group_by(health_board, fy, month, ldp_full, ldp, age_grp_2, age_grp, simd, sex) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ijb = health_board, .before = fy)

# combine data for ijb, hb and Scotland
pds_all <- bind_rows(pds_scot, pds_hb, pds_ijb)

pds_all %<>% rename(geog = ijb) 

pds_all$geog<- factor(pds_all$geog, levels = unique(pds_all$geog))

#create year lists
provisional_year <- paste0(as.numeric(substr(last(finalised_years),1,4)) + 1,
                           "/", as.numeric(substr(last(finalised_years),6,7)) + 1)

current_fy <- paste0(substr(fy,1,4),
                           "/", as.numeric(substr(fy,3,4)) + 1)

last_full_year <- if_else(qt == 4, current_fy, paste0(as.numeric(substr(fy,1,4)) - 1,
                           "/", as.numeric(substr(fy,3,4))))

all_years <- unique(pds_all$fy)

if(qt == 4){full_years = all_years}else{full_years = all_years[-length(all_years)]}


```
<!-- delete all of above when finished testing -->


PDS Pathways
=================================================

```{r data setup, include=FALSE}
wait_data <- read_rds(get_mi_data_path("wait_data", ext = "rds", test_output = test_output))

wait_data_2 <- read_rds(get_mi_data_path("wait_data_2", ext = "rds", test_output = test_output))

wait_data_3 <- read_rds(get_mi_data_path("wait_data_3", ext = "rds", test_output = test_output))

wait_data$health_board <- as.factor(wait_data$health_board)
wait_data$fy <- as.factor(wait_data$fy)
wait_data$simd <- as.factor(wait_data$simd)
wait_data$sex <- as.factor(wait_data$sex)
wait_data$ijb <- as.factor(wait_data$ijb)


wait_data_2$health_board <- as.factor(wait_data_2$health_board)
wait_data_2$fy <- as.factor(wait_data_2$fy)
wait_data_2 %<>% arrange(termination_or_transition_reason)
wait_data_2$sex <- as.factor(wait_data_2$sex)
wait_data_2$ijb <- factor(wait_data_2$ijb, levels = unique(pds_all$geog))
wait_data_2 %<>% mutate(termination_or_transition_reason = if_else(termination_or_transition_reason == "14 All reasons", substring(termination_or_transition_reason, 3), termination_or_transition_reason))
wait_data_2$termination_or_transition_reason <- as.factor(wait_data_2$termination_or_transition_reason)

wait_data_3$health_board <- as.factor(wait_data_3$health_board)
wait_data_3$fy <- as.factor(wait_data_3$fy)
wait_data_3 %<>% arrange(termination_or_transition_reason)
wait_data_3$sex <- as.factor(wait_data_3$sex)
wait_data_3$ijb <- factor(wait_data_3$ijb, levels = unique(pds_all$geog))
wait_data_3 %<>% mutate(termination_or_transition_reason = if_else(termination_or_transition_reason == "14 All reasons", substring(termination_or_transition_reason, 4), termination_or_transition_reason))
wait_data_3$termination_or_transition_reason <- as.factor(wait_data_3$termination_or_transition_reason)
 
```

Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

### Pathways - Waiting Times
***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

<ul>
  <li>[**Pathways - Waiting Times**](#pds-pathways)</li>
  <li>[Pathways - PDS Outcomes](#outcomes)</li>
  <li>[Pathways - Termination of PDS](#termination-reasons)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

Row
----------------------------------------------------------------------

### **Note**

**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.**


Row {.tabset data-height=760}
----------------------------------------------------------------------

### **Integration Authority Areas**

```{r dropdown-wait-ijb}
wait_data_ijb <- wait_data %>% 
      filter(sex == "All") %>% 
     filter(ijb != "All", simd == "All") %>% 
      select(ijb, fy, total_referrals, median_diagnosis_to_referral,
             perc_allocated, median_referral_to_allocation,
             perc_contacted, median_allocation_to_contact,
             median_diagnosis_to_contact) %>% 
  mutate(across(starts_with("perc"), ~ paste0(.,"%"))) %>%
  mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
      mutate(ijb = if_else(ijb == "Scotland", "AAA", ijb)) %>%
      arrange(ijb) %>% 
      mutate(ijb = if_else(ijb == "AAA", "Scotland", ijb)) %>% 
      set_colnames(c("Integration Authority Area", "fy", "Number of People Referred to PDS",  "Average (median) days from diagnosis to PDS referral",
                     "Percentage of Referrals allocated to PDS practitioner", "Average (median) days from referral to allocation of PDS practitioner", 
                     "Percentage of Referrals contacted by PDS practitioner",  "Average (median) days from allocation to first contact with PDS practitioner",
                     "Average (median) days from diagnosis to first contact"
      )) 

wait_table_data_ijb <- SharedData$new(wait_data_ijb)

data_filter_ijb_year <- filter_select(id = "wait_filter_ijb_year",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = wait_table_data_ijb,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,4,NA), NULL,
data_filter_ijb_year, NULL)

```

<h2 style="margin-left: 60px; margin-top: 0px; margin-bottom: -20px"> Pathways from diagnosis to contact by PDS practitioner </h2>
```{r wait-table-ijb}
bscols(widths = 12,
       div(style = css(width="97%", height="585px", margin="20px"),
    DT::datatable(wait_table_data_ijb, rownames = FALSE,  
                                        caption = htmltools::tags$caption(
                       style = 'caption-side: bottom; text-align: left;',
                       "A dash (-) indicates no dates of referral were submitted for diagnoses in this 
                              year."),
                       options = list(pageLength = 32,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:8)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

  

```

### **Health Boards**

```{r wait-dropdown-hb}

wait_data_hb <- wait_data %>% 
      filter(sex == "All") %>% 
      filter(ijb == "All" | ijb == "Scotland", simd == "All") %>% 
     select(health_board, fy, total_referrals, median_diagnosis_to_referral,
             perc_allocated, median_referral_to_allocation,
             perc_contacted, median_allocation_to_contact,
             median_diagnosis_to_contact) %>% 
  mutate(across(starts_with("perc"), ~ paste0(.,"%"))) %>%
  mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
      set_colnames(c("Health Board", "fy", "Number of People Referred to PDS",  "Average (median) days from diagnosis to PDS referral",
                     "Percentage of Referrals allocated to PDS practitioner", "Average (median) days from referral to allocation of PDS practitioner", 
                     "Percentage of Referrals contacted by PDS practitioner",  "Average (median) days from allocation to first contact with PDS practitioner",
                     "Average (median) days from diagnosis to first contact"
      )) 

wait_table_data_hb <- SharedData$new(wait_data_hb)

data_filter_hb_year <- filter_select(id = "wait_filter_hb_year",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = wait_table_data_hb,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,4,NA), NULL,
data_filter_hb_year, NULL)

```

<h2 style="margin-left: 60px; margin-top: 0px; margin-bottom: -20px"> Pathways from diagnosis to contact by PDS practitioner </h2>
```{r wait-table-hb}

bscols(widths = 12,
       div(style = css(width="97%", height="585px", margin="20px"),
  DT::datatable(wait_table_data_hb, rownames = FALSE,
                 caption = htmltools::tags$caption(
                       style = 'caption-side: bottom; text-align: left;',
                       "A dash (-) indicates no dates of referral were submitted for diagnoses in this 
                              year."),
              options = list(pageLength = 15,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:8)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```

Outcomes {.hidden}
=================================================

```{r add-percentage-function, include=FALSE}

add_percent <- function(df, value, name) {
  
 data <- df %>%  mutate(perc =  if_else(`Total Number of individuals` == 0, "-",
    paste0(round(100*{{value}}/`Total Number of individuals`,1), "%")))
  
colnames(data)[colnames(data) == 'perc'] <- name

return(data)
  
}

```

Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

### Pathways - PDS Outcomes
***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

<ul>
  <li>[Pathways - Waiting Times](#pds-pathways)</li>
  <li>[**Pathways - PDS Outcomes**](#outcomes)</li>
  <li>[Pathways - Termination of PDS](#termination-reasons)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

Row
----------------------------------------------------------------------

### **Note**

**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.**


Row {.tabset data-height=760}
----------------------------------------------------------------------

### **Standard Met**

```{r dropdown-met}
met_data <- pds_all %>% filter(ldp == "complete", fy %in% full_years) %>% group_by(geog, fy, ldp_full) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ldp_full = substring(ldp_full, 12)) %>%   pivot_wider(names_from = ldp_full, values_from = referrals) %>%
  rename(`Health Board/Integration Authority Area` = geog) %>% 
   mutate(`Total Number of individuals` = rowSums(across(where(is.numeric))), .after = fy) %>% 
mutate(`% PDS ended` = if_else(`Total Number of individuals` == 0, "-",
  paste0(round(100*`PDS ended`/`Total Number of individuals`,1), "%")), .after = `PDS ended`) %>% 
mutate(`% Still receiving PDS` = if_else(`Total Number of individuals` == 0, "-",
  paste0(round(100*`Still receiving PDS`/`Total Number of individuals`,1), "%")), .after = `Still receiving PDS`) %>% 
  select(-`PDS ended`, -`Still receiving PDS`)
  

met_table_data <- SharedData$new(met_data)

 data_filter_met_year <- filter_select(id = "met_filter_year",
                                     label = "Select Financial Year of Diagnosis:",
                                     group = ~fy,
                                     sharedData = met_table_data,
                                    multiple = FALSE
                                    )

 bscols(widths = c(1,4,NA), NULL,
 data_filter_met_year, NULL)

```

<h2 style="margin-left: 10px; margin-top: 0px; margin-bottom: -20px"> Individuals where PDS met LDP Standard</h2>
```{r met-table}
bscols(widths = 12,
       div(style = css(width="97%", height="585px", margin="20px"),
    DT::datatable(met_table_data, rownames = FALSE,
                                       # caption = htmltools::tags$caption(
                      # style = 'caption-side: bottom; text-align: left;',
                      # "A dash (-) indicates no dates of referral were submitted for diagnoses in this
                        #      year."),
                       options = list(pageLength = 46,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:4)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(1, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )


```

### **Standard Not Met**

```{r dropdown-not-met}
not_met_data <- pds_all %>% filter(ldp == "fail") %>% group_by(geog, fy, ldp_full) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ldp_full = substring(ldp_full, 8)) %>% 
  pivot_wider(names_from = ldp_full, values_from = referrals) %>%
  rename(`Health Board/Integration Authority Area` = geog) %>% 
   mutate(`Total Number of individuals` = rowSums(across(where(is.numeric))), .after = fy) %>% 
   add_percent(`PDS terminated before first contact`, "% PDS terminated before first contact") %>% 
 add_percent(`PDS not started and more than 12 months since diagnosis`, "% PDS not started and more than 12 months since diagnosis") %>% 
  add_percent(`PDS started more than 12 months after diagnosis`, "% PDS started more than 12 months after diagnosis") %>% 
  add_percent(`PDS terminated less than 11 months after first contact`, "% PDS terminated less than 11 months after first contact") %>% 
  select(-starts_with("PDS"))

not_met_table_data <- SharedData$new(not_met_data)

 data_filter_not_met_year <- filter_select(id = "not_met_filter_year",
                                     label = "Select Financial Year of Diagnosis:",
                                     group = ~fy,
                                     sharedData = not_met_table_data,
                                    multiple = FALSE
                                    )

 bscols(widths = c(1,4,NA), NULL,
 data_filter_not_met_year, NULL)

```

<h2 style="margin-left: 10px; margin-top: 0px; margin-bottom: -20px"> Individuals where PDS did not meet LDP Standard</h2>
```{r not-met-table}

bscols(widths = 12,
       div(style = css(width="97%", height="585px", margin="20px"),
    DT::datatable(not_met_table_data, rownames = FALSE,
                                       # caption = htmltools::tags$caption(
                      # style = 'caption-side: bottom; text-align: left;',
                      # "A dash (-) indicates no dates of referral were submitted for diagnoses in this
                        #      year."),
                       options = list(pageLength = 46,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:6)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(1, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )


```

### **PDS Ongoing**

```{r dropdown-ongoing}
ongoing_data <- pds_all %>% filter(ldp == "ongoing") %>% group_by(geog, fy, ldp_full) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ldp_full = substring(ldp_full, 11)) %>%   pivot_wider(names_from = ldp_full, values_from = referrals) %>%
  rename(`Health Board/Integration Authority Area` = geog) %>% 
   mutate(`Total Number of individuals` = rowSums(across(where(is.numeric))), .after = fy) %>% 
   add_percent(`PDS not started and less than 12 months since diagnosis`, "% PDS not started and less than 12 months since diagnosis") %>% 
 add_percent(`Still receiving PDS and less than 12 months since first contact`, "% Still receiving PDS and less than 12 months since first contact") %>% 
  select(-starts_with("PDS"), -starts_with("Still"))

ongoing_table_data <- SharedData$new(ongoing_data)

 data_filter_ongoing_year <- filter_select(id = "ongoing_filter_year",
                                     label = "Select Financial Year of Diagnosis:",
                                     group = ~fy,
                                     sharedData = ongoing_table_data,
                                    multiple = FALSE
                                    )

 bscols(widths = c(1,4,NA), NULL,
 data_filter_ongoing_year, NULL)

```

<h2 style="margin-left: 10px; margin-top: 0px; margin-bottom: -20px"> Individuals where LDP Standard cannot yet be determined (PDS Ongoing)</h2>
```{r ongoing-table}

bscols(widths = 12,
       div(style = css(width="97%", height="585px", margin="20px"),
    DT::datatable(ongoing_table_data, rownames = FALSE,
                                       # caption = htmltools::tags$caption(
                      # style = 'caption-side: bottom; text-align: left;',
                      # "A dash (-) indicates no dates of referral were submitted for diagnoses in this
                        #      year."),
                       options = list(pageLength = 46,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:4)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(1, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )


```

### **Exempt**

```{r dropdown-exempt}
exempt_data <- pds_all %>% filter(ldp == "exempt") %>% group_by(geog, fy, ldp_full) %>% 
  summarise(referrals = sum(referrals), .groups = "drop") %>% mutate(ldp_full = substring(ldp_full, 10)) %>%   pivot_wider(names_from = ldp_full, values_from = referrals) %>%
  rename(`Health Board/Integration Authority Area` = geog) %>% 
   mutate(`Total Number of individuals` = rowSums(across(where(is.numeric))), .after = fy) %>% 
   add_percent(`03 Service user has died`, "% 03 Service user has died") %>% 
 add_percent(`04 Service user has moved to a different Health Board area`, "% 04 Service user has moved to a different Health Board area") %>% 
  add_percent(`05 Service user has terminated PDS early/refused`, "% 05 Service user has terminated PDS early/refused") %>% 
  add_percent(`06 Service user no longer able to engage in PDS`, "% 06 Service user no longer able to engage in PDS") %>% 
  select(-starts_with("0"))

exempt_table_data <- SharedData$new(exempt_data)

 data_filter_exempt_year <- filter_select(id = "exempt_filter_year",
                                     label = "Select Financial Year of Diagnosis:",
                                     group = ~fy,
                                     sharedData = exempt_table_data,
                                    multiple = FALSE
                                    )

 bscols(widths = c(1,4,NA), NULL,
 data_filter_exempt_year, NULL)

```

<h2 style="margin-left: 10px; margin-top: 0px; margin-bottom: -20px">Individuals exempt from LDP Standard</h2>
```{r exempt-table}

bscols(widths = 12,
       div(style = css(width="97%", height="585px", margin="20px"),
    DT::datatable(exempt_table_data, rownames = FALSE,
                                       # caption = htmltools::tags$caption(
                      # style = 'caption-side: bottom; text-align: left;',
                      # "A dash (-) indicates no dates of referral were submitted for diagnoses in this
                        #      year."),
                       options = list(pageLength = 46,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 1),
                                                list(className = 'dt-right', targets = 2:6)
                                                #list(width = '10px', targets = 1:10)
                                                ))) %>%
           DT::formatStyle(1, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )


```

Termination Reasons {.hidden}
=================================================
Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

### Pathways - Termination of PDS
***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

<ul>
  <li>[Pathways - Waiting Times](#pds-pathways)</li>
  <li>[Pathways - PDS Outcomes](#outcomes)</li>
  <li>[**Pathways - Termination of PDS**](#termination-reasons)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

Row
----------------------------------------------------------------------

### **Note**

**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.**

Row {.tabset data-height=670}
----------------------------------------------------------------------

### **Integration Authority Areas**

```{r dropdown-term-ijb}
term_data_ijb_1 <- wait_data_3 %>% 
    filter(sex == "All", termination_or_transition_reason == "All reasons") %>%
    filter(ijb == "Scotland" | !grepl("NHS", ijb)) %>% 
    pivot_wider(names_from = ldp, values_from = c(referrals, median_referral_to_termination)) %>%
   select(fy, ijb,
           referrals_All,
           median_referral_to_termination_All,
           referrals_exempt,
           referrals_fail)
    
wait_data_totals_ijb <- wait_data %>% filter(sex == "All", simd == "All", ijb != "All" | ijb == "Scotland") %>% select(ijb, fy, total_referrals)

term_data_ijb <- left_join(wait_data_totals_ijb, term_data_ijb_1) %>% 
  mutate(across(starts_with("referrals"), ~ replace(., is.na(.), 0))) %>%
    mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
     mutate(perc_term_early = paste0(round((referrals_All/total_referrals)*100,1),"%")) %>% 
      mutate(perc_term_early_exempt = if_else(referrals_exempt == 0, NA,
        round((referrals_exempt/referrals_All)*100,1))) %>% 
          mutate(perc_term_early_exempt = if_else(!is.na(perc_term_early_exempt), paste0(perc_term_early_exempt, "%"), "-")) %>% 
  select(fy, ijb,
         total_referrals,
           referrals_All,
         perc_term_early,
           referrals_exempt,
         perc_term_early_exempt) %>% 

    set_colnames(c("fy", "Integration Authority Area", "Number of People Referred to PDS",
                   "Number of referrals whose PDS ended with no contact",
                   "Percentage of referrals whose PDS ended with no contact",
                   "Number of referrals whose PDS ended with no contact Exempt from LDP standard",
                   "Percentage of referrals whose PDS ended with no contact Exempt from LDP standard"))

term_table_data_ijb <- SharedData$new(term_data_ijb)

data_filter_year_term_ijb <- filter_select(id = "term_filter_year_ijb",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = term_table_data_ijb,
                                    multiple = FALSE
                                   )


bscols(widths = c(1,4,NA), NULL,
data_filter_year_term_ijb, NULL)

```

<h2 style="margin-left: 60px; margin-top: 0px; margin-bottom: -20px"> Pathways from referral to termination of PDS </h2>
```{r term-table-ijb}

bscols(widths = 12,
       div(style = css(width="97%", height="500px", margin="20px"),
     DT::datatable(term_table_data_ijb, rownames = FALSE,
              options = list(pageLength = 33,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0),
                                                list(className = 'dt-right', targets = 2:6)
                                                #list(width = '30px', targets = 6)
                                                ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```

### **Health Boards**

```{r dropdown-term-hb}

 term_data_hb_1 <- wait_data_3 %>% 
    filter(sex == "All", termination_or_transition_reason == "All reasons") %>%
    filter(ijb == "Scotland" | grepl("NHS", ijb)) %>% 
    pivot_wider(names_from = ldp, values_from = c(referrals, median_referral_to_termination)) %>%
  select(-health_board) %>% rename(health_board = ijb) %>% 
  select(fy, health_board,
           referrals_All,
           median_referral_to_termination_All,
           referrals_exempt,
           referrals_fail)
    
wait_data_totals_hb <- wait_data %>% filter(sex == "All", simd == "All", ijb == "All" | ijb == "Scotland") %>% select(health_board, fy, total_referrals)

term_data_hb <- left_join(wait_data_totals_hb, term_data_hb_1) %>% 
  mutate(across(starts_with("referrals"), ~ replace(., is.na(.), 0))) %>%
    mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
     mutate(perc_term_early = paste0(round((referrals_All/total_referrals)*100,1),"%")) %>% 
      mutate(perc_term_early_exempt = if_else(referrals_exempt == 0, NA,
        round((referrals_exempt/referrals_All)*100,1))) %>% 
          mutate(perc_term_early_exempt = if_else(!is.na(perc_term_early_exempt), paste0(perc_term_early_exempt, "%"), "-")) %>% 
  select(fy, health_board,
         total_referrals,
           referrals_All,
         perc_term_early,
           referrals_exempt,
         perc_term_early_exempt) %>% 

    set_colnames(c("fy", "Health Board", "Number of People Referred to PDS",
                   "Number of referrals whose PDS ended with no contact",
                   "Percentage of referrals whose PDS ended with no contact",
                   "Number of referrals whose PDS ended with no contact Exempt from LDP standard",
                   "Percentage of referrals whose PDS ended with no contact Exempt from LDP standard"))

term_table_data_hb <- SharedData$new(term_data_hb)

data_filter_year_term_hb <- filter_select(id = "term_filter_year_hb",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = term_table_data_hb,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,4,NA), NULL,
data_filter_year_term_hb, NULL)

```

<h2 style="margin-left: 60px; margin-top: 0px; margin-bottom: -20px"> Pathways from referral to termination of PDS </h2>
```{r term-table-hb}
bscols(widths = 12,
       div(style = css(width="97%", height="500px", margin="20px"),
     DT::datatable(term_table_data_hb, rownames = FALSE,
              options = list(pageLength = 15,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0),
                                                list(className = 'dt-right', targets = 2:6)
                                                #list(width = '30px', targets = 6)
                                                ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```

Row {.tabset data-height=770}
----------------------------------------------------------------------

### **Termination Reasons - PDS Ending Without Contact**

```{r dropdown-term-1}
 term_data_2 <- wait_data_3 %>%
    filter(sex == "All") %>%
    pivot_wider(names_from = ldp, values_from = c(referrals, median_referral_to_termination)) %>%
    mutate(across(starts_with("referrals"), ~ replace(., is.na(.), 0))) %>%
    mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>%
    select(fy, ijb, termination_or_transition_reason,
           referrals_All, 
           median_referral_to_termination_All,
           referrals_exempt,
           referrals_fail) %>%
    set_colnames(c("fy", "geog", "Reason for termination of post-diagnostic support",
                   "Number of people", 
                   "Average (median) days from referral to termination of PDS",
                   "Exempt from Standard",
                   "Standard Not Met"))

term_table_data_2 <- SharedData$new(term_data_2)

data_filter_year_term_2 <- filter_select(id = "term_filter_year_2",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = term_table_data_2,
                                    multiple = FALSE
                                   )

data_filter_geog_term_2 <- filter_select(id = "term_filter_geog_2",
                                    label = "Select Health Board or Integration Authority Area:",
                                    group = ~geog,
                                    sharedData = term_table_data_2,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,5,5,NA), NULL,
data_filter_year_term_2, data_filter_geog_term_2, NULL)



```

<h2 style="margin-left: 60px; margin-top: 0px; margin-bottom: -20px"> Pathways from referral to termination of post-diagnostic support without contact </h2>
```{r term-table-1}

bscols(widths = 12,
       div(style = css(width="97%", height="590px", margin="20px"),
     DT::datatable(term_table_data_2, rownames = FALSE,
              options = list(pageLength = 14,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0:1),
                                                list(className = 'dt-right', targets = 3:6)
                                                #list(width = '30px', targets = 6)
                                                ))) %>%
           DT::formatStyle(3, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```

### **Termination Reasons - PDS Ending On or After Contact**

```{r dropdown-term-2}
 term_data <- wait_data_2 %>% 
    filter(sex == "All") %>% 
    pivot_wider(names_from = ldp, values_from = c(referrals, median_contact_to_termination)) %>% 
    mutate(across(starts_with("referrals"), ~ replace(., is.na(.), 0))) %>% 
    mutate(across(starts_with("median"), ~ replace(., is.na(.), "-"))) %>% 
    select(fy, ijb, termination_or_transition_reason,
           referrals_All,
           median_contact_to_termination_All,
           referrals_complete,
           referrals_exempt,
           referrals_fail) %>% 
    set_colnames(c("fy", "geog", "Reason for end of post-diagnostic support",
                   "Number of people", 
                   "Average (median) days from first contact with PDS practitioner to end of PDS",
                   "Standard Met",
                   "Exempt from Standard",
                   "Standard Not Met"))
 
term_table_data <- SharedData$new(term_data)

data_filter_year_term <- filter_select(id = "term_filter_year",
                                    label = "Select Financial Year of Diagnosis:",
                                    group = ~fy,
                                    sharedData = term_table_data,
                                    multiple = FALSE
                                   )

data_filter_geog_term <- filter_select(id = "term_filter_geog",
                                    label = "Select Health Board or Integration Authority Area:",
                                    group = ~geog,
                                    sharedData = term_table_data,
                                    multiple = FALSE
                                   )

bscols(widths = c(1,5,5,NA), NULL,
data_filter_year_term, data_filter_geog_term, NULL)

```

<h2 style="margin-left: 60px; margin-top: 0px; margin-bottom: -20px"> Pathways from contact by PDS practitioner to end of post-diagnostic support </h2>
```{r term-table-2}

bscols(widths = 12,
       div(style = css(width="97%", height="590px", margin="20px"),
     DT::datatable(term_table_data, rownames = FALSE,
              options = list(pageLength = 14,
                             scrollX = FALSE,
                             scrollY = TRUE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0:1),
                                                list(className = 'dt-right', targets = 3:7)#,
                                                #list(width = '10px', targets = 6)
                                                ))) %>%
           DT::formatStyle(3, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )

```


```{js }


function filter_default() {

  document.getElementById("met_filter_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("met_filter_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("not_met_filter_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("not_met_filter_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("ongoing_filter_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("ongoing_filter_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("exempt_filter_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("exempt_filter_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");

  document.getElementById("wait_filter_ijb_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("wait_filter_ijb_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("wait_filter_hb_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("wait_filter_hb_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_year_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("term_filter_year_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("term_filter_year_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("term_filter_year_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("term_filter_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_geog").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("term_filter_geog").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_year_2").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("term_filter_year_2").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("term_filter_geog_2").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("term_filter_geog_2").getElementsByClassName("selectized")
  [0].selectize.removeOption("");

  document.getElementById("trend_filter_age_prop_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("trend_filter_age_prop_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("trend_filter_age_prop_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("trend_filter_age_prop_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("filter_trend_age_2_pop").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("filter_trend_age_2_pop").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("filter_pop_age_year").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("filter_pop_age_year").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("filter_pop_age_hb_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("NHS Ayrshire & Arran", false);

  document.getElementById("filter_pop_age_hb_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("filter_ldp_age_2").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("filter_ldp_age_2").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("filter_sex_prop_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("filter_sex_prop_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("filter_sex_prop_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("filter_sex_prop_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("filter_trend_sex_pop").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("filter_trend_sex_pop").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("filter_hb_sex_pop").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("filter_hb_sex_pop").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
    document.getElementById("filter_ijb_sex_pop").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("filter_ijb_sex_pop").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("filter_ldp_sex").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("filter_ldp_sex").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("trend_filter_simd_prop_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("trend_filter_simd_prop_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("trend_filter_simd_prop_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("trend_filter_simd_prop_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("filter_trend_simd_pop").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("filter_trend_simd_pop").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("filter_hb_simd_pop").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("filter_hb_simd_pop").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
    document.getElementById("filter_ijb_simd_pop").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("filter_ijb_simd_pop").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("filter_ldp_simd").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("filter_ldp_simd").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
    document.getElementById("trend_filter_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue("NHS Ayrshire & Arran", false);

  document.getElementById("trend_filter_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("trend_filter_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("Aberdeen City", false);

  document.getElementById("trend_filter_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
 
   document.getElementById("trend_filter_pop").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("trend_filter_pop").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("trend_filter_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue("NHS Ayrshire & Arran", false);

  document.getElementById("trend_filter_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
   document.getElementById("trend_filter_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("Aberdeen City", false);

  document.getElementById("trend_filter_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
 
   document.getElementById("trend_filter_pop").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("trend_filter_pop").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("trend_filter_year_hb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("trend_filter_year_hb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("trend_filter_year_ijb").getElementsByClassName("selectized") 
  [0].selectize.setValue("2023/24", false);

  document.getElementById("trend_filter_year_ijb").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  document.getElementById("trend_filter_outcomes_exp").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("trend_filter_outcomes_exp").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
    document.getElementById("trend_filter_outcomes_met").getElementsByClassName("selectized") 
  [0].selectize.setValue("Scotland", false);

  document.getElementById("trend_filter_outcomes_met").getElementsByClassName("selectized")
  [0].selectize.removeOption("");
  
  
  }
  
  window.onload = filter_default;

```
