`r if_else(max_fy == sel_fy, hb, paste0(hb, " ", str_replace(sel_fy, "/", ""), ' {.hidden}'))`
=================================================

```{r summary figures, include=FALSE}

# Expected vs Referrals
ref <- sum(subpage_data$referrals)
exp_rate <- (ref / exp) * 100

# 12 Months Complete
num <- subpage_data %>% filter(ldp %in% c("complete", "exempt")) %>% {sum(.$referrals)}
den <- subpage_data %>% filter(ldp %in% c("complete", "exempt", "fail")) %>% {sum(.$referrals)}
pds_rate <- (num / den) * 100

# Format figures with thousands separator
ref_format <- format(ref, big.mark = ",")
exp_format <- format(exp, big.mark = ",")
num_format <- format(num, big.mark = ",")
den_format <- format(den, big.mark = ",")

# Is there data for all four quarters of the selected year?
complete_year <- if_else(max_fy == sel_fy & qt != 4, FALSE, TRUE)

# If incomplete year, list quarters included
qt_text <-
  if(complete_year){""}else{
    if(qt == 1){"- Q1"}else{
      if(qt %in% 2:3){paste0("- Q1-", qt)}
    }
  }

# Text to explain incomplete years / referrals still ongoing
completeness_text <-
  case_when(
    complete_year == FALSE ~ 
      paste0("LDP Standard performance figures are not provided ",
             "until data is available for the full financial year."),
    sel_fy == min_fy ~ 
      paste0("The figures shown are now complete for this financial year and ",
             "should not change in future versions of these reports. However, ",
             "slight variations may be seen as data errors are resolved."),
    TRUE ~ 
      paste0("As PDS for some referrals in ", sel_fy, " is still ongoing, ",
             "it is not known yet whether or not they will meet the LDP ",
             "standard. Therefore, the figures shown are currently provisional",
             " and subject to change in future versions of this report.")
  )

# Title for LDP table
table_title <-
  ifelse(complete_year == TRUE,
          "",
          paste0(" - up to Q", qt))

```


Sidebar {.sidebar}
-----------------------------------------------------------------------



### `r hb`
#### Financial Year `r paste(sel_fy, qt_text)`

***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

Select Financial Year

|     `r paste0(if_else(sel_fy == "2020/21", "[**2020/21**]", "[2020/21]"), "(#", hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"), "-3)")`
|     `r paste0(if_else(sel_fy == "2019/20", "[**2019/20**]", "[2019/20]"), "(#", hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"), "-", "201920)")`
|     `r paste0(if_else(sel_fy == "2018/19", "[**2018/19**]", "[2018/19]"), "(#", hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"), "-", "201819)")`
|     `r paste0(if_else(sel_fy == "2017/18", "[**2017/18**]", "[2017/18]"), "(#", hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"), "-", "201718)")`

***

For more information regarding how the LDP Standard is calculated and how individuals with multiple records are presented, please see the [methodology](#methodology) page.

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@nhs.net](mailto:phs.dementiapds@nhs.net)


Row
----------------------------------------------------------------------

### **Note**

These reports are an ongoing development following the implementation of the revised [Dementia PDS dataset](https://www.isdscotland.org/Health-Topics/Mental-Health/Dementia-Post-diagnostic-Support/_docs/Dementia-PDS-Definitions-and-Recording-Guidance.pdf) effective 01 April 2019. As such, they are currently marked as **DRAFT** and may be subject to change in future versions.

`r completeness_text`


Row `r if(complete_year == FALSE)"{.hidden}"` 
----------------------------------------------------------------------

`r ifelse(complete_year == TRUE, "### Expected Value Box", "")`
```{r Expected Value Box, include = complete_year}
valueBox(paste0(round_half_up(exp_rate, 1), "%"), 
         caption = glue("of people estimated to be newly diagnosed with ",
                        "dementia were referred for post-diagnostic support."))
```

`r ifelse(complete_year == TRUE, "### <span style='color:CornflowerBlue'>**How is this figure calculated?**</span>", "")`

`r ifelse(complete_year == TRUE, glue("A total of <span style='color:CornflowerBlue'>**{ref_format}**</span> referrals were made to post-diagnostic support. This is divided by <span style='color:CornflowerBlue'>**{exp_format}**</span>, the estimated number of people newly diagnosed with dementia."), "")`

Row `r if(complete_year == FALSE)"{.hidden}"`
----------------------------------------------------------------------

`r ifelse(complete_year == TRUE, "### 12 Months Value Box", "")`
```{r 12 Months Value Box, include = complete_year}
valueBox(paste0(round_half_up(pds_rate, 1), "%"), 
         caption = glue("of those referred for post-diagnostic support ",
                        "received a minimum of 12 months of support."))
```

`r ifelse(complete_year == TRUE, "### <span style='color:CornflowerBlue'>**How is this figure calculated?**</span>", "")`

`r ifelse(complete_year == TRUE, glue("<span style='color:CornflowerBlue'>**{num_format}**</span> of referrals either met or were exempt from the LDP standard. This is divided by <span style='color:CornflowerBlue'>**{den_format}**</span>, the total number of referrals (excluding those whose support is ongoing)."), "")`


Row
----------------------------------------------------------------------

### **Number of Individuals relating to LDP Standard**: Financial Year `r paste0(sel_fy, table_title)`

```{r ldp-table}

ldp_table(subpage_data,
          scotland = TRUE,
          include_pc = complete_year)

```


Row {.data-height=1000}
----------------------------------------------------------------------

### **Number of Individuals Diagnosed and Referred for PDS** {data-width=800}

```{r referrals-plot}

plot_referrals(subpage_data, 
               scotland = TRUE,
               quarter = ifelse(max_fy == sel_fy, qt, NA))

```


Row
-----------------------------------------------------------------------
