`r if_else(max_fy == sel_fy, paste0(hb, '{data-navmenu="Health Boards"}'), paste0(hb, " ", str_replace(sel_fy, "/", ""), ' {.hidden}'))`
=================================================

```{r summary figures, include=FALSE}

# Expected vs Referrals
ref <- sum(subpage_data$referrals)
exp_rate <- (ref / exp) * 100

# 12 Months Complete
num <- subpage_data %>% filter(ldp %in% c("complete", "exempt")) %>% {sum(.$referrals)}
den <- subpage_data %>% filter(ldp %in% c("complete", "exempt", "fail")) %>% {sum(.$referrals)}
pds_rate <- (num / den) * 100

# Format figures with thousands separator
ref_format <- format(ref, big.mark = ",")
exp_format <- format(exp, big.mark = ",")
num_format <- format(num, big.mark = ",")
den_format <- format(den, big.mark = ",")

# Is there data for all four quarters of the selected year?
complete_year <- if_else(max_fy == sel_fy & qt != 4, FALSE, TRUE)

# If incomplete year, list quarters included
qt_text <-
  if(complete_year){""}else{
    if(qt == 1){"- Q1"}else{
      if(qt %in% 2:3){paste0("- Q1-", qt)}
    }
  }

# Title for LDP table
table_title <-
  ifelse(complete_year == TRUE,
          "",
          paste0(" - up to Q", qt))


# text to state impact of Covid 19
covid_text <-
  case_when(
    str_sub(sel_fy, 1, 4) == "2020" ~
    "**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS have been affected by the COVID-19 pandemic.**",
    TRUE ~ ""
  )

# Text to explain incomplete years / referrals still ongoing
latest_final_year <- dmy(paste0("0104",substr(finalised_years[length(finalised_years)],1,4)))

completeness_text <-
  case_when(
    str_sub(sel_fy, 1, 4) <= year(latest_final_year) ~
      paste0("Data for ", sel_fy, " are now final and will not change in ",
             "future versions of this report."),
    str_sub(sel_fy, 1, 4) == year(latest_final_year + years(1)) ~
      paste0("The figures shown for ", sel_fy, " are currently provisional and subject to ",
             "change in future versions of this report."),
    complete_year == FALSE ~ 
      paste0("The figures shown for ", sel_fy, " are currently provisional and subject to ",
             "change in future versions of this report. ",
             "LDP Standard performance figures are not provided ",
             "until data is available for the full financial year."),
    TRUE ~ 
      paste0("The figures shown for ", sel_fy, " are currently provisional and subject to ",
             "change in future versions of this report." ,
             "As PDS for some referrals is still ",
             "ongoing, it is not known yet whether or not they ",
             "will meet the LDP standard." )
  )


# Estimated dementia diagnosis dates note
est_date1 <- dmy(01042021)
est_date2 <- dmy(01042022)
est_date3 <- dmy(01042023)
est_date4 <- dmy(01042024)

  est_text <-  
    case_when(sel_fy == extract_fin_year(est_date1) | sel_fy == extract_fin_year(est_date2) | sel_fy == extract_fin_year(est_date3) | sel_fy == extract_fin_year(est_date4) ~
      paste0("",
             "**Please note:** ",
             "In December 2016, the Scottish Government published a report: 2014-2020 ",
             "Estimated and Projected Diagnosis Rates for Dementia in Scotland:",
             "(https://www.gov.scot/publications/estimated-projected-diagnosis-rates-dementia-scotland-2014-2020/). ", 
             "For financial years *2021/22*, *2022/23*, *2023/24*, and *2024/25* the rates referenced in ", 
             "the report were used to create national, age specific rates of dementia incidence ",
             "per 1,000 population which were then applied to the National Records of ",
             "Scotland (NRS) Mid-2021 Population Estimates to obtain the incidence estimates."),
      TRUE ~ paste0(""))
  

# Data quality notes - Aberdeen City
  ac_date1 <- dmy(01042019)
  ac_date2 <- dmy(01042020)

  ac_text <-  
    case_when(hb == "NHS Grampian" & sel_fy == extract_fin_year(ac_date1) |
              hb == "NHS Grampian" & sel_fy == extract_fin_year(ac_date2) ~
      paste0("",
             "**Please note:** ",
             "*Aberdeen City Health & Social Care Partnership changed ",
             "to provide PDS in 2019 to an inhouse hybrid model. ",
             "This change in model, and process of receiving referrals and recording, ",
             "resulted in data quality issues for financial years 2019/20 and 2020/21. ",
             "This should be taken into account when interpreting figures for Aberdeen City and NHS Grampian.*"),
          TRUE ~ paste0(""))
  
  
  # Data quality notes - Perth & Kinross
  tay_date1 <- dmy(01042018)
  tay_date2 <- dmy(01042019)
  tay_date3 <- dmy(01042023)
  tay_date4 <- dmy(01042024)
  
  tay_text <-  
    case_when(hb == "NHS Tayside" & sel_fy == extract_fin_year(tay_date1) |
              hb == "NHS Tayside" & sel_fy == extract_fin_year(tay_date2) ~
        paste0(" ", 
           "**Please note:** ",
           "*NHS Tayside experienced challenges in capturing and reporting on electronic ", 
           "system data within Perth & Kinross over the period 2018/19 to 2019/20. ", 
           "Despite local work undertaken to uncover the missing data, it has not been ",
           "possible to fill this gap. Subsequent measures put in place have successfully ", 
           "allowed NHS Tayside to improve on data reporting from 2019 onwards.*"),
      hb == "NHS Tayside" & sel_fy == extract_fin_year(tay_date3)|
      hb == "NHS Tayside" & sel_fy == extract_fin_year(tay_date4)~
        paste0(" ", 
            "**Please note:** ",
              "*PHS have identified issues with the data submitted by NHS Tayside for 2023/24 ", 
              "and 2024/25, which has resulted in some records showing as incorrectly having met the standard. ",
              "NHS Tayside has informed PHS that these data issues will be rectified once they have completed the ", 
              "migration to a new IT system. This is likely to be completed by the end of the year.*"), 
    TRUE ~ paste0(""))
  
  
    # Data Quality notes -  Orkney
    date22_23 <- dmy(01042022)
    date23_24 <- dmy(01042023)
  
  orkney_text <- 
    case_when(hb == "NHS Orkney" & sel_fy == extract_fin_year(date22_23) | 
              hb == "NHS Orkney" & sel_fy == extract_fin_year(date23_24) ~ 
              paste0(" ",
             "**Please note:** ",
             "*NHS Orkney had no referrals in 2022/23 (Q3 and Q4) and 2023/24 ",
             "(Q1 and Q2) as they were unable to access a consultant psychiatrist.*"),
    TRUE ~ paste0(""))
    
    
  # Data Quality notes - Shetland
  
  date22_23 <- dmy(01042022)
  date23_24 <- dmy(01042023)

  shetland_text <-  
    case_when(hb == "NHS Shetland" & sel_fy == extract_fin_year(date22_23) | 
              hb == "NHS Shetland" & sel_fy == extract_fin_year(date23_24) ~
               paste0(" ",
             "**Please note:** ",
              "*NHS Shetland did not have a PDS worker in post from 2022/23 Q1 through ", 
              "2023/24 Q3. As a result not all people referred to PDS could be allocated or ", 
              "contacted by a PDS worker within 12 months of diagnosis, hence they have been ", 
              "recorded as not having met the standard. A PDS worker was assigned in 2023/24 Q4 ",
              "and the PDS service in Shetland has resumed.*"), 
      TRUE ~ paste0(""))
  
  
   # Data quality notes - fife
  fife_date <- dmy(01042024)

  fife_text <-  
    case_when(hb == "NHS Fife" & sel_fy == extract_fin_year(fife_date) ~
      paste0(" ",
              "**Please note:** ",
              "*PHS have identified one record submitted by NHS Fife ", 
              "for 2024/25 that shows inconsistent dates. The reported dates resulted in this record ",
              "showing as having met the standard. PHS have queried the ", 
              "dates with the Health Board and expecting these to be rectified in future submissions.*"),  TRUE ~ paste0(""))
  
     # Data quality notes - borders
  bord_date <- dmy(01042024)

  bord_text <-  
    case_when(hb == "NHS Borders" & sel_fy == extract_fin_year(bord_date) ~
      paste0(" ",
              "**Please note:** ",
              "*PHS have identified one record submitted by NHS Borders ", 
              "for 2024/25 that shows inconsistent dates. The reported dates resulted in this record ",
              "showing as having met the standard. PHS have queried the ", 
              "dates with the Health Board and are expecting these to be rectified in future submissions.*"), TRUE ~ paste0(""))
  
     # Data quality notes - lanarkshire
  lan_date <- dmy(01042024)

  lan_text <-  
    case_when(hb == "NHS Lanarkshire" & sel_fy == extract_fin_year(lan_date) ~
      paste0(" ",
             "**Please note:** ",
              "*PHS have identified two records submitted by NHS Lanarkshire ", 
              "for 2024/25 that show inconsistent dates. The reported dates resulted in these records ",
              "showing as having met the standard. PHS have queried the ", 
              "dates with the Health Board and are expecting these to be rectified in future submissions.*"),  TRUE ~ paste0(""))

```

Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

### `r hb`
#### Financial Year `r paste(sel_fy, qt_text)`

***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

Select Financial Year

```{r fy-page-links, results='asis'}
fy_text <- case_when(
  all_fy == sel_fy ~ md_bold(all_fy),
  TRUE ~ all_fy
)

fy_url <- paste0(
  "#",
  hb %>% tolower() %>% str_replace_all(" &", "") %>% str_replace_all(" ", "-"),
  "-",
  case_when(
    all_fy == max(all_fy) ~ as.character(length(all_fy) - 1),
    TRUE ~ str_remove_all(all_fy, "/")
  )
)

md_link(
  text = fy_text,
  url = fy_url
) %>%
  md_list()
```

***

**FURTHER INFORMATION:**

<ul style="list-style-type:square;">
   <li >[Standard Not Met / PDS Ongoing (Pathways - PDS Outcomes)](#outcomes)</li>
   <li >[Methodology](#methodology)</li>
   <li >[Glossary](#glossary)</li>
   <li >[Navigation Guide](#navigation-guide)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)


Row
----------------------------------------------------------------------

### **Note**

`r covid_text`

`r completeness_text`

`r est_text`

`r ac_text`

`r tay_text`

`r shetland_text`

`r orkney_text`

`r fife_text`

`r bord_text`

`r lan_text`

Row `r if(complete_year == FALSE)"{.hidden}"` 
----------------------------------------------------------------------

`r ifelse(complete_year == TRUE, "### Expected Value Box", "")`
```{r Expected Value Box, include = complete_year}
valueBox(paste0(round_half_up(exp_rate, 1), "%"), 
         caption = glue("of people estimated to be newly diagnosed with ",
                        "dementia were referred for post-diagnostic support."))
```

`r ifelse(complete_year == TRUE, "### <span style='color:CornflowerBlue'>**How is this figure calculated?**</span>", "")`

`r ifelse(complete_year == TRUE, glue("A total of <span style='color:CornflowerBlue'>**{ref_format}**</span> referrals were made to post-diagnostic support. This is divided by <span style='color:CornflowerBlue'>**{exp_format}**</span>, the estimated number of people newly diagnosed with dementia."), "")`

Row `r if(complete_year == FALSE)"{.hidden}"`
----------------------------------------------------------------------

`r ifelse(complete_year == TRUE, "### 12 Months Value Box", "")`
```{r 12 Months Value Box, include = complete_year}
valueBox(if_else(!is.na(pds_rate),paste0(format(round_half_up(pds_rate, 1)), "%"), "NA"), 
         caption = glue("of those referred for post-diagnostic support ",
                        "received a minimum of 12 months of support."))
```

`r ifelse(complete_year == TRUE, "### <span style='color:CornflowerBlue'>**How is this figure calculated?**</span>", "")`

`r ifelse(complete_year == TRUE, glue("<span style='color:CornflowerBlue'>**{num_format}**</span> referrals either met or were exempt from the LDP standard. This is divided by <span style='color:CornflowerBlue'>**{den_format}**</span>, the total number of referrals (excluding those whose support is ongoing)."), "")`


Row
----------------------------------------------------------------------

### **Number of Individuals relating to LDP Standard**: Financial Year `r paste0(sel_fy, table_title)`

```{r ldp-table}

ldp_table(subpage_data,
          include_pc = complete_year)

```


Row {.data-height=1000}
----------------------------------------------------------------------

### **Number of Individuals Diagnosed and Referred for PDS** {data-width=800}

```{r referrals-plot}

plot_referrals(subpage_data, 
               scotland = FALSE,
               quarter = ifelse(max_fy == sel_fy, qt, NA))

```

<!-- END OF SCRIPT -->