All Referrals - Trends & Rates
=================================================

```{r data-trends, include=FALSE}

# Referrals
referrals <- standardised_rates %>%
  select(fy, geog, name, total_referrals)

# Referral Rates (Per 10,000 Population)
referral_rates <- standardised_rates %>% 
  select(fy, geog, name, all_of(contains("rate"))) %>%
  pivot_longer(cols = contains("rate"), names_to = "rate_type", values_to = "rate") %>%
  mutate(rate = round(rate, 1))

# Outcomes (Rates Per Expected Diagnoses & Percentage Standard Met)
outcomes <- measures %>%
  select(fy, geog, name, exp_rate, perc_met)

```

```{r functions-trends, include=FALSE}

create_static_table <- function(data, measure, geog_filter) {
  
  geog_name <- case_when(
    "ijb" %in% geog_filter & "health_board" %in% geog_filter ~ "Integration Authority Area/Health Board",
    "ijb" %in% geog_filter ~ "Integration Authority Area",
    "health_board" %in% geog_filter ~ "Health Board"
  )
  
  static_table <- data %>%
    arrange(desc(name)) %>%
    filter(name %in% geog_filter) %>%
    select(geog, fy, {{ measure }}) %>%
    mutate(across(where(is.numeric), ~ if_else(. %% 1 == 0, 
                                               format(., big.mark = ","), 
                                               paste0(., "%")))) %>%
    pivot_wider(names_from = fy, values_from = {{ measure }}) %>%
    rename(!!geog_name := geog) %>%
    kable(align = c("l", rep("r", length(unique(data$fy))))) %>%
    kable_styling(full_width = TRUE, c("striped", "hover")) %>%
    column_spec(1, bold = TRUE) %>%
    add_header_above(c(" " = 1, "Financial Year of Diagnosis" = length(unique(data$fy)))) %>%
    scroll_box(height = "685px")
  
  return(static_table)
}


create_dynamic_table <- function(data, measure, geog_filter, dropdown_col, dropdown_grp) {
  
  geog_name <- case_when(
    "ijb" %in% geog_filter & "health_board" %in% geog_filter ~ "Integration Authority Area/Health Board",
    "ijb" %in% geog_filter ~ "Integration Authority Area",
    "health_board" %in% geog_filter ~ "Health Board")
  
  table_data <- SharedData$new(
    data %>%
      filter(name %in% geog_filter) %>%
      select(geog, fy, name, rate_type, {{ measure }}) %>%
      pivot_wider(names_from = fy, values_from = {{ measure }}) %>%
      { if (dropdown_col == "fy") crossing(., x = unique(data[[dropdown_col]])) else mutate(., x = .data[[dropdown_col]]) } %>%
      arrange(desc(name)) %>%
      rename(!!geog_name := geog),
  key = ~paste0(x, rate_type),
  group = dropdown_grp)
  
  fy_targets <- which(grepl("/", names(table_data$origData()))) - 1
  
  bscols(
    widths = 12, 
    div(
      style = css(width="97%", height="560px", margin="20px"),
      DT::datatable(
        table_data, 
        rownames = FALSE, 
        selection = 'none',
        options = list(
          pageLength = nrow(table_data$origData()),
          scrollX = TRUE,
          scrollY = TRUE,
          dom = "t",
          ordering = FALSE,
          columnDefs = list(
            list(visible = FALSE, targets = c("rate_type", "x", "name")),
            list(className = 'dt-right', targets =  as.list(fy_targets))))) %>%
        DT::formatStyle(
          columns = geog_name, 
          fontWeight = "bold") %>%
        DT::formatStyle(
          columns = "name",
          target = "row",
          fontWeight = DT::styleEqual("scot", "bold"))))
}

```

Sidebar - trend {.sidebar}
-----------------------------------------------------------------------

<br>

### All Referrals - Trend
***

<font size="2"> 
<span style="color:red"> **MANAGEMENT INFORMATION: FOR LIMITED INTERNAL DISTRIBUTION AND NOT FOR PUBLIC RELEASE.** </span> </font>

***

<ul>
  <li>[**All Referrals - Trend**](#all-referrals---trends-rates)</li>
  <li>[All Referrals - Rates per 10,000 population](#pop-rates)</li>
  <li>[All Referrals - Outcomes by Financial Year](#trend-outcomes)</li>
</ul>

***
**FURTHER INFORMATION:**

<ul style="list-style-type:square;">
   <li >[About This Report](#home)</li>
   <li >[Glossary](#glossary)</li>
   <li >[Navigation Guide](#navigation-guide)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)


Row
----------------------------------------------------------------------

### **Note**

<span style="color:red"> **MANAGEMENT INFORMATION: FOR LIMITED INTERNAL DISTRIBUTION AND NOT FOR PUBLIC RELEASE.** </span>

This page includes a chart and table showing the trend for number of people referred to PDS by financial year for Scotland, Integration Authority Areas and Health Boards. Multiple areas can be selected in the Integration Authority and Health Board tabs. 

*The figures shown for `r provisional_year` onwards are currently provisional and subject to change in future versions of this report.*  

`r if(qt != 4) {div(style = css(fontStyle="italic"),paste0("For diagnoses in financial year ", current_fy, " data is available up to and including Q", qt, "."))}`
<br>
*See Additional Notes on [Home](#home) page for further information on data issues with specific Boards/Integration Authority Areas/Financial Years.*  

Row {.tabset data-height=1210}
----------------------------------------------------------------------

### **Scotland**

<br>
<br>
<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px"> Number of Individuals Diagnosed and Referred for PDS; Scotland</h2>

```{r trend-plot}

# Static Plot Data (All Referrals)
referrals_df_scot <- SharedData$new(
  referrals %>%  
  filter(name == "scot"))

# Plot (All Referrals)
referrals_plot_scot <- plot_trend(
  data = referrals_df_scot, 
  measure = total_referrals, 
  x ="Financial Year of Diagnosis", 
  y = "Number Referred", 
  measure_text = "Referrals: ", 
  Scotland = TRUE)

# Layout
bscols(widths = 12, div(style = css(width="98%", height="360px"), referrals_plot_scot))

```

<br>
<br>

```{r trend-table}

# Static Table (All Referrals)
create_static_table(
  data = referrals, 
  measure = total_referrals,
  geog_filter = c("ijb", "health_board", "scot"))
 
```

### **Integration Authority Areas**

```{r dropdown-ijb}

# Dynamic Plot Data (Referrals by IAA)
referrals_df_ijb <- SharedData$new(
  referrals %>%  
  filter(name == "ijb"))

# Dropdown (IAA)
referrals_filter_ijb <- filter_select(
  id = "trend_filter_ijb",
  label = "Select Integration Authority Area(s):",
  group = ~geog,
  sharedData = referrals_df_ijb,
  multiple = TRUE)

# Layout
bscols(widths = c(1,10,NA), NULL, referrals_filter_ijb, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px">Number of Individuals Diagnosed and Referred for PDS; Integration Authority Areas </h2>

```{r trend-plot-ijb}

# Dynamic Plot (Referrals by IAA)
referrals_plot_ijb <- plot_trend(
  data = referrals_df_ijb, 
  measure = total_referrals, 
  x ="Financial Year of Diagnosis", 
  y = "Number Referred", 
  measure_text = "Referrals: ", 
  colours = phs_colours_31)

# Layout
bscols(widths = 12, div(style = css(width="98%", height="360px"), referrals_plot_ijb))

```

```{r trend-table-ijb}

# Static Table (Referrals by IAA)
create_static_table(
  data = referrals, 
  measure = total_referrals,
  geog_filter = c("ijb", "scot"))
 
```

### **Health Boards**

```{r dropdown-hb}

# Dynamic Plot Data (Referrals by Health Board)
referrals_df_hb <- SharedData$new(
  referrals %>%  
  filter(name == "health_board"))
  
# Dropdown (Health Board)
referrals_filter_hb <- filter_select(
  id = "trend_filter_hb",
  label = "Select Health Board(s):",
  group = ~geog,
  sharedData = referrals_df_hb,
  multiple = TRUE)

# Layout
bscols(widths = c(1,10,NA), NULL, referrals_filter_hb, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px">Number of Individuals Diagnosed and Referred for PDS; Health Boards </h2>

```{r trend-plot-hb}

# Dynamic Plot (Referrals by Health Board)
referrals_plot_hb <- plot_trend(
  data = referrals_df_hb, 
  measure = total_referrals, 
  x ="Financial Year of Diagnosis", 
  y = "Number Referred", 
  measure_text = "Referrals: ", 
  colours = phs_colours_14)

# Layout
bscols(widths = 12, div(style = css(width="98%", height="360px"), referrals_plot_hb))

```

```{r trend-table-hb}

# Static Table (Referrals by Health Board)
create_static_table(
  data = referrals, 
  measure = total_referrals,
  geog_filter = c("health_board", "scot"))

```

Pop Rates {.hidden}
=====================================
Sidebar - rates {.sidebar}
-----------------------------------------------------------------------

<br>

### All Referrals - Rates per 10,000 population 

***

<font size="2"> 
<span style="color:red"> **MANAGEMENT INFORMATION: FOR LIMITED INTERNAL DISTRIBUTION AND NOT FOR PUBLIC RELEASE.** </span></font>

***
<ul>
  <li>[All Referrals - Trend](#all-referrals---trends-rates)</li>
  <li>[**All Referrals - Rates per 10,000 population**](#pop-rates)</li>
  <li>[All Referrals - Outcomes by Financial Year](#trend-outcomes)</li>
</ul>

***
**FURTHER INFORMATION:**

<ul style="list-style-type:square;">
   <li >[Glossary](#glossary)</li>
   <li >[Navigation Guide](#navigation-guide)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)


Row
----------------------------------------------------------------------

### **Note**

<span style="color:red"> **MANAGEMENT INFORMATION: FOR LIMITED INTERNAL DISTRIBUTION AND NOT FOR PUBLIC RELEASE.** </span>

This page includes rates of the number of people referred to PDS per 10,000 population (65 years and over). Note that for financial year *2024/25* and *2025/26* the Mid-2023 populations are used as this is the latest available estimate.<!-- UPDATE when new population estimates are available / when new financial year begins --> *See the [Glossary](#glossary) for more details.*

The Integration Authority Area and Health Board tabs include a chart and table showing the rate for each geographical area by financial year. 

The Trend tab includes a chart and table showing the trend of the rate by financial year for Scotland, Integration Authority Areas and Health Boards. Multiple areas can be selected.  

*The figures shown for `r provisional_year` onwards are currently provisional and subject to change in future versions of this report.*  

`r if(qt != 4) {div(style = css(fontStyle="italic"),paste0("For diagnoses in financial year ", current_fy, " data is available up to and including Q", qt, "."))}`
<br>
*See Additional Notes on [Home](#home) page for further information on data issues with specific Boards/Integration Authority Areas/Financial Years.*  

Row {.tabset data-height=1260}
----------------------------------------------------------------------

### **Integration Authority Areas**

```{r dropdown-pop-ijb}
  
# Dynamic Plot Data (Referral Rates by IAA and Rate Type)
rates_df_ijb <- SharedData$new(
  referral_rates %>%  
    filter(name == "ijb"),
  key = ~paste0(fy, rate_type), 
  group = "ratesijb")
  
# Dynamic Plot Data (Scotland Referral Rates by Rate Type)
rates_df_scot1 <- SharedData$new(
    referral_rates %>%  
    filter(name == "scot"),
  key = ~paste0(fy, rate_type), 
  group = "ratesijb")

# Dropdown (Year)
rates_filter_ijb_year <- filter_select(
  id = "trend_filter_year_ijb",
  label = "Select Financial Year:",
  group = ~fy,
  sharedData = rates_df_ijb,
  multiple = FALSE)

# Dropdown (Rate Type)
rates_filter_ijb_rate <- filter_select(
  id = "trend_filter_rate_ijb",
  label = "Select Rate Measure:",
  group = ~rate_type,
  sharedData = rates_df_ijb,
  multiple = FALSE)

# Layout
bscols(widths = c(1, 4, 4, NA), NULL, rates_filter_ijb_year, rates_filter_ijb_rate, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px"> Number of Individuals Diagnosed and Referred for PDS per 10,000 Population (65+); Integration Authority Areas</h2>

```{r plot-ijb-pop}

# Dynamic Plot (Referral Rates by IAA and Rate Type)
rates_plot_ijb <- plot_bar_pop_rate(
  bar_data = rates_df_ijb,
  line_data = rates_df_scot1,
  x = geog,
  y = rate)

# Layout
bscols(widths = 12, div(style = css(width="98%", height="410px"), rates_plot_ijb))

```

```{r trend-table-ijb-pop}

# Dynamic Table (Referral Rates by IAA and Rate Type)
create_dynamic_table(
  data = referral_rates, 
  measure = "rate", 
  geog_filter = c("scot", "ijb"),
  dropdown_col = "fy",
  dropdown_grp = "ratesijb")

```

### **Health Boards**

```{r dropdown-pop-hb}

# Dynamic Plot Data (Referral Rates by Health Board and Rate Type)
rates_df_hb <- SharedData$new(
  referral_rates %>%  
    filter(name == "health_board"),
  key = ~paste0(fy, rate_type), 
  group = "rateshb")
  
# Dynamic Plot Data (Scotland Referral Rates by Rate Type)
rates_df_scot2 <- SharedData$new(
    referral_rates %>%  
    filter(name == "scot"),
  key = ~paste0(fy, rate_type), 
  group = "rateshb")

# Dropdown (Year)
rates_filter_hb_year <- filter_select(
  id = "trend_filter_year_hb",
  label = "Select Financial Year:",
  group = ~fy,
  sharedData = rates_df_hb,
  multiple = FALSE)

# Dropdown (Rate Type)
rates_filter_hb_rate <- filter_select(
  id = "trend_filter_rate_hb",
  label = "Select Rate Measure:",
  group = ~rate_type,
  sharedData = rates_df_hb,
  multiple = FALSE)

# Layout
bscols(widths = c(1, 4, 4, NA), NULL, rates_filter_hb_year, rates_filter_hb_rate, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px"> Number of Individuals Diagnosed and Referred for PDS per 10,000 Population (65+); Health Boards</h2>

```{r plot-hb-pop}
 
# Dynamic Plot (Referral Rates by Health Board and Rate Type)
rates_plot_hb <- plot_bar_pop_rate(
  bar_data = rates_df_hb,
  line_data = rates_df_scot2,
  x = geog,
  y = rate)

# Layout
bscols(widths = 12, div(style = css(width="98%", height="410px"), rates_plot_hb))

```

```{r trend-table-hb-pop}

# Dynamic Table (Referral Rates by Health Board and Rate Type)
create_dynamic_table(
  data = referral_rates, 
  measure = "rate", 
  geog_filter = c("scot", "health_board"),
  dropdown_col = "fy",
  dropdown_grp = "rateshb")

```

### **Trend**

```{r dropdown-pop}
# Dynamic Plot Data (Scotland Referral Rates by Rate Type)
rates_df_all <- SharedData$new(
  referral_rates, 
  key = ~paste0(geog, rate_type), 
  group = "ratesall")

# Dropdown (Geography)
rates_filter_all_geog <- filter_select(
  id = "trend_filter_geog_trend",
  label = "Select Integration Authority Area(s) or Health Board(s):",
  group = ~geog,
  sharedData = rates_df_all,
  multiple = TRUE)

# Dropdown (Rate Type)
rates_filter_all_rate <- filter_select(
  id = "trend_filter_rate_trend",
  label = "Select Rate Measure:",
  group = ~rate_type,
  sharedData = rates_df_all,
  multiple = FALSE)

# Layout
bscols(widths = c(1, 4, 4, NA), NULL, rates_filter_all_geog, rates_filter_all_rate, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px"> Number of Individuals Diagnosed and Referred for PDS per 10,000 Population (65+)</h2>

```{r trend-plot-pop}

# Dynamic Plot (Scotland Referral Rates by Rate Type)
rates_plot_all <- plot_trend(
  data = rates_df_all, 
  measure = rate, 
  x ="Financial Year of Diagnosis", 
  y = "Rate Per 10,000 Popuation", 
  colours = phs_colours_46, 
  measure_text = "Rate per 10,000 population: ")

# Layout
bscols(widths = 12, div(style = css(width="98%", height="360px"), rates_plot_all))

```

```{r trend-table-pop}

# Dynamic Table (Referral Rates by IAA and Rate Type)
create_dynamic_table(
  data = referral_rates, 
  measure = "rate", 
  geog_filter = c("scot", "ijb", "health_board"),
  dropdown_col = "geog",
  dropdown_grp = "ratesall")

```

Trend Outcomes {.hidden}
=====================================
Sidebar - outcomes {.sidebar}
-----------------------------------------------------------------------

<br>

### All Referrals - Outcomes by Financial Year 

***

<font size="2"> 
<span style="color:red"> **MANAGEMENT INFORMATION: FOR LIMITED INTERNAL DISTRIBUTION AND NOT FOR PUBLIC RELEASE.** </span> </font>

***
<ul>
  <li>[All Referrals - Trend](#all-referrals---trends-rates)</li>
  <li>[All Referrals - Rates per 10,000 population](#pop-rates)</li>
  <li>[**All Referrals - Outcomes by Financial Year**](#trend-outcomes)</li>
</ul>

***
**FURTHER INFORMATION:**

<ul style="list-style-type:square;">
   <li >[Methodology](#methodology)</li>
   <li >[Glossary](#glossary)</li>
   <li >[Navigation Guide](#navigation-guide)</li>
</ul>


***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)


Row
----------------------------------------------------------------------

### **Note**

<span style="color:red"> **MANAGEMENT INFORMATION: FOR LIMITED INTERNAL DISTRIBUTION AND NOT FOR PUBLIC RELEASE.** </span>

This page includes charts and tables showing, for the selected areas, the trend by financial year for information relating to the LDP Standard.  

The first tab shows the percentage of the estimated number of people newly diagnosed with dementia that have been referred to PDS for Scotland and Health Boards (estimates are not available for Integration Authority Areas). 

The second tab shows the percentage of referrals that have received one year’s support which started within a year of diagnosis (or have been exempt from the LDP Standard) for Scotland, Integration Authority Areas and Health Boards. 

*The figures shown for `r provisional_year` onwards are currently provisional and subject to change in future versions of this report.*  

`r if(qt != 4) {div(style = css(fontStyle="italic"),paste("LDP Standard performance figures are not provided until data is available for the full financial year."))}`
<br>
*See Additional Notes on [Home](#home) page for further information on data issues with specific Boards/Integration Authority Areas/Financial Years.*  

Row {.tabset data-height=1215}
----------------------------------------------------------------------

### **Percentage of estimated diagnoses referred to PDS**

```{r dropdown-exp}

# Dynamic Plot Data (Expected Diagnosis Rates by Health Board)
exp_df <- SharedData$new(
  outcomes %>%
    filter(name %in% c("scot", "health_board")))

# Dropdown (Health Board)
filter_exp <- filter_select(
  id = "trend_filter_outcomes_exp",
  label = "Select Health Board(s):",
  group = ~geog,
  sharedData = exp_df)

# Layout
bscols(widths = c(1,10,NA), NULL, filter_exp, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px"> Percentage of people estimated to be newly diagnosed with dementia who were referred for PDS</h2>

```{r trend-plot-exp}

# Dynamic Plot (Expected Diagnosis Rates by Health Board)
exp_plot <- plot_trend_perc(
  data = exp_df, 
  measure = exp_rate, 
  x ="Financial Year of Diagnosis", 
  colours = phs_colours_15)

# Layout
bscols(widths = 12, div(style = css(width="98%", height="360px"), exp_plot))

```

```{r trend-table-exp}

# Static Table (Expected Diagnosis Rates by Health Board)
create_static_table(
  data = exp_rates, 
  measure = "exp_rate", 
  geog_filter = c("health_board", "scot"))

```

### **Percentage receiving one year's PDS support**

```{r dropdown-met-ldp}
# Dynamic Plot Data (Percentage Met)
met_df <- SharedData$new(
  outcomes)

# Dropdown (Geography)
filter_met <- filter_select(
  id = "trend_filter_outcomes_exp",
  label = "Select Health Board(s):",
  group = ~geog,
  sharedData = met_df)

# Layout
bscols(widths = c(1,10,NA), NULL, filter_met, NULL)

```

<h2 style="margin-left: 70px; margin-top: 0px; margin-bottom: 0px">Percentage of referrals who received a minimum of one year’s PDS (Standard Met/Exempt)</h2>
```{r trend-plot-met-ldp}

# Dynamic Plot (Percentage Met by Geography)
met_plot <- plot_trend_perc(
  data = met_df, 
  measure = perc_met, 
  x ="Financial Year of Diagnosis", 
  colours = phs_colours_46)

# Layout
bscols(widths = 12, div(style = css(width="98%", height="360px"), met_plot))

```


```{r trend-table-met}

# Static Table (Percentage Met by Geography)
create_static_table(
  data = outcomes, 
  measure = "perc_met", 
  geog_filter = c("ijb", "health_board", "scot"))

```

<!-- END OF SCRIPT -->
