Sidebar {.sidebar}
-----------------------------------------------------------------------

<br>

### Deprivation - Trend
***

<font size="2"> 
<span style="color:red"> 
**MANAGEMENT INFORMATION ONLY:** <br>
**NOT FOR ONWARD DISTRIBUTION**
</span> </font>

***

<ul>
  <li>[Trend](#deprivation-simd)</li>
  <li>[Proportions](#simd-proportions)</li>
  <li>[Rates per 10,000 population](#simd-rates)</li>
  <li>[Outcomes](#simd-outcomes)</li>
</ul>

***

Please get in touch with any comments, suggestions and feedback: [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)


Row
----------------------------------------------------------------------

### **Note**

**Please note that both the Dementia Post Diagnostic Support service provision and data submission to PHS were affected by the COVID-19 pandemic.**


Row {.tabset data-height=900}
----------------------------------------------------------------------

### **Scotland**

<h2 style="margin-left: 50px; margin-top: 0px; margin-bottom: 0px"> Number of people referred to PDS by SIMD Quintile and Financial Year
 </h2>
```{r plot-trend-simd-legend}

 bscols(widths = 12,
 div(id="trendsimdlegend",plot_trend_simd_legend(pds_all_simd), style="margin-bottom:-353px"))

```


```{r plot-trend-simd}
bscols(widths = 12,
  div(style = css(width="98%", height="385px"),
plot_trend_simd(pds_all_simd %>% filter(geog == "Scotland"), measure = total_referrals, y = "Number"))
)

```


```{r table-trend-simd}

trend_simd_table_data <- pds_all_simd %>% filter(geog == "Scotland") %>% 
  select(geog,fy,simd,total_referrals) %>%
  pivot_wider(names_from = fy, values_from = total_referrals) %>%
             rename(`SIMD Quintile` = simd)


bscols(widths = 12,
       div(style = css(width="97%", height="235px", margin="20px"),
DT::datatable(trend_simd_table_data, rownames = FALSE,
              options = list(pageLength = 10,
                             scrollX = TRUE,
                             scrollY = FALSE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0),
                                               list(className = 'dt-right', targets = 2:9)
                                               ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )



```

### **Health Boards**

```{r dropdown-trend-simd-hb}

pds_hb_simd_data <- SharedData$new(pds_all_simd %>% filter(grepl("NHS", geog)), key = ~geog, group = "trend_simd_hb")

data_filter_trend_simd_hb <- filter_select(id = "filter_trend_simd_hb",
                                    label = "Select Health Board:",
                                    group = ~geog,
                                    sharedData = pds_hb_simd_data,
                                    multiple = FALSE
                                      )

bscols(widths = c(1,5,NA),
       NULL,
       data_filter_trend_simd_hb,
       NULL)


```

<h2 style="margin-left: 50px; margin-top: 0px; margin-bottom: 0px"> Number of people referred to PDS by SIMD Quintile and Financial Year
 </h2>
```{r plot-trend-simd-legend-hb}

 bscols(widths = 12,
 div(id="trendsimdlegend",plot_trend_simd_legend(pds_all_simd), style="margin-bottom:-353px"))

```


```{r plot-trend-simd-hb}
bscols(widths = 12,
  div(style = css(width="98%", height="385px"),
plot_trend_simd(pds_hb_simd_data, measure = total_referrals, y = "Number"))
)

```


```{r table-trend-simd-hb}

trend_simd_table_data <- pds_all_simd %>%
  select(geog,fy,simd,total_referrals) %>%
  pivot_wider(names_from = fy, values_from = total_referrals) %>%
             rename(`SIMD Quintile` = simd)


trend_simd_table_hb <- SharedData$new(trend_simd_table_data %>% filter(grepl("NHS", geog)), key = ~geog, group = "trend_simd_hb")


bscols(widths = 12,
       div(style = css(width="97%", height="235px", margin="20px"),
DT::datatable(trend_simd_table_hb, rownames = FALSE,
              options = list(pageLength = 10,
                             scrollX = TRUE,
                             scrollY = FALSE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0),
                                               list(className = 'dt-right', targets = 2:9)
                                               ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )



```

### **Integration Authority Areas**

```{r dropdown-trend-simd-ijb}

pds_ijb_simd_data <- SharedData$new(pds_all_simd %>% filter(geog != "Scotland", !grepl("NHS", geog)), key = ~geog, group = "trend_simd_ijb")

data_filter_trend_simd_ijb <- filter_select(id = "filter_trend_simd_ijb",
                                    label = "Select Health Board:",
                                    group = ~geog,
                                    sharedData = pds_ijb_simd_data,
                                    multiple = FALSE
                                      )

bscols(widths = c(1,5,NA),
       NULL,
       data_filter_trend_simd_ijb,
       NULL)


```

<h2 style="margin-left: 50px; margin-top: 0px; margin-bottom: 0px"> Number of people referred to PDS by SIMD Quintile and Financial Year
 </h2>
```{r plot-trend-simd-legend-ijb}

 bscols(widths = 12,
 div(id="trendsimdlegend",plot_trend_simd_legend(pds_all_simd), style="margin-bottom:-353px"))

```


```{r plot-trend-simd-ijb}
bscols(widths = 12,
  div(style = css(width="98%", height="385px"),
plot_trend_simd(pds_ijb_simd_data, measure = total_referrals, y = "Number"))
)

```


```{r table-trend-simd-ijb}

trend_simd_table_data <- pds_all_simd %>%
  select(geog,fy,simd,total_referrals) %>%
  pivot_wider(names_from = fy, values_from = total_referrals) %>%
             rename(`SIMD Quintile` = simd)


trend_simd_table_ijb <- SharedData$new(trend_simd_table_data %>% filter(geog != "Scotland", !grepl("NHS", geog)), key = ~geog, group = "trend_simd_ijb")


bscols(widths = 12,
       div(style = css(width="97%", height="235px", margin="20px"),
DT::datatable(trend_simd_table_ijb, rownames = FALSE,
              options = list(pageLength = 10,
                             scrollX = TRUE,
                             scrollY = FALSE,
                             dom = "t",
                             ordering = FALSE,
                             columnDefs = list(list(visible = FALSE, targets = 0),
                                               list(className = 'dt-right', targets = 2:9)
                                               ))) %>%
           DT::formatStyle(2, fontWeight = "bold"#, padding = "4px"
                          )
        )
     )



```