---
title: "Dementia PDS Quarterly Management Report: 2018/19 Q4"
output: 
  flexdashboard::flex_dashboard:
    logo: isdscotland.png
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}

# Load environment file
source(here::here("code", "00_setup-environment.R"))

# Load functions
purrr::walk(dir(here::here("functions"), full.names = TRUE), source)

# Load PDS data
pds <- read_csv(here("data", glue("{fy}-{qt}_final-data.csv"))) %>%
  
  # Filter HB for fasther knitting when testing
  # filter(substr(health_board, 1, 1) == c("A", "B")) %>%
  
  # Remove codes from board and IJB
  mutate(health_board = str_sub(health_board, 3, -1),
         ijb          = str_sub(ijb, 11, -1))

# Load expected diagnoses reference file
exp <- read_csv(here("reference-files", "expected-diagnoses.csv"))

```

Home
=================================================

Row
-------------------------------------------------

### About This Report

This report contains data for referrals made to post diagnostic support services with a diagnosis date between **`r format(start_date, "%d %B %Y")`** and **`r format(end_date, "%d %B %Y")`** and is based on board submissions made in **`r month(month(floor_date(end_date, "months")) + 1, label = TRUE, abbr = FALSE)` `r year(floor_date(end_date, "months") + 1)`**.

These reports are developed by the NSS Public Health and Intelligence National Dementia PDS Team and contain performance-based analysis against the Scottish Government's LDP Standard on Dementia Post-Diagnostic Support whereby anyone newly diagnosed with dementia is entitled to a years worth of person-centred support.

We would welcome any comments or feedback you may have on these management reports. Please get in touch with the ISD Dementia PDS team at: [NSS.ISDDementiaPDS@nhs.net](mailto:NSS.ISDDementiaPDS@nhs.net)


Row
-------------------------------------------------

### LDP Standard

The Local Delivery Plan (LDP) standard is as follows:

People newly diagnosed with dementia will be offered a minimum of one year’s post-diagnostic support, coordinated by a named Link Worker.

Performance against the LDP standard is reported in two parts:

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

1. The percentage of people estimated to be newly diagnosed with dementia who were referred for post-diagnostic support.
2. The percentage of people referred who received a minimum of one year’s support.

</div>


<!-- Scotland -->

```{r scotland, include=FALSE}

scotland <- map(.x = sort(unique(pds$fy)),
                .f = ~ set_env(data = pds,
                               exp  = exp,
                               hb   = "Scotland",
                               year = .x))

```

`r paste(knitr::knit_child(text = scotland), collapse = '')`


<!-- HEALTH BOARDS -->

```{r health-boards, include=FALSE}

health_boards <- pmap(expand.grid(sort(unique(pds$fy)),
                                  sort(unique(pds$health_board))), 
                      .f = ~ set_env(data = pds,
                                    exp  = exp,
                                    hb   = .y,
                                    year = .x))
```

`r paste(knitr::knit_child(text = health_boards), collapse = '')`


Methodology
=================================================

Row
-------------------------------------------------

### Methodology

Notes will be added here to describe the methodology.

Include information on what is done with outstanding errors; e.g. missing PDS status recoded to active.

Include note about what year of expected diagnoses is used for each financial year.

The code used to produce these reports is available on [GitHub](https://github.com/alicebyers5/dementia-pds).
