---
title: "Dementia PDS Quarterly Management Report: 2016/17 - 2019/20 Q1"
output: 
  flexdashboard::flex_dashboard:
    logo: isdscotland.png
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}

# Load environment file
source(here::here("code", "00_setup-environment.R"))

# Load functions
purrr::walk(dir(here::here("functions"), full.names = TRUE), source)

# Load PDS data
pds <- read_rds(here("data", glue("{fy}-{qt}_final-data.rds"))) %>%
  
  # Filter HB for fasther knitting when testing
  filter(substr(health_board, 1, 1) == c("A", "B")) %>%
  
  # Remove codes from board and IJB
  mutate(health_board = str_sub(health_board, 3, -1),
         ijb          = str_sub(ijb, 11, -1))

# Load expected diagnoses reference file
exp <- read_csv(here("reference-files", "expected-diagnoses.csv"))

```

Home
=================================================

Row
-------------------------------------------------

### About This Report

This report contains data for referrals made to post diagnostic support services with a diagnosis date between **`r format(start_date, "%d %B %Y")`** and **`r format(end_date, "%d %B %Y")`**.

All data in this report are based on the most recently submitted data and are refreshed quarterly for each new report. This page includes data as submitted in **`r sub_month(fy, qt)`**. 

These reports are developed by the NSS Public Health and Intelligence National Dementia PDS Team and contain performance-based analysis against the Scottish Government's LDP Standard on Dementia Post-Diagnostic Support whereby anyone newly diagnosed with dementia is entitled to a years worth of person-centred support.

We would welcome any comments or feedback you may have on these management reports. Please get in touch with the ISD Dementia PDS team at: [NSS.ISDDementiaPDS@nhs.net](mailto:NSS.ISDDementiaPDS@nhs.net)


Row
-------------------------------------------------

### LDP Standard

The Local Delivery Plan (LDP) standard is as follows:

People newly diagnosed with dementia will be offered a minimum of one year’s post-diagnostic support, coordinated by a named Link Worker.

Performance against the LDP standard is reported in two parts:

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

1. The percentage of people estimated to be newly diagnosed with dementia who were referred for post-diagnostic support.
2. The percentage of people referred who received a minimum of one year’s support.

</div>


<!-- Scotland -->

```{r scotland, include=FALSE}

scotland <- map(.x = sort(unique(pds$fy)),
                .f = ~ set_env(data = pds,
                               exp  = exp,
                               hb   = "Scotland",
                               year = .x,
                               quarter = qt))

```

`r paste(knitr::knit_child(text = scotland), collapse = '')`


<!-- HEALTH BOARDS -->

```{r health-boards, include=FALSE}

health_boards <- pmap(expand.grid(sort(unique(pds$fy)),
                                  sort(unique(pds$health_board))), 
                      .f = ~ set_env(data = pds,
                                     exp  = exp,
                                     hb   = .y,
                                     year = .x,
                                     quarter = qt))
```

`r paste(knitr::knit_child(text = health_boards), collapse = '')`


Methodology
=================================================

Row
-------------------------------------------------

### <!-- No Title -->

This page includes more detail regarding the methodology used to arrive at the figures in this report. It is hoped that by sharing this, the reports will be easier to understand and local reporting will be more consistent.

This report was produced using R and R Markdown. The code is available publically on [GitHub](https://github.com/alicebyers5/dementia-pds).


Row {.tabset}
-------------------------------------------------

### **Number of Expected Diagnoses**

In December 2016, the Scottish Government published a report: [Estimated and Projected Disgnosis Rates for Dementia in Scotland: 2014-2020](https://www.gov.scot/publications/estimated-projected-diagnosis-rates-dementia-scotland-2014-2020/). Estimations are available per calendar year and health board therefore analysis of this part of the LDP standard is unavailable by IJB or any other breakdowns. 

More infomation of the methodology used to calculate these figures and the limitations of this are available in the report.

Please note that as estimations are available by calendar year and figures in this report are by financial year, the estimation for the calendar year with the majority of months in the selected financial year is used. For example, analysis for financial year 2019/20 uses estimations for the calendar year 2019.

It is expected that this report will be refreshed and methodology reviewed in the near future. More information of this will be included in this section as and when it is available.


### **Local Delivery Plan (LDP) Standard Classification**

XXX


### **Data Quality**

What changes are made to the outstanding errors on the file? e.g. missing PDS Status recoded to active.


<!-- END OF SCRIPT -->