---
output: 
  phstemplates::phs_report_docx:    
    reference_docx: "/conf/dementia/A&I/Outputs/publication/templates/phs-offstats-report.docx"
    fig_caption: no
    cover_page: "/conf/dementia/A&I/Outputs/publication/templates/phs-offstats-cover.docx"
    cover_title: "Dementia Post-Diagnostic Support"
    cover_subtitle: "Local Delivery Plan Standard - Figures to 2021/22"
    cover_date: "26/03/2024"
    toc_depth: 3
---
```{r TableData, include = FALSE}

source(here::here("code", "publication", "00_setup-pub-environment.R"))
source(here("functions", "flextable_style.R"))

pub_date_url <- 
  paste0("https://publichealthscotland.scot/publications/",
         "dementia-post-diagnostic-support/dementia-post-diagnostic-support-local-delivery-plan-standard-figures-to-",
         (latest_fy))

# Function to format percentages
format_perc <- function(x, dp = 1){
  x %>%
    round_half_up(dp) %>%
    format(nsmall = dp) %>%
    paste0("%") %>%
    trimws()
}

# Read in data ----

# LDP Dataset
pds <- 
  read_rds(data_path(directory = "publication", 
                    type = "pub_data",
                    ext = "rds")) %>% 
  filter(ijb != "Unknown" & referrals > 0)

# Expected Diagnoses (Incidence)
exp <- read_csv(exp_diagnoses_path()) %>%
  select(fy, health_board = health_board_label, diagnoses)

# Error rates 
err <- 
  read_rds(data_path(directory = "mi", 
                    type = "error_data",
                    ext = "rds")) %>% 
  filter(health_board == "Scotland" & fy %in% fy_in_pub) %>%
  mutate(perc = format_perc(total_errors / records * 100)
  ) %>%
  select(fy, perc) %>%
  mutate(text = glue("for {fy} was {perc}"))

a_city_statement <-
  paste("Aberdeen City Health & Social Care Partnership ceased its contract ", 
        "with Alzheimer Scotland during 2019 and introduced an in-house ", 
        "Dementia Post-Diagnostic Support (PDS) service. This transition ", 
        "resulted in some PDS cases being terminated by Alzheimer Scotland ", 
        "earlier than 12 months and therefore not meeting the LDP standard.", 
        "As part of the transition, individuals were contacted to ask if they ", 
        "still wanted to receive PDS which was then provided by the in-house ", 
        "service, if required. This should be taken into account when ", 
        "interpreting figures for Aberdeen City in 2018/19. Although figures ", 
        "for 2019/20 and 2020/21 include the total number of people referred ", 
        "to PDS across all Integration Authority areas in NHS Grampian, data ", 
        "for Aberdeen City is not included in the measurement figures for the ",
        "LDP standard. This is due to data quality issues and missing dates ", 
        "meaning it is not possible to accurately measure these referrals ", 
        "against the LDP standard.")
        
  
```

```{r summary-data, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}
summary <-
  pds %>%
  filter(fy %in% c(latest_fy, revised_fy)) %>%
  group_by(fy) %>%
  summarise(across(referrals:denominator, sum), .groups = "drop") %>%
  left_join(
    exp %>% filter(health_board == "Scotland") %>% select(-health_board),
    by = "fy"
  ) %>%
  mutate(
    inc_perc = referrals / diagnoses * 100,
    year_perc = numerator / denominator * 100
  ) %>%
  mutate(across(contains("perc"),
                ~ paste0(format(round_half_up(., 1), nsmall = 1), "%")))
```

```{r incidence-data, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}

# Incidence data for latest year
inc <-
  pds %>%
  filter(fy == max(fy_in_pub)) %>%
  group_by(health_board) %>%
  summarise(across(c(referrals), sum),
            .groups = "drop") %>%
  adorn_totals(name = "Scotland") %>%
  left_join(exp %>% filter(fy == max(fy_in_pub)), 
            by = "health_board") %>%
  mutate(perc = format_perc(referrals / diagnoses * 100)) %>%
  select(health_board, diagnoses, referrals, perc)

# Top 3 HBs
inc_top3 <- 
  inc %>% 
  arrange(desc(perc)) %>%
  filter(row_number() %in% 1:3)

# Bottom 2 HBs
inc_bot2 <- 
  inc %>% 
  arrange(perc) %>%
  filter(row_number() %in% 1:2)

# Commentary for latest year incidence data
inc_text <- glue(
  "In Scotland, {inc %>% filter(health_board == 'Scotland') %>% ",
  "pull(perc)} of those people estimated to be newly diagnosed ",
  "with dementia in {latest_fy} were referred for post-diagnostic ",
  "support. The effects of measures relating to the COVID-19 pandemic ",
  "are likely to have affected the figures for {latest_fy}. ",
  "{inc_top3$health_board[1]} had the highest percentage ",
  "of referrals compared to the estimated number of people newly ",
  "diagnosed with dementia ({inc_top3$perc[1]}), ",
  "followed by {inc_top3$health_board[2]} ",
  "({inc_top3$perc[2]}) and {inc_top3$health_board[3]} ",
  "({inc_top3$perc[3]}). ",
  "{glue_collapse(inc_bot2$health_board, sep = ' and ')} ",
  "had the lowest percentages, with ",
  "{glue_collapse(inc_bot2$perc, sep = ' and ')} ",
  "respectively."
)

# Incidence data for all years
inc_trend <-
  pds %>%
  group_by(health_board, fy) %>%
  summarise(across(c(referrals), sum),
            .groups = "drop") %>%
  group_by(fy) %>%
  group_modify(~ adorn_totals(., name = "Scotland")) %>%
  left_join(exp, by = c("health_board", "fy")) %>%
  ungroup() %>%
  mutate(perc = referrals / diagnoses * 100) %>%
  select(-c(referrals:diagnoses))

# Data for incidence trend table
inc_trend_table <-
  inc_trend %>%
  mutate(perc = format_perc(perc)) %>%
  pivot_wider(names_from = fy, values_from = perc)

# Data for incidence trend commentary
inc_trend_comm <-
  inc_trend %>%
  filter(health_board == "Scotland") %>%
  mutate(perc = format_perc(perc)) %>%
  arrange(perc)

# Commentary for incidence trend
inc_trend_text <- glue(
  "The percentage of the estimated number of people in Scotland newly ",
  "diagnosed with dementia referred for post-diagnostic support has ",
  "fluctuated slightly over the {english(length(fy_in_pub) - 1)} year period ",
  "{first(fy_in_pub)} to {last(fy_in_pub) [-1]}, ranging from ",
  "{first(inc_trend_comm$perc)} in {first(inc_trend_comm$fy)} to ",
  "{last(inc_trend_comm$perc)} in {last(inc_trend_comm$fy) [-1]}. ", 
  "The reduction to {first(inc_trend_comm$perc)} in {first(inc_trend_comm$fy)} ", 
  "is likely to have been due to the effects of measures relating to the COVID-19 ",
  "pandemic.")
```

```{r 12-months-data, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}

# Latest year 12m PDS data by HB
hb <-
  pds %>%
  filter(fy == max(fy_in_pub)) %>%
  group_by(health_board) %>%
  summarise(across(complete:denominator, sum),
            .groups = "drop") %>%
  adorn_totals(name = "Scotland") %>%
  mutate(
    calc = (numerator / denominator * 100),
    perc = format_perc(numerator / denominator * 100)
  ) %>%
  select(health_board, referrals, complete, exempt, 
         ongoing, fail, calc, perc)

# Top 3 HBs
top3_hb <- 
  hb %>%
  arrange(desc(calc)) %>%
  filter(row_number() %in% 1:3)
 
# Bottom 2 HBs
bot2_hb <-
  hb %>%
  arrange(calc) %>%
  filter(row_number() %in% 1:2)

hb <- hb %>%  
    select(health_board, referrals, complete, exempt, 
         ongoing, fail, perc)

# Commentary for latest year HB 12m PDS
text_hb <- glue(
  "In Scotland, {hb %>% filter(health_board == 'Scotland') %>% ",
  "pull(perc)} of those people referred for dementia post-diagnostic ",
  "support received a minimum of one year's support. ",
  "{top3_hb$health_board[1]} had the highest percentage of people receiving ",
  "a minimum of one year's post-diagnostic support ",
  "({top3_hb$perc[1]}) followed by {top3_hb$health_board[2]} ",
  "({top3_hb$perc[2]}) and {top3_hb$health_board[3]} ({top3_hb$perc[3]}). ",
  "{glue_collapse(bot2_hb$health_board, sep = ' and ')} had the lowest ",
  "percentages with {glue_collapse(bot2_hb$perc, sep = ' and ')} respectively."
)

# Latest year 12m PDS by IJB
ijb <-
  pds %>%
  filter(fy == max(fy_in_pub)) %>%
  group_by(ijb) %>%
  summarise(across(complete:denominator, sum),
            .groups = "drop") %>%
  adorn_totals(name = "Scotland") %>%
  mutate(
    perc = format_perc(numerator / denominator * 100)) %>%
  select(ijb, referrals, complete, exempt, 
         ongoing, fail, perc)

# Top 2 IJB
top2_ijb <- 
  ijb %>%
  arrange(desc(perc)) %>%
  filter(row_number() %in% 1:3)

# Bottom 2 IJB
bot2_ijb <-
  ijb %>%
  arrange(perc) %>%
  filter(row_number() %in% 1:2)

# Commentary for latest year IJB 12m PDS
text_ijb <- glue(
  "In {latest_fy}, {top2_ijb$ijb[1]} Integration Joint Board had the highest ",
  "percentage of people receiving a minimum of one year's post-diagnostic ",
  "support ({top2_ijb$perc[1]}), followed by {top2_ijb$ijb[2]} ",
  "({top2_ijb$perc[2]}). {glue_collapse(bot2_ijb$ijb, sep = ' and ')} ",
  "had the lowest percentages with {glue_collapse(bot2_ijb$perc, ",
  "sep = ' and ')} respectively."
)

# Headers for 12m PDS tables
headers <-
  c("Number of People Referred to PDS",
    "Standard Met",
    "Exempt from Standard",
    "PDS Ongoing",
    "Standard Not Met",
    "Percentage of LDP Standard Achieved")

hb_headers <- c("NHS Board", headers)
ijb_headers <- c("Integration Joint Board", headers)

# Trend for 12m PDS by HB
hb_trend <-
  pds %>%
  group_by(health_board, fy) %>%
  summarise(across(numerator:denominator, sum),
            .groups = "drop") %>%
  group_by(fy) %>%
  group_modify(~ adorn_totals(., name = "Scotland")) %>%
  ungroup() %>%
  mutate(perc = numerator / denominator * 100)

# Data for HB trend table
hb_trend_table <-
  hb_trend %>%
  mutate(perc = format_perc(perc)) %>%
  select(-c(numerator:denominator)) %>%
  pivot_wider(names_from = fy, values_from = perc)
  
# Data for Scot trend commentary
trend_comm <-
  hb_trend %>%
  filter(health_board == "Scotland") %>%
  mutate(perc = format_perc(perc)) %>%
  arrange(perc)

# Commentary for Scotland trend
scot_trend_text <- glue(
  "The percentage of people in Scotland referred for post-diagnostic support ",
  "who received a minimum of one year's support has ",
  "fluctuated in the {english(length(fy_in_pub))} year period ",
  "{first(fy_in_pub)} to {last(fy_in_pub)}, ranging from ",
  "{first(trend_comm$perc)} in {first(trend_comm$fy)} to ",
  "{last(trend_comm$perc)} in {last(trend_comm$fy)}.", 
  "The effects of measures relating to the COVID-19 pandemic ", 
  "are likely to have affected the 2019/20 and 2020/21 figures."
)

# Data for HB trend commentary
hb_trend_comm <-
  hb_trend %>%
  filter(health_board != "Scotland") %>%
  group_by(health_board) %>%
  arrange(fy) %>%
  summarise(fy = fy,
            fy1 = lag(fy),
            fy2 = lag(fy, 2),
            diff1 = perc - lag(perc),
            diff2 = perc - lag(perc, n = 2),
            .groups = "drop") %>%
  filter(fy == latest_fy) %>%
  group_by(fy1, fy2) %>%
  summarise(across(
    contains("diff"),
    ~ case_when(
      sum(. > 0) / n() == 0.5 ~ "half",
      sum(. > 0) / n() > 0.5 ~ "more than half",
      sum(. > 0) / n() < 0.5 ~ "less than half"
    )
  ),
  .groups = "drop")
  

# Commentary for HB trend
hb_trend_text <- glue(
  "When comparing percentages for {hb_trend_comm$fy1} and {latest_fy}, ",
  "{hb_trend_comm$diff1} of the NHS Boards had a higher rate in {latest_fy} ",
  "than in {hb_trend_comm$fy1}."
)

if(hb_trend_comm$diff1 == hb_trend_comm$diff2){
  hb_trend_text <- glue(
    "{hb_trend_text} This proportion remains the same when {hb_trend_comm$fy2}",
    " and {latest_fy} are compared."
  )
}

# Data for IJB trend table
ijb_trend_table <-
  pds %>%
  group_by(ijb, fy) %>%
  summarise(across(numerator:denominator, sum),
            .groups = "drop") %>%
  group_by(fy) %>%
  group_modify(~ adorn_totals(., name = "Scotland")) %>%
  ungroup() %>%
  mutate(perc = format_perc(numerator / denominator * 100)) %>%
  select(-c(numerator:denominator)) %>%
  pivot_wider(names_from = fy, values_from = perc)

```

```{r demographics-data, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}
age <-
  pds %>%
  filter(fy == latest_fy & age_grp != "Unknown") %>%
  group_by(age_grp) %>%
  summarise(across(referrals:denominator, sum), .groups = "drop") %>%
  mutate(
    ref_dist = referrals / sum(referrals) * 100,
    ldp = numerator / denominator * 100
  ) %>%
  mutate(
    age_text = case_when(
      str_detect(age_grp, "to") ~ paste("between", age_grp, "years"),
      age_grp == "90+" ~ "90 years and over",
      age_grp == "59 and Under" ~ "59 years and under"
    )
  )

age_ref <- age %>% 
  filter(ref_dist %in% c(max(ref_dist), min(ref_dist))) %>%
  arrange(ref_dist) %>%
  mutate(ref_dist = format_perc(ref_dist))
  
age_referrals_text <- glue(
  "People aged {last(age_ref$age_text)} accounted for the largest percentage ",
  "of referrals for dementia post-diagnostic support in {latest_fy} ",
  "({last(age_ref$ref_dist)}). In contrast, the lowest percentage of referrals ",
  "was for people aged {first(age_ref$age_text)} ({first(age_ref$ref_dist)})."
)

age_ldp <-
  age %>%
  filter(ldp %in% c(max(ldp), min(ldp))) %>%
  arrange(ldp) %>%
  mutate(ldp = format_perc(ldp))

ldp_top_ref <-
  age %>%
  filter(ref_dist == max(ref_dist)) %>%
  mutate(ldp = format_perc(ldp))

age_ldp_text <- glue(
  "In {latest_fy}, the percentage of referrals receiving a minimum of one ",
  "year's post-diagnostic support ranged from {first(age_ldp$ldp)} for those ",
  "aged {first(age_ldp$age_text)}, to {last(age_ldp$ldp)} for those aged ",
  "{last(age_ldp$age_text)}. The percentage for those {ldp_top_ref$age_text} ",
  "(age group with the highest number of referrals) was {ldp_top_ref$ldp}."
)

simd <-
  pds %>%
  filter(fy == latest_fy & simd != "Unknown") %>%
  group_by(simd) %>%
  summarise(across(referrals:denominator, sum), .groups = "drop") %>%
  mutate(
    ref_dist = referrals / sum(referrals) * 100,
    ldp = numerator / denominator * 100
  ) %>%
  mutate(
    across(c(ref_dist, ldp), format_perc),
    simd = str_sub(simd, 1, 1)
  )

simd_ref_top <- simd %>% filter(ref_dist == max(ref_dist))
simd_ref_bot <- simd %>% filter(ref_dist == min(ref_dist))

simd_referrals_text <- glue(
  "Deprivation quintile {simd_ref_top$simd} had the highest percentage of ",
  "referrals for dementia post-diagnostic support in {latest_fy} ",
  "({simd_ref_top$ref_dist}). Deprivation quintile {simd_ref_bot$simd} had ",
  "the lowest percentage of referrals ({simd_ref_bot$ref_dist})."
)

simd_ldp_top <- simd %>% filter(ldp == max(ldp))
simd_ldp_bot <- simd %>% filter(ldp == min(ldp))

simd_ldp_text <- glue(
  "Deprivation quintile {simd_ldp_top$simd} had the highest percentage of ",
  "referrals who received a minimum of one year's support in {latest_fy} ",
  "({simd_ldp_top$ldp}). Deprivation quintile {simd_ldp_bot$simd} had the ",
  "lowest percentage of referrals who received a minimum of one year's ",
  "support ({simd_ldp_bot$ldp})."
)
```

```{r alt-text, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Figure 1 - incidence by HB
f1_alt_text <- glue(
  "Bar chart showing percentage of estimated number of people newly diagnosed ",
  "with dementia referred for post-diagnostic support by NHS Board in ",
  "financial year {latest_fy}."
)

f2_alt_text <- glue(
  "Bar chart showing percentage of referrals who received a minimum of ",
  "one year's post-diagnostic support by NHS Board in ",
  "financial year {latest_fy}."
)

f3_alt_text <- glue(
  "Bar chart showing percentage of referrals who received a minimum of ",
  "one year's post-diagnostic support by Integration Joint Board in ",
  "financial year {latest_fy}."
)

f4_alt_text <- glue(
  "Bar chart showing distribution of referrals to dementia ",
  "post-diagnostic support by age group in financial year {latest_fy}."
)

f5_alt_text <- glue(
  "Bar chart showing percentage of referrals who received a minimum of ",
  "one year's post-diagnostic support by age group in ",
  "financial year {latest_fy}."
)

f6_alt_text <- glue(
  "Bar chart showing distribution of referrals to dementia ",
  "post-diagnostic support by deprivation quintile in ",
  "financial year {latest_fy}."
)

f7_alt_text <- glue(
  "Bar chart showing percentage of referrals who received a minimum of ",
  "one year's post-diagnostic support by deprivation quintile in ",
  "financial year {latest_fy}."
)
```

```{r footnotes, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}
source_footnote <- 
  paste0("Source: Public Health Scotland quarterly dementia post-diagnostic ",
        "support dataset. Data submissions from NHS Boards as at ", 
        format(end_date, "%d %B %Y"), ".")

prov_footnote <- 
  paste("Figures for", latest_fy, "are provisional subject to all",
        "service users completing their support.")

revised_footnote <-
  paste("Figures for", revised_fy, "have been revised (^R^) and are",
        "now final.")

a_city_footnote_hb <-
  paste("The 2020/21 figures do not include Aberdeen City. Their figures are ",
        "affected by a change in service provision of PDS during 2019 that ",
        "has resulted in data quality issues. This will impact on the figures ",
        "for NHS Grampian and Scotland.",
        "See [Appendix 1](#reporting) for further information.")
        
a_city_footnote_ijb <-
  paste("The total number of people referred to PDS in Aberdeen City for 2020/21 is ",
        "included in the table, however there are no LDP standard figures shown. ", 
        " This is due to a change during 2019 to the PDS service provided ", 
        "by Aberdeen City which has resulted in data quality issues. ",
        "See [Appendix 1](#reporting) for further information.")
    

a_city_footnote_general <-
  paste("Aberdeen City are excluded from this chart due to data quality issues.",
        "See [Appendix 1](#reporting) for further information.")

incidence_footnote <-
  paste0("The estimated number of people newly diagnosed with dementia is ",
        "subject to the limitations detailed within the [Estimated and ",
        "Projected Diagnosis Rates for Dementia in Scotland: 2014-2020]",
        "(https://www.gov.scot/publications/estimated-projected-diagnosis-rates-dementia-scotland-2014-2020/) publication. ",
        "Estimates for calendar year ", str_sub(latest_fy, 1, 4),
        " have been used.")

incidence_footnote_trend <-
  paste0("The estimated number of people newly diagnosed with dementia is ",
        "subject to the limitations detailed within the [Estimated and ",
        "Projected Diagnosis Rates for Dementia in Scotland: 2014-2020]",
        "(https://www.gov.scot/publications/estimated-projected-diagnosis-rates-dementia-scotland-2014-2020/) publication. ",
        "Estimates are used as follows: calendar year 2016 estimates for 2016/17, ",
        "calendar year 2017 estimates for 2017/18, calendar year 2018 estimates ", 
        "for 2018/19, calendar year 2019 estimates for 2019/20 and calendar year ",
        "2020 estimates for 2020/21.")

method_footnote <-
  paste("For detailed information on how the percentage of LDP standard",
        "achieved is calculated, ",
        "please see the [Background section](#background) of this report.")

interpret_footnote <-
  paste("When interpreting this information consideration should also be",
        "taken of the percentage of people estimated to be newly diagnosed",
        "with dementia being referred to post-diagnostic support",
        "(see [section 1](#section1)).")

age_unknown <- 
  pds %>% filter(fy == latest_fy) %>% count(age_grp)

age_footnote <- glue(
  "Age is calculated as at the dementia diagnosis date. {if_else('Unknown' ",
  "%in% age_unknown$age_grp, 'There are a small number of records with an ",
  "incomplete date of birth and therefore the age is unknown.', '')}"
)

simd_unknown <-
  pds %>% filter(fy == latest_fy) %>% count(simd)

simd_footnote <- glue(
  "Deprivation is calculated by matching postcodes to the ",
  "Scottish Index of Multiple Deprivation (SIMD) quintiles. There are a ", 
  "small number of records (16) where it was not possible to assign ", 
  "deprivation category based on the postcode information available.")

interpretation_text <- glue("**---Manual adjustment required here---**")
```

# Introduction
This release by Public Health Scotland (PHS) reports on the Scottish Government’s Local Delivery Plan (LDP) standard that everyone newly diagnosed with dementia will be offered a minimum of one year’s post-diagnostic support, coordinated by an appropriately trained Link Worker, including the building of a person-centred support plan.
Data are presented by financial year of diagnosis and this report presents finalised figures for `r revised_fy` and provisional figures for `r latest_fy` which are subject to some service users completing their support.

The Scottish Government published their [third national dementia strategy](https://www.gov.scot/publications/scotlands-national-dementia-strategy-2017-2020/) in 2017. This included the commitment to extend and embed dementia post-diagnostic support. In order to effectively monitor the delivery of post-diagnostic support a national [local delivery plan (LDP) standard](https://www.gov.scot/publications/nhsscotland-performance-against-ldp-standards/pages/introduction/) was introduced for all people newly diagnosed with dementia to receive a minimum of one year’s post-diagnostic support. 

The LDP standard is reported in two parts, each addressing a separate element to the standard:

1.	The percentage of people estimated to be newly diagnosed with dementia who were referred for post-diagnostic support.
2.	The percentage of people referred for dementia post-diagnostic support who received a minimum of one year’s support coordinated by a link worker, including the 
building of a person-centred support plan.

NHS Boards provide quarterly data submissions to PHS on individuals diagnosed with dementia and referred for post-diagnostic support within their local areas and this dataset forms the basis of the LDP standard calculation. 

\newpage

## Impact of COVID-19 on provision of dementia post-diagnostic support

In December 2020, the Scottish Government published a national action plan: [Dementia And COVID-19 - National Action Plan To Continue To Support Recovery For People With Dementia And Their Carers](https://www.gov.scot/publications/dementia-covid-19-national-action-plan-continue-support-recovery-people-dementia-carers/). This plan is a partnership document with COSLA and a range of stakeholders and explains how the Scottish Government is working, and plans to work, with others to strengthen community resilience, support people with dementia and their families to continue to get the right care, treatment and support at the right time as we live with, and come through and recover from, the COVID-19 pandemic.

Commitment 4 of the national action plan states:

“We will continue to support our national commitment on post-diagnostic support, to increase access to this service and to the community support individuals need to continue living well as part of the wider community. As part of this, in partnership with COSLA, local partnerships, Alzheimer Scotland and other stakeholders we will take forward work in the first four months of 2021 to review and assess the provision and design of post-diagnostic services and identify both best practice and barriers to further expansion of the service. We will also establish a process to engage regularly with local delivery partners to assess progress and identify and help address local issues.”

In December 2020, Alzheimer Scotland published a [report](https://www.alzscot.org/news/covid-19-the-hidden-impact) looking into the impact of coronavirus on people with dementia, their families and carers who are living at home.

The COVID-19 pandemic and the infection control measures put in place are likely to 
have had an impact on the number of people being diagnosed and referred, 
particularly in 2020/21.

Some areas have reported difficulties in the COVID-19 pandemic affecting their 
ability and capacity to update their data systems which are required to provide the dementia PDS dataset, however it is not anticipated that this has a large impact on 
the data presented in this report.

\newpage

# Main Points
<Div custom-style = "Bullet 1">There were `r summary %>% filter(fy == latest_fy) %>% pull(referrals)` people diagnosed and referred for dementia post-diagnostic support in `r latest_fy`, compared to `r summary %>% filter(fy == revised_fy) %>% pull(referrals)` in `r revised_fy`. The effects of measures relating to the COVID-19 pandemic are likely to have contributed to this reduction.</Div>
<Div custom-style = "Bullet 1">Of those referred in `r latest_fy` for post-diagnostic support, `r summary %>% filter(fy == latest_fy) %>% pull(year_perc)` received a minimum of one year's support. In `r revised_fy`, the percentage was `r summary %>% filter(fy == revised_fy) %>% pull(year_perc)`.</Div>
<Div custom-style = "Table or chart caption">Percentage of referrals who received a minimum of one year’s post-diagnostic support by NHS Board; `r latest_fy`^1,2^</Div>


<Div custom-style = "Figure_Style">
```{r fig-summary, echo= FALSE, fig.cap= `f2_alt_text`, out.width = 600}
# Figure summary
include_graphics(pub_figures_path(type = "c2"))

```
</Div>

<Div custom-style = "Footnote Text">
1. `r prov_footnote`
2. `r a_city_footnote_hb`
</Div>

<Div custom-style = "Bullet 1">In Scotland, `r summary %>% filter(fy == latest_fy) %>% pull(inc_perc)` of those people estimated to be newly diagnosed with dementia in `r latest_fy` were referred for post-diagnostic support, compared to `r summary %>% filter(fy == revised_fy) %>% pull(inc_perc)` in `r revised_fy`. The effects of measures relating to the COVID-19 pandemic are likely to have contributed to this reduction.</Div>

\newpage

# Results and Commentary

## 1. Number and percentage of people estimated to be newly diagnosed with dementia who were referred for post-diagnostic support{#section1}

This part of the LDP standard requires the number of referrals for post-diagnostic support to be compared against an estimated number of people newly diagnosed with dementia each year. Health Board level estimates of the number of people newly diagnosed with dementia (incidence) used for this calculation are from the paper [Estimated and Projected Diagnosis Rates for Dementia in Scotland 2014-2020](https://www.gov.scot/publications/estimated-projected-diagnosis-rates-dementia-scotland-2014-2020/) published by the Scottish Government in 2016. 

Table 1 presents the number and percentage of people referred for dementia post-diagnostic support compared to the estimated number of people newly diagnosed with dementia in `r latest_fy` by NHS Board. 

<Div custom-style = "Table or chart caption">Table 1: Estimated number of people newly diagnosed with dementia referred for post-diagnostic support (PDS) by NHS Board; `r latest_fy`^1,2,3^</Div>

<br>

```{r table-1, echo = FALSE, ft.align = "center"}
inc %>%
  mutate(across(where(is.numeric), ~ na_if(., 0))) %>%
  flextable() %>%
  ft_dementia_style() %>%
    set_header_labels(
    values = c(
      health_board = "NHS Board",
      diagnoses = "Estimated Number of People Newly Diagnosed with Dementia",
      referrals = "Number of People Referred to PDS",
      perc = paste("Percentage of Estimated Number of People",
                   "Diagnosed with Dementia Referred to PDS")
    )) %>% 
    align(j = 2, align = "right", part = "body") %>%
    height(height = 0.236, part = "body") %>%
    hrule(rule = "atleast", part = "body") %>%
    width(width = 2.1) %>% 
    append_chunks(
    part = "body", i = 3, j = 1,
     as_chunk(" text + hyperlink", 
              props = fp_text(color = "#005c99", bold = TRUE, font.size = 12))
  )
  

```

<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r incidence_footnote`
</Div>

`r inc_text`

Figure 1 presents the percentage of people referred for dementia post-diagnostic support compared to the estimated number of people newly diagnosed with dementia by NHS Board in `r latest_fy`.

<Div custom-style = "Table or chart caption">Figure 1: Percentage of the estimated number of people newly diagnosed with dementia referred for post-diagnostic support (PDS) by NHS Board; `r latest_fy`^1,2,3^</Div> 
<Div custom-style = "Figure_Style">
```{r fig-1, echo= FALSE, fig.cap= `f1_alt_text`, out.width = 420}
# Figure 1
include_graphics(pub_figures_path(type = "c1"))

```

<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r incidence_footnote`
</Div>

Table 2 presents the trend in the percentage of estimated number of people newly diagnosed with dementia referred for post-diagnostic support (PDS) for financial years `r fy_in_pub[1]` to `r latest_fy` by NHS Board.

<Div custom-style = "Table or chart caption">Table 2: Trend - Percentage of the estimated number of people newly diagnosed with dementia referred for post-diagnostic support (PDS) by NHS Board ^1,2,3,4^ </Div>

```{r table-2, echo = FALSE, ft.align = "center"}
# Table 2
inc_trend_table %>%
  flextable() %>%
  ft_dementia_style() %>%
    set_header_labels(
    values = c(health_board = "NHS Board")) %>% 
  set_table_properties(layout = "autofit") %>% 
  compose(
    j = ncol(inc_trend_table), part = "header",
    value = as_paragraph(latest_fy, as_sup("P"))
  ) %>%
  compose(
    j = ncol(inc_trend_table) - 1, part = "header",
    value = as_paragraph(nth(fy_in_pub, -2), as_sup("R"))
  )
```

<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r revised_footnote`
4. `r incidence_footnote_trend`
</Div>


`r inc_trend_text`

\newpage

## Number and percentage of people referred for dementia post-diagnostic support who received a minimum of one year’s support

This part of LDP standard reports on the number of people referred for dementia post-diagnostic support who received a minimum of one year’s support. Figures presented in this section are available by NHS Board and Integration Authority area, and should be interpreted in conjunction with [section 1](#section1).

The criteria used to define this part of the LDP standard is detailed in [Appendix 1](#background).

### NHS Board

Table 3 presents the number and percentage of people referred for post-diagnostic support who received a minimum of one year’s support by NHS board for `r latest_fy`. The percentage by NHS Board is also shown in Figure 2.

<Div custom-style = "Table or chart caption">Table 3: Number and percentage of people referred for dementia post-diagnostic support (PDS) who received a minimum of one year’s support by NHS Board; `r latest_fy`^1,2,3,4,5^</Div>

```{r table-3, echo = FALSE, ft.align = "center"}
# Table 3 
names(hb_headers) <-  names(hb %>%
          select(health_board, referrals, complete, exempt, 
         ongoing, fail, perc))

hb %>%
  mutate(across(where(is.numeric), ~ na_if(., 0))) %>%
  flextable() %>% 
  ft_dementia_style() %>%
  set_header_labels(values = hb_headers) %>% 
  set_table_properties(layout = "autofit")

```


<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r method_footnote`
4. `r interpret_footnote`
5. `r a_city_footnote_hb`
</Div>

`r interpretation_text`

`r text_hb`

<Div custom-style = "Table or chart caption">Figure 2: Percentage of referrals who received a minimum of one year’s post-diagnostic support by NHS Board; `r latest_fy`^1,2,3,4,5^</Div>

<Div custom-style = "Figure_Style">
```{r fig-2, echo=FALSE, fig.cap= `f2_alt_text`, out.width = 600}
# Figure 2 
include_graphics(pub_figures_path(type = "c2"))

```


<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r method_footnote`
4. `r interpret_footnote`
5. `r a_city_footnote_hb`
</Div>

<br>

Table 4 presents the trend in the percentage of people referred for post-diagnostic support who received a minimum of one year’s support for financial years `r fy_in_pub[1]` to `r latest_fy` by NHS Board.

<Div custom-style = "Table or chart caption">Table 4: Trend - Percentage of people referred for dementia post-diagnostic support (PDS) who received a minimum of one year’s support by NHS Board ^1,2,3,4,5,6^ </Div>

```{r table-4, echo = FALSE, ft.align = "center"}
# Table 4 
hb_trend_table  %>%
   flextable() %>% 
  ft_dementia_style() %>% 
  set_header_labels(values = c(health_board = "NHS Board")) %>% 
  set_table_properties(layout = "autofit") %>% 
  compose(
    j = ncol(hb_trend_table), part = "header",
    value = as_paragraph(latest_fy, as_sup("P"))
  ) %>%
  compose(
    j = ncol(hb_trend_table) - 1, part = "header",
    value = as_paragraph(nth(fy_in_pub, -2), as_sup("R"))
  )
```

<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r revised_footnote`
4. `r method_footnote`
5. `r interpret_footnote`
6. `r a_city_footnote_hb`
</Div>

`r interpretation_text`

`r scot_trend_text`

`r hb_trend_text`

### Integration Authority area

Table 5 presents the number and percentage of people referred for post-diagnostic support who received a minimum of one year’s support by Integration Authority area. The percentage by Integration Authority area is also shown in Figure 3.

<Div custom-style = "Table or chart caption">Table 5: Number and percentage of people referred for dementia post-diagnostic support (PDS) who received a minimum of one year’s support by Integration Authority area; `r latest_fy`^1,2,3,4,5^</Div>

```{r table-5, echo = FALSE, ft.align = "center"}
#Table 5 
names(ijb_headers) <- names(ijb)

ijb %>%
  mutate(across(where(is.numeric), ~ na_if(., 0))) %>%
  flextable() %>% 
  ft_dementia_style() %>% 
  set_header_labels(values = ijb_headers) %>% 
set_table_properties(layout = "autofit")

```


<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r method_footnote`
4. `r interpret_footnote`
5. `r a_city_footnote_ijb`
</Div>

`r interpretation_text`

`r text_ijb`

\newpage

<Div custom-style = "Table or chart caption">Figure 3: Percentage of people referred who received a minimum of one year’s post-diagnostic support by Integration Authority area; `r latest_fy`^1,2,3,4,5^</Div>

<Div custom-style = "Figure_Style">
```{r fig-3, echo=FALSE, fig.cap= `f3_alt_text`, out.width = 420}
# Figure 3 
include_graphics(pub_figures_path(type = "c3"))

```

<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r method_footnote`
4. `r interpret_footnote`
5. `r a_city_footnote_ijb`
</Div>


Table 6 presents the trend in the percentage of people referred for post-diagnostic support who received a minimum of one year’s support for financial years `r fy_in_pub[1]` to `r latest_fy` by Integration Authority area.

\newpage

<Div custom-style = "Table or chart caption">Table 6: Trend - Percentage of people referred for dementia post-diagnostic support (PDS) who received a minimum of one year’s support by Integration Authority area ^1,2,3,4,5,6^</Div>

```{r table-6, echo = FALSE, ft.align = "center"}
# Table 6
ijb_trend_table %>%
   flextable() %>% 
  ft_dementia_style() %>% 
  set_header_labels(values = c(ijb = "Integration Authority area")) %>% 
  set_table_properties(layout = "autofit") %>% 
  compose(
    j = ncol(ijb_trend_table), part = "header",
    value = as_paragraph(latest_fy, as_sup("P"))
  ) %>%
  compose(
    j = ncol(ijb_trend_table) - 1, part = "header",
    value = as_paragraph(nth(fy_in_pub, -2), as_sup("R"))
  )
```

<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r revised_footnote`
4. `r method_footnote`
5. `r interpret_footnote`
6. `r a_city_footnote_ijb`
</Div>

\newpage

## 3. Demographics and Inequalities

This part of the report presents information on the demographics of individuals who have been referred for dementia post-diagnostic support in Scotland. Age and deprivation have been identified as two of the main areas of interest. 

### Age

Figure 4 presents the age distribution of those referred for dementia post-diagnostic support in Scotland for `r latest_fy`.

<Div custom-style = "Table or chart caption">Figure 4: Age distribution of referrals for dementia post-diagnostic support; `r latest_fy`^1,2,3^</Div>

<Div custom-style = "Figure_Style">
```{r fig-4, echo=FALSE, fig.cap= `f4_alt_text`, out.width = 600}
# Figure 4 
include_graphics(pub_figures_path(type = "c4"))
```

<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r age_footnote`
</Div>

`r interpretation_text`
`r age_referrals_text`

Figure 5 presents the percentage of those referred for dementia post-diagnostic support who received a minimum of one year’s support by age group for `r latest_fy`. 

<Div custom-style = "Table or chart caption">Figure 5: Percentage of referrals who received a minimum of one year’s post-diagnostic support by age group; `r latest_fy`^1,2,3,4^</Div>

<Div custom-style = "Figure_Style">
```{r fig-5, echo=FALSE, fig.cap= f5_alt_text, out.width = 600}
# Figure 5 
include_graphics(pub_figures_path(type = "c5"))
```

<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r age_footnote`
4. `r a_city_footnote_general`
</Div>

`r interpretation_text`
`r age_ldp_text` 

\newpage

### Deprivation

Figure 6 presents the distribution of referrals for dementia post-diagnostic support by deprivation quintile for `r latest_fy`. Each deprivation quintile indicates the level of deprivation using a scale of 1 (most deprived) to 5 (least deprived). At Scotland level, approximately one fifth of the general population are within each deprivation quintile.

<Div custom-style = "Table or chart caption">Figure 6: Distribution of referrals to dementia post-diagnostic support by deprivation quintile; `r latest_fy`^1,2,3^</Div>

<Div custom-style = "Figure_Style">
```{r fig-6, echo=FALSE, fig.cap= `f6_alt_text`, out.width = 600}
# Figure 6
include_graphics(pub_figures_path(type = "c6"))

```

<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r simd_footnote`
</Div>

`r interpretation_text`
`r simd_referrals_text`

Figure 7 presents the percentage of those referred for dementia post-diagnostic support who received a minimum of one year’s support by deprivation quintile for `r latest_fy`. 

<Div custom-style = "Table or chart caption">Figure 7: Percentage of referrals who received a minimum of one year’s post-diagnostic support by deprivation quintile; `r latest_fy`^1,2,3,4^</Div>

<Div custom-style = "Figure_Style">
```{r fig-7, echo=FALSE, fig.cap= f7_alt_text, out.width = 600}
# Figure 7 
include_graphics(pub_figures_path(type = "c7"))
```

<Div custom-style = "Footnote Text">
1. `r source_footnote`
2. `r prov_footnote`
3. `r simd_footnote`
4. `r a_city_footnote_general`
</Div>

`r interpretation_text`
`r simd_ldp_text`

\newpage

# Glossary  

**Incidence**  
The number of new cases of a particular illness or disease during a defined time period. For the purposes of this publication we are looking at the number of new diagnoses of dementia.

**LDP Standard**  
Formerly known as HEAT Targets, Local Delivery Plan (LDP) standards are priorities agreed between Scottish Government and NHS Boards. Performance on Dementia Post-Diagnostic Support is one of the current LDP Standards. Further information can be found on the [Scottish Government website](https://www.gov.scot/About/Performance/scotPerforms/NHSScotlandperformance/Dementia-LDP).

**Post-Diagnostic Support (PDS)**  
Support commissioned by the Scottish Government that everyone newly diagnosed with dementia is entitled to a minimum of one year’s post-diagnostic support. Further information on post-diagnostic support can be found on the [Alzheimer Scotland](https://www.alzscot.org/pds) website.

**Referral**  
When a person receives a new diagnosis of dementia, a referral is made to a service that provides post-diagnostic support and allocates a named person to work alongside the individual and those close to them.

**Deprivation Quintile**  
The Scottish Index of Multiple Deprivation (SIMD) Quintiles. Deprivation for individuals is estimated from aggregate data derived from the census and other routine sources. These are used to estimate the deprivation of small geographical areas, called data zones. The Scottish Index of Multiple Deprivation (SIMD) has seven domains (income, employment, education, housing, health, crime, and geographical access) at data zone level, which have been combined into an overall index to pick out area concentrations of multiple deprivation. Data in this report are analysed by the ‘Scotland level’ Scottish Index of Multiple Deprivation population weighted quintiles. Each quintile consists of approximately 20% of the population living in Scotland, with deprivation quintile 1 indicating the 20% of the population living in the most deprived areas and deprivation quintile 5 the 20% of the population living in the least deprived areas.

\newpage

# Contact
**Zeg Ashraf, Principal Information Analyst**  
Health & Social Care  
0131 314 1737  
[phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

**Jennifer Thom, Information Analyst**  
Health & Social Care  
0131 275 1754  
[phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

For all media enquiries please email [phs.comms@phs.scot](mailto:phs.comms@phs.scot) or call 0131 275 6105.

# Further Information
Further information and data for this publication are available from the [publication page](https://publichealthscotland.scot/publications/dementia-post-diagnostic-support/dementia-post-diagnostic-support-local-delivery-plan-standard-figures-to-202021/) on our website.

The next release of this publication will be in `r format(pub_date + years(1), "%B %Y")`.


# Rate this publication
Let us know what you think about this publication via. the link at the bottom of this [publication page](https://publichealthscotland.scot/publications/dementia-post-diagnostic-support/dementia-post-diagnostic-support-local-delivery-plan-standard-figures-to-202021/) on the PHS website.

\newpage

# Appendices
## Appendix 1 - Background information
To effectively monitor performance of post-diagnostic support delivery, a national [Local Delivery Plan (LDP) standard](https://www.gov.scot/About/Performance/scotPerforms/NHSScotlandperformance/Dementia-LDP) was introduced in April 2013 for all people newly diagnosed with dementia to receive a minimum of one year’s post-diagnostic support.

The LDP standard is defined and calculated as follows:

* **LDP standard met** - The LDP standard is considered met if post-diagnostic support (PDS) started within 12 months of diagnosis and support was ongoing after 12 months, or PDS started within 12 months of diagnosis and ended after at least 11 months.
   
*	**LDP standard not met** - The LDP standard is considered not met if a first substantive contact had not occurred within 12 months of diagnosis or where PDS was stopped prior to 12 months where this was not due to an exempt reason (see below). 
   
* **Exempt from LDP standard** - Exemptions from the LDP standard include where PDS had not yet started, or had started and was completed before 12 months due to the following reasons: service user died, service user moved to a different health board area, service user terminated early or refused and service user no longer actively able to engage in PDS.
   
* **PDS ongoing** - Post-diagnostic support was considered still ongoing if there was less than 12 months since diagnosis and PDS had not yet started, or PDS had started within 12 months and had not yet been delivered for a minimum of 11 months.
   
This part of the LDP standard is calculated as:

<Div custom-style = "Formula">
$$
\text{LDP Standard Achieved (%)} = \frac{\text{LDP Standard met + Exempt from LDP Standard}}{\text{LDP Standard met + Exempt + LDP Standard not met}} \times \text{100}
$$

Service users for whom it is not yet known if they have met the standard as their PDS is ongoing are excluded from the calculation and therefore figures for the latest year are currently provisional subject to all service users completing their support.

### Comparability to LDP standard figures published prior to 2016/17

Information presented in this publication is not comparable to dementia post-diagnostic support LDP standard information published for time periods prior to 2016/17. This is due to a combination of a change in data definitions and reporting, 
and improvements to data quality which are detailed below.

### Data Definitions and Reporting{#reporting}

NHS Boards provide quarterly data submissions to PHS on individuals diagnosed and referred for post-diagnostic support within their local areas and this dataset forms the basis of the LDP standard calculation. 

Revised [data definitions](https://publichealthscotland.scot/media/20921/2023-12-14-dementia-pds-definitions-and-recording-guidance-v14.pdf) and reporting processes were effective from 1 April 2019 for all referrals for post-diagnostic support from 1 April 2016 onwards. The revised definitions were designed in consultation with stakeholders to improve the quality and consistency of the data reported.


### Data Quality

PHS undertake data quality checks and feedback data errors and queries to each Health Board, relating to the Dementia Post-Diagnostic Support dataset, following each data submission.

As at the `r format(end_date, "%d %B %Y")` data submission, the Scotland level error rate `r glue_collapse(err$text, sep = ", ", last = " and ")`. This relates to the percentage of records with one or more error.

For a relatively small number of individuals, multiple records were submitted and to avoid counting these service users more than once, the following rules were applied to select only one record per individual:

1.	Keep record with earliest diagnosis date. If these are the same, then;
2.	Keep record with termination reason that service user has moved to a different Health Board area. If no record was terminated for this reason, then;
3.	Keep record with earliest first contact date.

There also exists a Service Level Agreement between NHS Highland and NHS Greater Glasgow & Clyde health boards, where some PDS is provided to Argyll & Bute residents by West Dunbartonshire IJB. The support provided to these service users has been apportioned to NHS Highland in this report, as part of the LDP Standard is a population based measure, and so by not including these Argyll & Bute residents this figure may be skewed.

As a result of the COVID-19 pandemic, some areas have reported difficulties in updating their data systems which are required to provide the dementia PDS dataset, however it is not anticipated that this has a large impact on the data presented in this report.

### Data Quality - Aberdeen City

Aberdeen City Health & Social Care Partnership ceased its contract with Alzheimer 
Scotland during 2019 and introduced an in-house Dementia Post-Diagnostic Support 
(PDS) service. This transition resulted in some PDS cases being terminated by 
Alzheimer Scotland earlier than 12 months and therefore not meeting the LDP 
standard. As part of the transition, individuals were contacted to ask if they still 
wanted to receive PDS which was then provided by the in-house service, if required. 
This should be taken into account when interpreting figures for Aberdeen City in 
2018/19. Although figures for 2019/20 and 2020/21 include the total number of people referred to PDS across all Integration Authority areas in NHS Grampian, data 
for Aberdeen City is not included in the measurement figures for the LDP standard. 
This is due to data quality issues and missing dates meaning it is not possible to 
accurately measure these referrals against the LDP standard.

### Data Quality - Perth & Kinross

NHS Tayside experienced challenges in capturing and reporting on electronic 
systems data within Perth & Kinross over the period 2018/19 to December 
2019. Despite local work undertaken to uncover the missing data, it has not been 
possible to fill this data gap. Subsequent measures put in place have successfully 
allowed NHS Tayside to improve on data reporting from 2019 onwards.


\newpage

## Appendix 2 - Publication metadata

**Publication title**  
[Dementia Post-Diagnostic Support: Local Delivery Plan (LDP) standard - Figures to `r latest_fy`]

**Description**  
[This publication reports on the [LDP standard](https://www.gov.scot/About/Performance/scotPerforms/NHSScotlandperformance/Dementia-LDP) that those people newly diagnosed with dementia should receive a minimum of one year's post-diagnostic support.]

**Theme**  
Health and Social Care

**Topic**  
Dementia Post-Diagnostic Support

**Format**  
PDF Report with Excel Tables

**Data source(s)**  
Public Health Scotland (PHS) Dementia Post-diagnostic support data submission from NHS Boards

[Estimated and Projected Diagnosis Rates for Dementia in Scotland: 2014-2020](https://www.gov.scot/publications/estimated-projected-diagnosis-rates-dementia-scotland-2014-2020/) 

**Date that data are acquired**  
Public Health Scotland (PHS) Dementia Post-diagnostic support data submission from NHS Boards as at `r format(end_date, "%d %B %Y")`

**Release date**  
`r format(pub_date, "%d %B %Y")`

**Frequency**  
Annual

**Timeframe of data and timeliness**  
This publication includes those diagnosed with dementia and referred for dementia post-diagnostic support between 1 April `r str_sub(fy_in_pub[1], 1, 4)` to 31 March 20`r str_sub(latest_fy, 6, 7)`. For diagnoses in `r latest_fy`, it is possible some service users are still receiving their post-diagnostic support and they are reported as ongoing.

**Continuity of data**  
Initial data collection for Dementia post-diagnostic support began in April 2013, however due to data completeness and quality issues the definitions and recording processes were revised during 2018/19 and were effective from 1 April 2019 for all records with a dementia diagnosis post 1 April 2016.

Information presented in this publication is not comparable to dementia post-diagnostic support LDP standard information published for time periods prior to 2016/17.  This is due to a combination of the change in definitions, improvements to data quality and refinements to the method used to calculate the standard.

**Revisions statement**  
Public Health Scotland (PHS) aims to continually improve the interpretation of the data and therefore analysis methods are regularly reviewed and may be updated in the future.

**Revisions relevant to this publication**  

This publication presents finalised figures for `r revised_fy` and provisional figures for `r latest_fy` subject to some service users still receiving post-diagnostic support.

**Concepts and definitions**  
The Data Definitions and Recording Guidance effective 01 April 2019 can be found on the [PHS website](https://publichealthscotland.scot/media/20921/2023-12-14-dementia-pds-definitions-and-recording-guidance-v14.pdf).

**Relevance and key uses of the statistics**  
The data presented in this release supports the Scottish Government’s LDP standard relating to those people newly diagnosed with dementia should receive a minimum of one year’s post-diagnostic support.

**Accuracy**  
This is an Official Statistics publication and the UK Statistics Authority’s Code of Practice has been followed throughout.

NHS Boards have the responsibility of gathering and submitting information on the delivery of Dementia post-diagnostic support for all Integration Joint Boards to support the measurement of the LDP standard. It is expected by PHS that quality assurance methods and measures are in place locally and implemented to ensure information is accurate and correct. PHS conduct quality checks upon receipt of data and feedback data queries to NHS Boards. 

As at the `r format(end_date, '%d %B %Y')` data submission, the Scotland level error rate `r glue_collapse(err$text, sep = ', ', last = ' and ')`.

`r a_city_statement`

**Completeness**  
Data submissions are received for all NHS Boards and include data for all Integration Joint Boards. 

As a result of the COVID-19 pandemic, some areas have reported difficulties in updating their data systems which are required to provide the dementia PDS dataset, however it is not anticipated that this has a large impact on the data presented in this report.

**Comparability**  
Information presented in this publication is not comparable to dementia post-diagnostic support LDP standard information published for time periods prior to 2016/17. This is due to a combination of the change in definitions, improvements to data quality and refinements to the method used to calculate the standard.

Comparability between NHS Boards / Integration Joint Boards should be done so with caution as services can provide different models of care and have varying resource issues.

**Accessibility**  
It is the policy of Public Health Scotland (PHS) to make its web sites and products accessible according to [published guidelines](https://beta.isdscotland.org/front-matter/accessibility-statement/). Accessibility of the report and findings are of continuous consideration throughout the report development and all figures have been assessed against the PHS accessibility guidelines.

**Coherence and clarity**  
The summary and publication report are accessible via the [PHS website]
  ("https://publichealthscotland.scot/publications/dementia-post-diagnostic-support/dementia-post-diagnostic-support-local-delivery-plan-standard-figures-to-202021/")
Tables and charts are presented within an Excel workbook with drop down boxes.

**Value type and unit of measurement**  
Numbers, percentages

**Disclosure**  
The [PHS protocol on Statistical Disclosure](https://beta.isdscotland.org/media/4191/public-health-scotland-statistical-disclosure-control-protocol.pdf) is followed.

**Official Statistics designation**  
Official Statistics

**UK Statistics Authority Assessment**  
[N/A]

**Last published**  
`r format(last_pub_date, "%d %B %Y")`

**Next published**  
`r paste("March", year(pub_date) + 1)`

**Date of first publication**  
24 January 2017

**Help email**  
phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)
<br>


**Date form completed**  
`r format(today(), "%d %B %Y")`

\newpage

## Appendix 3 - Early access details

### Pre-Release Access

Under terms of the "Pre-Release Access to Official Statistics (Scotland) Order 2008", PHS is obliged to publish information on those receiving Pre-Release Access ("Pre-Release Access" refers to statistics in their final form prior to publication). The standard maximum Pre-Release Access is five working days. Shown below are details of those receiving standard Pre-Release Access.

### Standard Pre-Release Access

Scottish Government Health Department

NHS Board Chief Executives

NHS Board Communication leads



\newpage

## Appendix 4 – PHS and Official Statistics

### About Public Health Scotland (PHS)

PHS is a knowledge-based and intelligence driven organisation with a critical reliance on data and information to enable it to be an independent voice for the public's health, leading collaboratively and effectively across the Scottish public health system, accountable at local and national levels, and providing leadership and focus for achieving better health and wellbeing outcomes for the population. Our statistics comply with the [Code of Practice for Statistics](https://www.statisticsauthority.gov.uk/code-of-practice/the-code/) in terms of trustworthiness, high quality and public value. This also means that we keep data secure at all stages, through collection, processing, analysis and output production, and adhere to the '[five safes](https://blog.ons.gov.uk/2017/01/27/the-five-safes-data-privacy-at-ons/)'.
