---
output: 
  word_document:
    reference_docx: "summary-template.docx"
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}

# Run setup environment script
source(here::here("code", "00_setup-environment.R"))

# Load basefile
pds <-
  read_rds(here("data", 
                glue("{fy}-{substr(as.numeric(fy)+1, 3, 4)}/Q{qt}"),
                glue("{fy}-{qt}_final-data.rds"))) %>%
  filter(fy %in% fy_in_pub)

# Number of referrals
referrals <-
  pds %>%
  group_by(fy) %>%
  summarise(referrals = sum(referrals))

# Create contact information
contacts <- tibble(
  contact1 = c("Lisa Reedie", "Principal Information Analyst", "0131 275 6117"),
  contact2 = c("Alice Byers", "Senior Information Analyst", "0131 314 1725")
)

```

# Dementia Post-Diagnostic Support
## NHS Board Performance to `r max(pds$fy)`
#### A Management Information publication for Scotland

#### Publication date: `r format(pub_date, "%d %B %Y")`
##### RESTRICTED STATISTICS: embargoed to 09:30 `r format(pub_date, "%d/%m/%Y")`

### About this release

This release by Information Services Division (ISD) reports on NHS Board performance against the Scottish Government’s Local Delivery Plan (LDP) standard that all those newly diagnosed with dementia should have a minimum of twelve months post-diagnostic support. Performance against the LDP standard is reported in two parts. The percentage of people referred for post diagnostic support who received a minimum of one year’s support, and the percentage of people estimated to be newly diagnosed with dementia who were referred for post-diagnostic support.

Figures reported in this release are for `r glue_collapse(fy_in_pub, sep = ", ", last = " and ")`. They are published as management information because **??**.


### Main Points

* There were `r referrals %>% filter(fy == fy_in_pub[1]) %>% pull(referrals)` people referred for dementia post-diagnostic support in `r fy_in_pub[1]` and `r referrals %>% filter(fy == fy_in_pub[2]) %>% pull(referrals)` in `r fy_in_pub[2]`.

* Quisque iaculis congue aliquet. Aenean in dictum nisl. Etiam quis ullamcorper ex. Aenean mollis ante eget.

Maecenas bibendum consequat vehicula. Fusce id viverra lorem, et

* Curabitur luctus luctus lorem, at commodo mauris rutrum quis. Mauris aliquet turpis vel magna bibendum hendrerit. Nulla finibus porta sapien ut pretium. Aliquam elementum mauris.

* Vivamus bibendum ut tellus rhoncus porttitor. Nam id nibh et.

* Ut in dapibus massa, ut gravida ligula. Vestibulum ut consectetur:

    + Vivamus luctus varius nibh, a scelerisque ex tincidunt non. Etiam dignissim.
    + Curabitur laoreet viverra magna eget dapibus. Maecenas scelerisque euismod mattis. Sed cursus.
    + Sed in iaculis lectus, sed fermentum urna. Donec efficitur diam eu ipsum viverra, eu ornare justo mollis. Phasellus in dictum tellus.

### Background

Aliquam sed maximus ante, a imperdiet est. Vivamus vel diam facilisis, pulvinar erat consequat, consequat nulla. Praesent lorem dolor, luctus ut libero vitae, venenatis congue tortor.

Nunc at mauris euismod, mattis tellus sed, vehicula dolor. Duis quis auctor elit. Fusce eu dui eu magna convallis porttitor in ac purus. Proin sed tellus massa. In pulvinar augue sit amet faucibus maximus. Aenean porttitor arcu vitae lacus fringilla condimentum. Praesent laoreet, felis non dignissim viverra, libero nunc eleifend sapien, sed dignissim felis risus et tellus.

Please see [News and Updates section](http://www.isdscotland.org/) of our website for more details.

### Contact

```{r contact-table, echo = FALSE}
contacts %>%
  flextable() %>%
  delete_part(part = "header") %>%
  bold(i = 1) %>%
  align(align = "left") %>%
  border_remove() %>%
  height_all(height = 0.2) %>%
  width(j = 1:2, width = 2.2)
```

<br> [nss.isddementiapds@nhs.net](mailto:nss.isddementiapds@nhs.net)


### Further Information

Find out more in the [full report](http://www.isdscotland.org/). The data from this publication is available to download [from our webpage](http://www.isdscotland.org/) along with a [background information and glossary](http://www.isdscotland.org/), and [metadata document](http://www.isdscotland.org/). 

For more information on XXX see the [XXX section of our website](http://www.isdscotland.org/). For related topics, please see the [XXX](http://www.isdscotland.org/) pages.

The next release of this publication will be DD Month YYYY.

### NHS Performs

A selection of information from this publication is included in [NHS Performs](http://www.nhsperforms.scot/). NHS Performs is a website that brings together a range of information on how hositals and NHS Boards within NHSScotland are performing.


