---
output: 
  officedown::rdocx_document:
    reference_docx: "templates/summary-template.docx"
    fig_caption: no
---

```{r set-up, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}
source(here::here("code", "publication", "00_setup-pub-environment.R"))
source(here("functions", "flextable_style.R"))

latest_fy  <- nth(fy_in_pub, -1)
revised_fy <- nth(fy_in_pub, -2)

pub_date_url <- 
  paste0("https://beta.isdscotland.org/find-publications-and-data/",
         "conditions-and-diseases/dementia/dementia-post-diagnostic-support/",
         format(pub_date, "%e-%B-%Y") %>% str_trim())

# Function to format percentages
format_perc <- function(x, dp = 1){
  x %>%
    round_half_up(dp) %>%
    format(nsmall = dp) %>%
    paste0("%") %>%
    trimws()
}

# Read in data ----

# LDP Dataset
pds <- 
  read_rds(
    here("data", "publication", glue("{pub_date}_pub-data.rds"))
  ) %>%
  filter(ijb != "Unknown" & referrals > 0)

# Expected Diagnoses (Incidence)
exp <- read_csv(here("reference-files", "expected-diagnoses.csv")) %>%
  select(fy, health_board = health_board_label, diagnoses)

# Error rates 
err <- 
  read_rds(
    here("data", 
         glue("{fy}-{substr(as.numeric(fy)+1, 3, 4)}/Q{qt}"),
         glue("{fy}-{qt}_error-summary.rds"))
  ) %>%
  filter(health_board == "Scotland" & fy %in% fy_in_pub) %>%
  mutate(perc = format_perc(total_errors / records * 100)
  ) %>%
  select(fy, perc) %>%
  mutate(text = glue("for {fy} was {perc}"))

# Create contact information
contact1 <- c("Lisa Reedie", 
              "Principal Information Analyst", 
              "0131 275 6117",
              "phs.dementiapds@phs.scot")
contact2 <- c("Alice Byers", 
              "Senior Information Analyst", 
              "0131 314 1725",
              "")

contact <- tibble(contact1, contact2)
```

```{r summary-data, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}
summary <-
  pds %>%
  filter(fy %in% c(latest_fy, revised_fy)) %>%
  group_by(fy) %>%
  summarise(across(referrals:denominator, sum), .groups = "drop") %>%
  left_join(
    exp %>% filter(health_board == "Scotland") %>% select(-health_board),
    by = "fy"
  ) %>%
  mutate(
    inc_perc = referrals / diagnoses * 100,
    year_perc = numerator / denominator * 100
  ) %>%
  mutate(across(contains("perc"),
                ~ paste0(format(round_half_up(., 1), nsmall = 1), "%")))
```

<Div custom-style = "Publication Title">Dementia Post-Diagnostic  
Support</Div>
<Div custom-style = "Publication subtitle">Local Delivery Plan Standard; Figures to `r latest_fy`</Div>
<Div custom-style = "National stats">An Official Statistics release for Scotland</Div>

<Div custom-style = "Normal-no-notes"><br></Div>

**Publication date: `r format(pub_date, "%d %B %Y")`**

<Div custom-style = "RestrictedStats">RESTRICTED STATISTICS: embargoed to 09:30 `r format(pub_date, "%d/%m/%Y")`</Div>

### About this release
This release by Public Health Scotland (PHS) reports on the Scottish Government’s Local Delivery Plan (LDP) standard that all people newly diagnosed with dementia should receive a minimum of one year’s post-diagnostic support. The LDP standard is reported in two parts: the percentage of people estimated to be newly diagnosed with dementia who were referred for post-diagnostic support; and, of those referred, the percentage who received a minimum of one year’s support. This report presents finalised figures for `r glue_collapse(setdiff(fy_in_pub, latest_fy), sep = ", ", last = " and ")` and provisional figures for `r latest_fy` which are subject to some service users completing their support.

### Main Points

* There were `r summary %>% filter(fy == latest_fy) %>% pull(referrals)` people diagnosed and referred for dementia post-diagnostic support in `r latest_fy`, compared to `r summary %>% filter(fy == revised_fy) %>% pull(referrals)` in `r revised_fy`.

* Of those referred in `r latest_fy` for post-diagnostic support, `r summary %>% filter(fy == latest_fy) %>% pull(year_perc)` received a minimum of one year's support. In `r revised_fy`, the percentage was `r summary %>% filter(fy == revised_fy) %>% pull(year_perc)`.

<Div custom-style = "Chart title">Percentage of referrals who received a minimum of one year’s post-diagnostic support by NHS Board; `r latest_fy`^P^</Div>

<Div custom-style = "Figure_Style">
```{r fig-summary, echo=FALSE}
external_img(
  here("publication", "output", pub_date, "figures", 
       paste0(pub_date, "_summary-chart.png")),
  width = 4, height = 3.8,
  alt = glue(
    "Bar chart showing percentage of referrals who received a minimum of ",
    "one year's post-diagnostic support by NHS Board in ",
    "financial year {latest_fy}."
  )
)
```
</Div>

<Div custom-style = "Footnotes">
**Notes**

1. Figures for `r latest_fy` are provisional (^P^) subject to all service users completing their support.

2. Figures for NHS Grampian are affected by a change in service provision of PDS within Aberdeen City during 2019. See background for further information.
</div>

* In Scotland, `r summary %>% filter(fy == latest_fy) %>% pull(inc_perc)` of those people estimated to be newly diagnosed with dementia in `r latest_fy` were referred for post-diagnostic support, compared to `r summary %>% filter(fy == revised_fy) %>% pull(inc_perc)` in `r revised_fy`.

### Background

The Scottish Government published their [third national dementia strategy](https://beta.gov.scot/publications/scotlands-national-dementia-strategy-2017-2020/) in 2017. This included the commitment to extend and embed dementia post-diagnostic support (PDS). In order to effectively monitor the delivery of PDS a national [local delivery plan (LDP) standard](https://www.gov.scot/About/Performance/scotPerforms/NHSScotlandperformance/Dementia-LDP) was introduced for all people newly diagnosed with dementia to receive a minimum of one year’s PDS.

NHS Boards provide quarterly data submissions to PHS, in line with data definitions effective 1 April 2019, on individuals diagnosed with dementia and referred for post-diagnostic support within their local areas. This dataset forms the basis of the LDP standard calculation. For this report, the Scotland level error rate `r glue_collapse(err$text, sep = ", ", last = " and ")`.

Aberdeen City Health & Social Care Partnership ceased its contract with Alzheimer Scotland during 2019 and introduced an in-house dementia PDS service. This transition resulted in some PDS cases being terminated by Alzheimer Scotland earlier than 12 months and therefore not meeting the LDP standard.  As part of the transition, individuals were contacted to ask if they still wanted to receive PDS which was then provided by the in-house service, if required. This should be taken into account when interpreting figures for 2018/19.

Information presented in this publication is not comparable to information published for time periods prior to 2016/17. 

Part of the LDP standard calculation requires the number of referrals for PDS to be compared against an estimated number of newly diagnosed dementia cases each year. Health Board level estimates of people newly diagnosed with dementia (incidence) used for this calculation are from the paper [‘Estimated and Projected Diagnosis Rates for Dementia in Scotland 2014-2020’](https://www.gov.scot/publications/estimated-projected-diagnosis-rates-dementia-scotland-2014-2020/) published by the Scottish Government in 2016.

### Contact

```{r contact-table, echo = FALSE, ft.align = "left"}
set_flextable_defaults(
  font.family = "Arial", 
  font.size = 12,
  font.color = "black"
)

contact %>%
  flextable() %>%
  compose(i = 4, j = 1,
          value = as_paragraph(
            hyperlink_text(x = contact$contact1[4],
                           url = paste0("mailto:", contact$contact1[4]),
                           props = fp_text(color = "#964091",
                                           underlined = TRUE,
                                           font.size = 12))
          )) %>%
  delete_part(part = "header") %>%
  bold(i = 1) %>%
  align(align = "left") %>%
  border_remove() %>%
  height_all(height = 0.01) %>%
  width(width = 2.5) %>%
  line_spacing(part = "body", space = 0.5)
```

For all media enquires, please email [phs.comms@phs.scot](mailto:phs.comms@phs.scot) or call 07500 854 574.

### Further Information
Data from this publication, along with the full report, are available from the [publication page](`r pub_date_url`) on our website.

For further information, please see the [Dementia Post-Diagnostic Support](https://www.isdscotland.org/Health-Topics/Mental-Health/Dementia-Post-diagnostic-Support/) web page. 

For information on the Dementia Benchmarking toolkit, please see the publication [web page](https://beta.isdscotland.org/find-publications-and-data/conditions-and-diseases/dementia/dementia-benchmarking-toolkit/). For related topics, please see the [mental health](https://www.isdscotland.org/Health-Topics/Mental-Health/) and [health and social community care](http://www.isdscotland.org/Health-Topics/Health-and-Social-Community-Care/) web pages.

The next release of this publication will be in `r format(pub_date + years(1), "%B %Y")`.
