---
output: 
  officedown::rdocx_document:
    reference_docx: "templates/summary-template.docx"
    fig_caption: no
---


```{r, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}

# Run setup environment script
source(here::here("code", "00_setup-environment.R"))

# Write numbers with thousands separator
knit_hooks$set(inline = function(x){
  if(!is.character(x)){prettyNum(x, big.mark=",")}else{x}
})

latest_fy <- last(fy_in_pub)
prev_fy   <- nth(fy_in_pub, -2)

# Read in data
pds <- 
  read_rds(
    here("data", 
         glue("{fy}-{substr(as.numeric(fy)+1, 3, 4)}/Q{qt}"),
         glue("{fy}-{qt}_final-data.rds"))
  ) %>%
  
  # Select only FY to be incuded in pub
  filter(fy %in% fy_in_pub) %>%
  
  # Remove codes from board and IJB
  mutate(health_board = str_sub(health_board, 3, -1),
         ijb          = if_else(is.na(ijb),
                                "Unknown",
                                str_sub(ijb, 11, -1)))

# Load expected diagnoses reference file
exp <- read_csv(here("reference-files", "expected-diagnoses.csv")) %>%
  filter(health_board == "Scotland" & fy %in% fy_in_pub)

perc_complete <-
  pds %>%
  group_by(fy, ldp) %>% 
  summarise(ref = sum(referrals), .groups = "drop") %>%
  group_by(fy, x = ldp %in% c("complete", "exempt")) %>%
  mutate(complete = sum(ref)) %>%
  group_by(fy) %>%
  mutate(all = sum(ref)) %>%
  filter(x) %>%
  distinct(fy, complete, all) %>%
  mutate(perc = round_half_up(complete / all * 100, 1))

age_data <-
  pds %>%
  filter(age_grp != "Unknown") %>%
  group_by(fy, age_grp) %>%
  summarise(ref = sum(referrals), .groups = "drop") %>%
  group_by(fy) %>%
  mutate(perc = ref / sum(ref) * 100) %>%
  ungroup()

incidence <-
  pds %>% 
  group_by(fy) %>%
  summarise(ref = sum(referrals), .groups = "drop") %>%
  left_join(exp, by = "fy") %>%
  mutate(perc = round_half_up(ref / diagnoses * 100, 1))

alt_text <-
  paste0("Bar chart showing distribution of referrals to dementia ",
         "post-diagnostic support by age group in financial year ",
         latest_fy, ".")

err <- read_rds(here("data", 
                     glue("{fy}-{substr(as.numeric(fy)+1, 3, 4)}/Q{qt}"),
                     glue("{fy}-{qt}_error-summary.rds"))) %>%
  filter(fy %in% fy_in_pub) %>%
  group_by(fy) %>%
  summarise(across(where(is.numeric), sum), .groups = "drop") %>%
  mutate(perc = round_half_up(total_errors/records * 100, 0))

# Create contact information
contact1 <- c("Lisa Reedie", 
              "Principal Information Analyst", 
              "0131 275 6117",
              "phs.dementiapds@phs.scot")
contact2 <- c("Alice Byers", 
              "Senior Information Analyst", 
              "0131 314 1725",
              "")

contact <- tibble(contact1, contact2)

pub_date_url <- 
  paste0("https://beta.isdscotland.org/find-publications-and-data/",
         "conditions-and-diseases/dementia/dementia-post-diagnostic-support/",
         format(pub_date, "%e-%B-%Y") %>% str_trim())
```

<Div custom-style = "Publication Title">Dementia Post-Diagnostic  
Support</Div>
<!-- <Div custom-style = "Publication Title">Support</Div> -->
<Div custom-style = "Publication subtitle">Local Delivery Plan Standard; Figures to `r latest_fy`</Div>
<Div custom-style = "National stats">An Official Statistics publication for Scotland</Div>

<br>

**Publication date: `r format(pub_date, "%d %B %Y")`**

<Div custom-style = "RestrictedStats">RESTRICTED STATISTICS: embargoed to 09:30 `r format(pub_date, "%d/%m/%Y")`</Div>

### About this release
This release by Public Health Scotland (PHS) reports on the Scottish Government’s Local Delivery Plan (LDP) standard that all those newly diagnosed with dementia should receive a minimum of one year’s post-diagnostic support. The LDP standard is reported in two parts. The percentage of people estimated to be newly diagnosed with dementia who were referred for postdiagnostic support and, of those referred, the percentage who received a minimum of one year’s support. This report presents finalised figures for `r glue_collapse(setdiff(fy_in_pub, latest_fy), sep = ", ", last = " and ")` and provisional figures for `r latest_fy` which are subject to some service users completing their support.

### Main Points
* There were `r pds %>% filter(fy == latest_fy) %$% sum(referrals)` people diagnosed and referred for dementia post-diagnostic support in `r latest_fy`, compared to `r pds %>% filter(fy != latest_fy) %>% group_by(fy) %>% summarise(ref = sum(referrals)) %>% pull(ref) %>% glue_collapse(sep = ", ", last = " and ")` in `r pds %>% filter(fy != latest_fy) %$% unique(fy) %>% glue_collapse(sep = ", ", last = " and ")` respectively.

* Of those referred in `r latest_fy` for post-diagnostic support, `r perc_complete %>% filter(fy == latest_fy) %>% pull(perc)`% received a minimum of one year's support. In `r prev_fy`, the percentage was `r perc_complete %>% filter(fy == prev_fy) %>% pull(perc)`%.

* In `r latest_fy`, those aged `r age_data %>% filter(fy == latest_fy) %>% filter(perc == max(perc)) %>% pull(age_grp)` years accounted for the largest percentage of people referred for post-diagnostic support (`r age_data %>% filter(fy == latest_fy) %$% max(perc) %>% round_half_up(1) %>% format(nsmall = 1)`%).

<Div custom-style = "Chart Title">Age distribution of referrals to dementia post-diagnostic support; `r latest_fy`^p^</Div>
<Div custom-style = "Figure_Style">
```{r age-dist-chart, echo=FALSE}
external_img(
  here("publication", "output", pub_date, "figures", 
       paste0(pub_date, "_summary-chart.png")),
  width = 6.8, height = 3.5,
  alt = "alt text here"
)
```
</Div>

<Div custom-style = "Footnotes">^p^ Figures for `r latest_fy` are provisional subject to all service users completing their support.</div>

<br>

* In Scotland, `r incidence %>% filter(fy == latest_fy) %>% pull(perc)`% of those people estimated to be newly diagnosed with dementia in `r latest_fy` were referred for post-diagnostic support. 

### Background
The Scottish Government published their [third national dementia strategy](https://beta.gov.scot/publications/scotlands-national-dementia-strategy-2017-2020/) in 2017. This included the commitment to extend and embed dementia post-diagnostic support. In order to effectively monitor the delivery of post-diagnostic support a national [local delivery plan (LDP) standard](https://www.gov.scot/About/Performance/scotPerforms/NHSScotlandperformance/Dementia-LDP) was introduced for all those newly diagnosed with dementia to receive a minimum of one year’s postdiagnostic support.

NHS Boards provide quarterly data submissions to Public Health Scotland on individuals diagnosed and referred for post-diagnostic support within their local areas and this dataset forms the basis of the LDP standard calculation.

Revised [data definitions](https://www.isdscotland.org/Health-Topics/Mental-Health/Dementia-Post-diagnostic-Support/_docs/Dementia-PDS-Definitions-and-Recording-Guidance.pdf) and reporting processes were effective from 1 April 2019 and designed in consultation with stakeholders to improve the quality and consistency of the data reported. The Scotland level error rate for `r latest_fy` is `r err %>% filter(fy == latest_fy) %>% pull(perc)`%. **Add error rate for previous years here**.

Information presented in this publication is not comparable to previously published information relating to the dementia post-diagnostic support LDP standard. This is due to a combination of the change in definitions, improvements to data quality and refinements to the method used to calculate the standard which are detailed in the main publication report.

Part of the LDP standard calculation requires the number of referrals for post-diagnostic support to be compared against an estimated number of newly diagnosed dementia cases each year. Health Board level estimates of people newly diagnosed with dementia (incidence) used for this calculation are from the paper [‘Estimated and Projected Diagnosis Rates for Dementia in Scotland 2014-2020’](https://www.gov.scot/publications/estimated-projected-diagnosis-rates-dementia-scotland-2014-2020/) published by the Scottish Government in 2016.

<br>

### Contact

```{r contact-table, echo = FALSE, ft.align = "left"}
set_flextable_defaults(
  font.family = "Arial", 
  font.size = 12,
  font.color = "black"
)

contact %>%
  flextable() %>%
  compose(i = 4, j = 1,
          value = as_paragraph(
            hyperlink_text(x = contact$contact1[4],
                           url = paste0("mailto:", contact$contact1[4]),
                           props = fp_text(color = "#964091",
                                           underlined = TRUE,
                                           font.size = 12))
          )) %>%
  delete_part(part = "header") %>%
  bold(i = 1) %>%
  align(align = "left") %>%
  border_remove() %>%
  height_all(height = 0.01) %>%
  width(width = 2.5) %>%
  line_spacing(part = "body", space = 0.5)
```

For all media enquires, please email [phs.comms@phs.scot](mailto:phs.comms@phs.scot) or call 07500 854 574.

<br>

### Further Information
Data from this publication, along with the full report, are available from the [publication page](`r pub_date_url`) on our website.

For further information, please see the [Dementia Post-Diagnostic Support](https://www.isdscotland.org/Health-Topics/Mental-Health/Dementia-Post-diagnostic-Support/) web page. 

For information on the Dementia Benchmarking toolkit, please see the publication [web page](https://beta.isdscotland.org/find-publications-and-data/conditions-and-diseases/dementia/dementia-benchmarking-toolkit/). For related topics, please see the [mental health](https://www.isdscotland.org/Health-Topics/Mental-Health/) and [health and social community care](http://www.isdscotland.org/Health-Topics/Health-and-Social-Community-Care/) web pages.

The next release of this publication will be in `r format(pub_date + years(1), "%B %Y")`.
