---
title: "Dementia Post-Diagnostic Support"
output: 
  word_document:
    reference_docx: "/conf/dementia/A&I/Outputs/publication/templates/phs-offstats-summary.docx"
    fig_caption: no
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi = 300)
library(ggplot2)
```

```{r set-up, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}
source(here::here("code", "publication", "00_setup-pub-environment.R"))

pub_date_url <- 
  paste0("https://publichealthscotland.scot/publications/",
         "dementia-post-diagnostic-support/dementia-post-diagnostic-support-local-delivery-plan-standard-figures-to-",
         (latest_fy))

fig_alttext <- glue("Bar chart showing percentage of referrals who received a minimum of one year's post-diagnostic support by NHS Board in financial year {latest_fy}.")

# Function to format percentages
format_perc <- function(x, dp = 1){
  x %>%
    round_half_up(dp) %>%
    format(nsmall = dp) %>%
    paste0("%") %>%
    trimws()
}

# Read in data ----

# LDP Dataset
pds <- 
  read_rds(data_path(directory = "publication", 
                    type = "pub_data",
                    ext = "rds"))%>%
  filter(ijb != "Unknown" & referrals > 0)

# Expected Diagnoses (Incidence)
exp <- read_csv(exp_diagnoses_path()) %>%
  select(fy, health_board = health_board_label, diagnoses)

# Error rates 
err <- 
  read_rds(data_path(directory = "mi", 
                    type = "error_data",
                    ext = "rds")) %>% 
  filter(health_board == "Scotland" & fy %in% fy_in_pub) %>%
  mutate(perc = format_perc(total_errors / records * 100)
  ) %>%
  select(fy, perc) %>%
  mutate(text = glue("for {fy} was {perc}"))
```

```{r summary-data, echo = FALSE, message = FALSE, warning = FALSE, error = FALSE}
summary <-
  pds %>%
  filter(fy %in% c(latest_fy, revised_fy)) %>%
  group_by(fy) %>%
  summarise(across(referrals:denominator, sum), .groups = "drop") %>%
  left_join(
    exp %>% filter(health_board == "Scotland") %>% select(-health_board),
    by = "fy"
  ) %>%
  mutate(
    inc_perc = referrals / diagnoses * 100,
    year_perc = numerator / denominator * 100
  ) %>%
  mutate(across(contains("perc"),
                ~ paste0(format(round_half_up(., 1), nsmall = 1), "%")))
```

<Div custom-style = "Publication subtitle">Local Delivery Plan Standard; Figures to `r latest_fy`</Div>
<Div custom-style = "Stats designation">An Official statistics release for Scotland</Div>
<Div custom-style = "Publication date">Publication date: `r format(pub_date, "%d %B %Y")`</Div>
<Div custom-style = "Restricted Stats">RESTRICTED STATISTICS: embargoed to 09:30 `r format(pub_date, "%d/%m/%Y")`</Div>

# About this release
This release by Public Health Scotland (PHS) reports on the Scottish Government’s Local Delivery Plan (LDP) standard that everyone newly diagnosed with dementia will be offered a minimum of one year’s post-diagnostic support, coordinated by an appropriately trained Link Worker, including the building of a person-centred support plan. Performance is reported in two parts: 1. The percentage of people estimated to be newly diagnosed with dementia who were referred for post-diagnostic support. 2. The percentage of people referred who received a minimum of one year’s support coordinated by a link worker, including the building of a person-centred support plan. This report presents finalised figures for `r glue_collapse(setdiff(fy_in_pub, latest_fy), sep = ", ", last = " and ")` and provisional figures for `r latest_fy` which are subject to some service users completing their support.

# Main Points

<Div custom-style = "Bullet 1">There were `r summary %>% filter(fy == latest_fy) %>% pull(referrals)` people diagnosed and referred for dementia post-diagnostic support in `r latest_fy`, compared to `r summary %>% filter(fy == revised_fy) %>% pull(referrals)` in `r revised_fy`.</Div>

<Div custom-style = "Bullet 1">Of those referred in `r latest_fy` for post-diagnostic support, `r summary %>% filter(fy == latest_fy) %>% pull(year_perc)` received a minimum of one year's support. In `r revised_fy`, the percentage was `r summary %>% filter(fy == revised_fy) %>% pull(year_perc)`.</Div>

<Div custom-style = "Table or chart caption">Percentage of referrals who received a minimum of one year’s post-diagnostic support by NHS Board; `r latest_fy`^P^</Div>

```{r chart, fig.width=7.18, fig.height=3.31, fig.cap=fig_alttext}
include_graphics(pub_figures_path(type = "summary"))
```

<Div custom-style = "Footnote Text">
**Notes**

1. Figures for `r latest_fy` are provisional (^P^) subject to all service users completing their support.

2. Figures for NHS Grampian are affected by a change in service provision of PDS within Aberdeen City during 2019. See background for further information.
</div>

<Div custom-style = "Bullet 1">In Scotland, `r summary %>% filter(fy == latest_fy) %>% pull(inc_perc)` of those people estimated to be newly diagnosed with dementia in `r latest_fy` were referred for post-diagnostic support, compared to `r summary %>% filter(fy == revised_fy) %>% pull(inc_perc)` in `r revised_fy`.</Div>

# Background

The Scottish Government published their [third national dementia strategy](https://beta.gov.scot/publications/scotlands-national-dementia-strategy-2017-2020/) in 2017. This included the commitment to extend and embed dementia post-diagnostic support (PDS). In order to effectively monitor the delivery of PDS a national [local delivery plan (LDP) standard](https://www.gov.scot/About/Performance/scotPerforms/NHSScotlandperformance/Dementia-LDP) was introduced for all people newly diagnosed with dementia to receive a minimum of one year’s PDS.

NHS Boards provide quarterly data submissions to PHS, in line with data definitions effective 1 April 2019, on individuals diagnosed with dementia and referred for post-diagnostic support within their local areas. This dataset forms the basis of the LDP standard calculation. For this report, the Scotland level error rate `r glue_collapse(err$text, sep = ", ", last = " and ")`.

The figures presented for 2019/20 and 2020/21 include the total number of people referred to 
PDS across all partnership areas however due to data quality issues Aberdeen City data is not 
included in the measurement figures for the LDP standard as it is not possible to accurately 
measure these referrals against the standard.

Information presented in this publication is not comparable to information published for time periods prior to 2016/17. 

Part of the LDP standard calculation requires the number of referrals for PDS to be compared against an estimated number of newly diagnosed dementia cases each year. Health Board level estimates of people newly diagnosed with dementia (incidence) used for this calculation are from the paper [‘Estimated and Projected Diagnosis Rates for Dementia in Scotland 2014-2020’](https://www.gov.scot/publications/estimated-projected-diagnosis-rates-dementia-scotland-2014-2020/) published by the Scottish Government in 2016.

# Contact

Zeg Ashraf | Principal Information Analyst | 0131 314 1737 [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

Jennifer Noall | Senior Information Analyst | 0131 275 7220 | [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

Jennifer Thom | Information Analyst | 0131 314 1754 | [phs.dementiapds@phs.scot](mailto:phs.dementiapds@phs.scot)

For all media enquires, please email [phs.comms@phs.scot](mailto:phs.comms@phs.scot) or call 0131 275 6105.

# Further Information
Data from this publication, along with the full report, are available from the [publication page](`r pub_date_url`) on our website.

Our statistical practice is regulated by the Office for Statistics Regulation (OSR).

Visit our website for [further information about our statistics and PHS as an Official Statistics producer.](https://publichealthscotland.scot/our-organisation/about-our-statistics/official-statistics/)

The next release of this publication will be in `r format(pub_date + years(1), "%B %Y")`.

Other formats of this publication are available on request by calling 0131 314 5300 or emailing phs.otherformats@phs.scot.

# NHS Performs
A selection of information from this publication is included in [NHS Performs](http://www.nhsperforms.scot). NHS Performs is a website that brings together a range of information on how hospitals and NHS Boards within NHSScotland are performing.

